\documentclass{book}
\usepackage{geometry, parskip}
\geometry{a5paper, left=20mm, right=20mm, top=10mm}
\pagenumbering{gobble}
\begin{document}
%\chapter*{\textit{You exist, in my mind}}
%\begin{quote}
%	\textit{I was 7, when my fear of night first began.\\
%			A child should sleep on their bed.\\
%			Not under it.\\\
%			But just to make it clear, I wasn't scared of \textbf{the} night.
%			In fact, I thrived during the darkest hours of the night and revelled
%			when the midnight clock chimed.
%			I wasn't scared of the night.
%			No, not the night or the monsters under my bed.
%			No, not the night and all the dreary thoughts that would leave and enter my head.\\
%			Sleep.\\
%			I was scared of sleep. Terrified of it. I hated the feeling of being
%			``alive'' a nightmare gave to the false sense of security a dream gave.
%	        I hated everything about it and all the lies told about it, just the word itself was enough
%			to throw of my whole mood. Thus, I can justify my hatred of it but not conclude it. As sleep
%			allows us all to temporarily detach from the parasitical relationship we have with life. I
%			suppose it's been long enough for me to brush dust off of old memories. Very well then, this is
%			my story. Of a different world and a different time when the world was ghost-quiet except for the
%			crack of dawn and when problems started as quickly as they vanished.}
%underling
%	\end{quote}

\chapter*{\textbf{To Hell With It}}
\newpage
	\begin{center}
		\textbf{\huge{\textit{Dead people receive more flowers than the living because
		gratitude is swapped for regret.}}}
	\end{center}
	\smallskip
	\Large{\textbf{At least that's what was written on the chalkboard
	outside of a flower shop.\\
	Flights were scheduled to touch down
	at 8 precisely. The sky above me looked lazily drawn,
	the colour of old-television, but tuned to one of those
	long-dead channels. Clouds stared back at me,
	continuing the notion I held, that they looked nothing more
	than splodges of dirty paint on a clean canvas, before continuing
	with their journey.
	And there seemed to be a constant
	racket of murmuring, just within earshot.\\
	Yes, today was day, I was set to leave.
	The date was the 29$^{th}$ of February
	I had just graduated from university
	and was ready to be packed and shipped into one
	of those dinky little office cubicles they kept in the big city.
    Having, sat through years of state education all my life, It felt only fitting
    to show my grades to my father,
	Having shifted through hundreds of job openings, father finally
	looked at me with a half-sunken face, and said `Why ye-s', after concurring with his friends.\\\\
	describe wills suit. my host or buddies as they were called.
	Over the course of my final academic years, I had developed
	what I could only describe as an unprovoked and unimagined
	scorn to every man and woman, I was to meet.\\\\
	However, two people were exempt from my criticism.\\\\
    %%%%%%%
 	Yes, Akbar.\\\\Akbar was exempt.\\\\
	If tolerance, is a continuous chain of suffering,
	then there was something gorgeous about him in the frenzy of it all,
    some heightened sense of alertness, as if he was
	related to one of those self-aware simulations, locked thousands of miles away.\\
	When most registered men, could do nothing
	more than to look away
	and raise a handkerchief to their face, as if to politely protest your presence.\\
	Akbar would waver you on and give it no second thought.
	Akbar was more machine than man in that sense.
	In my worst of temperments, I snapped and
	asked. \\
	``What do you want Akbar?
	Money, Broads, Dames, Hookers... There's loads
	of them downtown, you should go there one day, do a man like you some good'' .\\\\
	%manoeuvre
	``I don't know... I want something that isn't this, old sport''\\\\
	This annoyed me.\\\\
	He looked to me, as if all principle left my body, then resumed his current task and continued with his sanguine walk.\\
	I knew what wasn't this. And I knew never to ask again.\\\\
	No-Akbar turned out alright in the end.\\
	What preyed on Akbar, was something I believed every
	good man must be put through, before he be considered, that
	he be recognised for his deeds.\\
	Other men of our time, took much apart into mere prattle without
	practice. Akbar had not. Only conditioned, to make many a permanent
	of decisions, on temporary fuel. Akbar had not.\\
	No-Akbar had turned out alright in the end.\\
	If not for her, I'm certain his character would
	be revealed to all the hidden chasms of the world.
    He was a gentleman in every sense of the word, capable solely for her.\\\\
	That sign I had read this morning, obviously must have meant a great deal for me,
	well at the time of course. I've brushed it of as clever marketing but
	I wouldn't still be thinking about it, if that was the case.\\\\
	Whenever, I had made a clever observation in class I wish she could have been there to witness my temporary geniusness.
	The rational thing to do, would be to just ignore it. But...\\
	It was a beautiful sign. Letters seemed to dance and flow down the
	and the white chalk stood out.
	}}
	\newpage
	\Large{\textbf{The alarm bell rang.\\\\
				   Rring ring! Rring ring!\\\\
                   Two giant arms and two steel fists were cocked back like a revolver;
				   ready to fire their empty rounds, into not-so-empty space.
				   Rounds ricocheted off of bruised walls and dove right into my ears,
				   rattling the ins-and-outs of my skull.\\\\
				   Rring ring! Rring ring!\\\\
				   Post-it notes.\\\\
				   Tacked to the wall and written in a cursive script, all but one, began to lose their grip.
				   Fluttering towards the floor; they bowed towards their audience. Reduced to rubble they were no more. \\\\
				   Glass bottles.\\\\
				   Half-full and half-empty.
				   Clanked from side-to-side, rolling past and right into each other
				   And as they did, their insides swashed up and down like a ships rum on a stormy night.
				   And just like Poseidons wrath...\\\\
				   Rring ring! Rring ring!\\\\
				   My ears were met with a heavy thud.\\\\
				   Then a gristly crunch.\\\\
				   And a small shatter.\\\\
                   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
				   At first the crack was tiny, like the spindles of a spiders web.
				   But as it skipped along the panel of glass, it reached every corner
				   and made work, where needed done.
				   As if a million hammers had struck all at once, it lay there defeated.\\\\
				   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
				   Wind, swept through the crime-scene, bits of glass were blown left-and-right carried.\\\\
				   At that moment in time, I could have only been clawing at the insides of my eyelids.
				   I wanted out.\\\\
				   And fast.\\\\
				   My eyes felt like two tents, pegged down and flapping about amidst the chaos.\\\\
				   \textit{Huh?}\\\\
				   \textit{They won't budge.}\\\\
				   Left eye.\\\\
				   Shut.\\\\
				   Right eye?\\\\
				   Shut to.\\\\
				   My brain felt hot and heavy and I put in every effort to open my eyes.
				   My bed, which had sat patiently along my room soon began
				   to give into the alarms demands.\\\\}}
			%	   My screams fade, and are quickly replaced
			%	   by silenced by the quick footsteps of man and whizizng of cars.
			%	   He was the opposite of Akbar.
		    %      I didn't like the look of him.
\end{document}
