\documentclass{book}
\usepackage{geometry, parskip}
\geometry{a5paper, left=20mm, right=20mm, top=10mm}
\pagenumbering{gobble}
\begin{document}
\chapter*{You exist, in my mind}
\begin{quote}
\textit{I was 7, when my fear of the night first began.\\\\
A child should sleep on their bed.\\\\
Not under it.\\\\
But just to make it clear, I wasn't scared of the night. In fact, I thrived during the darkest of hours and revelled when the midnight clock rang.
I wasn't scared of the night.
No, not the night or the monsters that hid under my bed.
No, not the night and all the dreary thoughts that would enter my head.
Sleep.\\\\
I was scared of sleep... absolutely terrified of it. I hated everything about it; from the false sense of security a dream gave you
to the feeling of being ``alive'' a nightmare gave.
I hated everything about it and all the lies told about it, just the word itself was enough to throw of my whole mood.
Thus, I can justify my hatred of sleep but not conclude it, I suppose it's been long enough for me to brush dust of old memories.
Very well then, this is my story. Of a different world and a different time when the world was ghost-quite except for the crack of dawn and when problems
started as quickly as they vanished.}
\end{quote}
\chapter{In this world, we have no-one}
\Large{\textbf{The alarm bell rang.\\\\
	Rring ring! Rring ring!\\\\
	Two giant arms and two fists were cocked back like a revolver.
	Ready to fire their empty rounds into not-so-empty space.
	Their rounds ricocheted off of bruised walls and bounced right into my ears;
	rattling the ins-and-outs of my skull.\\\\
	Rring ring! Rring ring!\\\\
	Post it notes.\\\\
	Tacked down to the wall and written in a scrawly script began to lose
	their grip; fluttering towards the floor. Taking a mere bow as they were
	reduced to rubble.\\\\
    Glass bottles.\\\\
	Half-full and Half-empty. Clanked from side-to-side.
	Rolling past and right into each other; their insides
	swashing up and down like a ship's
	rum on a stormy night.
	And just like the oceans thunder....\\\\
	Rring ring! Rring ring!\\\\
	My ears were met with a heavy thud.\\\\
	Then a gristly crunch.\\\\
	And a loud crack.\\\\
	The wind swept up the crime-scene, blowing away bits
	of glass to the side and whistled away as if
	nothing had just took place.\\\\
	At that moment in time, I could have been only praying for everything to stop.
	For my room to go back to normal. For morning to arrive. To just wakeup.\\\\
	I wanted out.\\\\
	And fast.\\\\
	My eyelids were two tents, pegged down, and flapped about amidst the chaos.
	\\\\
	\textit{Huh?}
	\\\\
	\textit{They won't budge.}
	\\\\
	Left eye.
	Shut.\\\\
	Right eye?
	Shut to.\\\\
	\newpage
	Try, as I might no amount of eye scrunching could pry
	open these shut eyes.
	I began to imagine every possible way someone \textit{could} open their eyes:
	\begin{itemize}
		\item Maybe a surgeon making a careful incision with a scalpel into the folds of your eyelids
		\item Or what if a mechanical gently unclasped your eyelids with an ancient pair of pliers?
		\item Or how about  a wizard making you drink a potion that would magically make you see again
	\end{itemize}
	SHUT.\\\\
	They were 100\% shut.\\\\
	I gave up and waited. Waited for it all to stop. Waited to
	drift back to bed and dream about cats and hot water bottles.
	That dream never came and my bed which had been sitting patiently
	in the furthest reaches of my room soon to began to give
	into the alarms demands.\\\\
	It began to stretch.\\\\
	Then it sank.\\\\
	And slowly began to shake and slump; dancing to the alarms metronome...\\\\
	\textit{This is ridiculous.}\\\\
	For starters, I couldn't even see but I could already picture
	the sheer amount of mess I'd be needing to clean up.
	With a strong resolve to escape the clutches of sleep, I began
	furiously wiggling my toes and mustering all my possible strength
	to form an oddly shaped ball with my fists.\\\\
	After what seemed to be an eternity, I pushed off of
	my sprawled out blanket and rested my limp body onto my
	headboard. My eyes, were still shut but I was certain
	I was \textit{somewhat} sitting up.\\\\
	Creeeeek.\\\\
	Wait, what was that?\\\\
	My bedroom door burst open and I felt an invisible force
	loom over my body and begin to peel my eyelids all the way
	back to the beginning. The faint warm glow of streetlights
	reflected off pellets of glass was becoming clearer.\\\\

	A large rate of some: thin, soft, whitish cloth-like substance began
	threading its way through the rails of my headboard; teetering
	cautiously to my side.\\\\
	Dawn hadn't seen where \textit{it} had come from but even in his
	immobilised state was wise enough to shield his mouth with a single hand.
	To the far-far corner of him a sprangled linen blanket had disappeared.
	Above him, hanging off of the ceiling with its spindles, rested a the
	To the far corner of him a woven linen blanet twisted and folded and slithered
	up his calf, over his thigh and over his chest and finally rested; teetering
	on his left eye.\\\\
	Almost as if it was alive, I could hear the moaning and
	clunking of springs. One by one
	rails and springs began to lift up.\\\\
	``Noooooooo'' I screamed.\\\\
	I was being folded in!.\\\\
	Shouting, was no use as my voice became an incomprehensible muffle
against the sheets.}}}\\\\

\Large{\textbf{
	Without a thought to spare, I grabbed both my knees and tucked myself into a ball.\\\\
	\textit{From someone else's perspective,
		it would look utterly stupid, maybe cute.
		A teen locked under his blanket stuck in the fetal
	position, but no one was watching.}\\\\
	Now, being rotated up and down side by side and free falling.
	I attempted to extend my arms and legs as far as I could but couldn't
	help but flail like a duck as I was falling with incredible speed.\\\\
	This is where the nightmare stops, I thought.
	THIS is where my breathing kicks in, and I wake up in a cold sweat.
	Dreams always leave it to the scariest bit to make it extra
	breathtaking.\\\\
	Haha right?\\\\
	Like dropping a fly into a great big vat of jelly,
	the soft duvet folded around him and swallowed him whole.\\\\
	Left, was no imprint on the bed; no sign of disturbance; no nothing.
	The only clue as to what had happened that night was the wreckage of the room.\\\\
	``Ooof''.\\\\
	My screams fade out and are replaced with quick footsteps and the
	whizzing of cars. I breath in slowly, breath out slowly.\\\\
	When he fell from the sky, his brain prepared for a crash landing.
	Yet it turns out, the only difference between a crash landing in a dream
	and a crash landing in real life was the way he reacted.\\\\
    Muddy creeks and channels, brownish rotting wooden walls and beams, cranes, tugs, big and little ships.
	Restaurants selling good meat and fine chinaware.
	\textit{The city's surrounded itself.\\
		Mute-grey sky rises, clad with concrete armour
		and lined by rectangular eyes; litter the streets.\\\\
		But never seem to end.\\\\
		Busy bodies with airbrushed faces brush past you,\\\\
		Only to fade away round the bend.\\\\
		A whistles been blown, slicing at the blanket of day and a taxi
		arrives.\\\\
	When will it seem to end?\\\\
Follow these streets and you'll discover the web pumping blood to its heart.
\\\\I flick through the map on my phone, taking the occasional upwards glance to
	confirm my whereabouts. When, my eyes accidentally lock with a thin
	bespectacled man walkign down the boulevard. In an irregularly striped suit..
	Hoping, he could direct me to where I need to go, I decide to match my pacing with his\\\\
	He walks faster.\\\\
	I walk faster.\\\\
	He walks faster.\\\\
	I walk faster.\\\\
	It goes on like this for a while
	and I start to see a thin bead of
	sweat trickle down the mans forehead.\\\\
	``Hi, I was just curious if you knew wh-\\\\
	``And what business do you have tailing people'' he snaps,
     cutting me of. ``Do you get a kick out of it'' he asks, now digging
	 a pointed finger into my chest. ``Oh God, you better
	 not be one of those perfume people.}}








\end{document}



