\documentclass{book}
\usepackage{geometry}
\geometry{a5paper, left=20mm, right=20mm, top=10mm}
\begin{document}
\chapter*{You exist, in my mind}
\begin{quote}
    \textit{I was 7, when my fear of the night first began.\\\\
        A child should sleep on their bed.\\\\
        Not under it.\\\\
        But just to make it clear, I wasn't scared of the night. In fact, I thrived during the darkest of hours and revelled when the midnight clock rang.
        I wasn't scared of the night.
        No, not the night or the monsters that hid under my bed.
        No, not the night and all the dreary thoughts that would enter my head.
        Sleep.\\\\
        I was scared of sleep... absolutely terrified of it. I hated everything about it; from the false sense of security a dream gave you
        to the feeling of being ``alive'' a nightmare gave.
        I hated everything about it and all the lies told about it, just the word itself was enough to throw of my whole mood.
        Thus, I can justify my hatred of sleep but not conclude it, I suppose it's been long enough for me to brush dust of old memories.
        Very well then, this is my story. Of a different world and a different time when the world was ghost-quite except for the crack of dawn and when problems
        started as quickly as they vanished.}
	\end{quote}
\chapter{In this world, we have no-one}
\begin{quote}
The alarm bell rang.\\\\
Rring ring! Rring Rring!\\\\
Two giant arms and two steel fists were cocked back like a revolver; ready to fire their empty rounds - into empty space.\\\\
Rounds ricocheted of blank walls and bounced around in Dawn's ears; rattling the ins - and outs of his skull.\\\\
Post-it notes.\\\\ Tacked to the walland decorated with detailed drawings fluttered towards the floor; taking a bow as they were reduced to mere cinders.\\\\ Glass bottles.\\\\
Half-full and half-empty. Clanked and clanked as they rolled  past one and other. Their insides swashed up and down like a ships rum on a stormy night.\\\\
And a glass picture frame.\\\\
My eyes were met with a loud thud. Then a gristly crunch. The wind cleared away the crime scene, sweeping away the loose shards of glass and whistled as if nothing had happened.\\\\
I could have only been praying for the torture to stop, as each and every vibration creeped its way up my spine. I lay stone-faced,with my eyes and body facing the side. Waiting. Waiting for the ringing to stop.\\\\
It never did and my bed which had been sitting in the furthest corners of my room soon began to give into the alarms demands.\\\\
Stretching.\\\\
Sinking.\\\\ And slumping to the alarms metronome.
\\\\ *I was soon to follow
 \end{quote}
{The city's surrounded itself.
Mute-grey sky-rises, clad with concrete armour and tattered with windowless stares.
They litter the streets at regular intervals - but never seem to end.
Busy bodies and airbrushed faces brush past you - only to disappear, past the bend.
A whistles been blown; it slices at the thick blanket of day.
A cloud starts to brew, deflecting thick golden tridents of ray.
A taxi arrives - going round a busy street that the driver knows wont end.
The honk of a horn.
Red light.
Red light.
And a cop car quickly arrives - only to disappear past the bend.
Follow this maze of streets and you'll discover the web of veins pumping vitality to its heart.}

\paragraph{\textit{I flick through this map on my phone, taking the occasional upwards glance to confirm my whereabouts.
When, my eyes accidentally lock with a thin bespectacled man walking down the boulevard in a striped suit.
Hoping he could direct me to where I need to go, I decide to match my pacing with his.
\\\\He walks faster.
\\\\I walk faster.
\\\\He walks faster.
\\\\I walk faster.
\\\\It goes on like this for a while, before I stop to see a thin bead of sweat trickle down the mans forehead. As I aim to resume my following of the strange man I notice he's stopped abruptly.
\\\\``Hi, I was just curious if you knew wh-
\\\\``And what business do you have tailing people'' he snaps cutting me off. ``Do you get a kick out of it'', now digging his pointed finger into my chest. ``Oh God, you better not be on e of those perfume people.
\\\\``Oh, no no no'' I chuckle. ``Just wanted to ask if you happen to know where Silver Solicitors is?''.
\\\\A look of annoyance furrowed his brow and he begins to let out a lengthy sigh. ``Why yes, I happen to be their president and would you like a guided tour'' he sarcastically scoffs while walking of.
\\\\``No, I work there'' I reply, smiling idiotically.
\\\\Whatever, I had said seemed to struck a chord with the strange man. The expression begins to leave from his face and the curls of his lips begin to purse up.
His suit cuffs remain glued to the side and I can hear the starch in his suit begin to shrink.
A moment passes.
Then another.
I'm tempted to interject but before I can, I hear his shoes make a quick 180 degrees turn and I'm face to face with the man.
\\\\They say eyes are the windows to the soul, but for me his eyes are just bags of bleach and his face shrunk to the bone. His nose is sharp and his hair brushed to the side. As our stare-down continues, I can almost make out the sharp shrill of a woman and the sudden screeching of a car.
``Look, if you don't know it's okay thanks anyway!'' I gleam back.
\\\\``What, no you can't be here I-I-I watched them b-b-bury you!''.
\\\\``Bury?'' I chuckle to myself. ``Well, how can that be I'm here, look you seem to be in a rush it's nice to meet you and I'm sorry for the emm tailing'' I say, reaching out to shake his hand.
\\\\I reach for his hand, but its stapled to his side, I reach for the other one and find it unstapled. I swing it merrily up and down. A look of horror consumes his face and white threatens to swallow him whole.
\\\\Screeeech.
\\\\There's that screech again.
\\\\My eyes scan the scene, but there's nothing to see. I return to my handshake, when I realise I was holding on to nothing. As my eyes return to meet the mans, I see a thin angular frame become a dot in the horizon as a man begins his frantic run.
\\\\The fuck was that about, I mumble relived that I can finally drop the nice-guy act.
\\\\No wait, forget that thought.
\\\\What did he want to say?
Letting curiosity get the better of me, I chase after him for a second time.\\\\Tigthness begins to build up in my suit and I can hear the click-clacking of my shoes against city tiles. ``Wait, what was you gonna say'' I yell out, my voice fading in the distance. As the dot becomes smaller and smaller, my breathing becomes heavier and heavier. I think I see him and the-\\\\Smack-Bang, like a bowling ball to the face. My nose is swarmed by a rancid smell and my eyes begin to water. Sealing my mouth shut, my eyes are met with a horrid bright blue neon sign.\\\\WELCOME TO SMOKERS LOUNGE! Smoking prohibited outside of lounge.\\\\``Smokers lounge'' I tut to myself forgetting all about the strange man, ``anything but a lounge''. It was one of those dingy locations I had seen highlighted on my phone, so I knew I had to be close. ``Filthy, filthy, filthy'' I mutter as I walk towards the sign. Mist forms above my cold breath and I backtrack a few steps.\\\\All around me are different walks of life, huddled together in one large group. Blue-collar, white-collar, red-collar yep they're all here. To each their own, I say but if it wasn't for their wide-eyed smiles and gigantic grins I wouldn't have made anything of it. Large groups of men and women are sprawled across a single small patch of grass. Each of them huffing and puffing large bellows of smoke out their mouth's. Office worker, construction worker, office worker, sanitation worker. The ties on their suits and tool-belts on their waists all flap fitfully in the wind as their owners continue to smoke. They're huddled as if they were a colony of penguins clinging to the last remains of winter warmth.\\\\Yet....\\\\This crowd...\\\\ They're so happy!\\\\I can make out their middle aged banter and chuffed expression through the waft of smoke and there doesn't seem to be a care in their eyes. They all seem so happy, so young, so yout-\\\\Honk!\\\\No I say to myself. They've got yellowish stained teeth, black lungsand a burning hole in their wallet.\\\\Honk!\\\\ Another car speeds slips through a closing green light and the final waft of smoke disappears before my eyes.\\\\``Filthy, filthy'' I mutter.}}


\paragraph{A ballad of branches sat lurking amidst shadows.
They crawled and floated up into the air, clattering their skeleton bones against each other.
Their boney fingers scraped against the windowsill, each time the wind came by.
\\\\Tip-tap. Tip-tap.
\\\\It was like a signal and the wind was on cue.
It weaved through the crowd and wisped past needle-like branches, slipping an eerie-lullaby through the window gaps.
\\\\Rain pounds at the grass and an animal with a cloven hoof walks upon it.
The ground gurgles and burbles as its hoof sinks into the bequeathed ground and the creature gives out a deathly scream as it realises its fate. A crow caws and simply watches from a distance.
\\\\Rring Rring! Rring Rring!
\\\\The alarm rang for the final time that night.}
\paragraph{``Thank you oh so much'' I gleefully reply, waving of a kind stranger who had walked me to my workplace. I didn't know as to why I had forgotten my office's location but I thought it had something to do with last nights drinks. As I feel a drop of rain on my lapel, I quickened my pace and slipped through closing company doors.
\\\\Once inside I put on a smile and casually headed for the elevator. The air inside was warm with a hint of perfume and I pressed the 23rd button for the 23rd floor.
}

\paragraph{
An ordeal through hell itself; 10 rounds with the king of the nightmare world and an unstoppable alarm.
``A silly smile snuck is way onto h-''.
``What caught the eughh eye's'' he mumbled.\\\\Thump!\\\\Falling ever so gracefully onto the cold hardwood floor he remained. Oblivious to the past sounds of the alarm, he remained. Still muttering those same lines.}
%Wakes up from the dream





\chapter{In this world, there's an awful wind}
\begin{quote}
\paragraph{I laid still.\\\\
Breathing in slowly. Breathing out slowly.\\\\
``How long was I out for}
\end{quote}
\end{document}


