\documentclass[12pt,openany]{book}
\usepackage{graphicx}
\title{\textbf{Darkness Knocks}}
\author{Chris John Amby}
\begin{document}
\maketitle

\begin{quote}
\textit{"And in my passing breath, through
the extremeties of my eye's, had I seen
the true unpreserved beauty of this world. How
grotesque a rose was and how the raw sunlight
would roll n trample over newly formed grass.
And it was then, I was truly on terms with the world.}\\
\end{quote}
\newpage

It was a country that rained, always rained and I preferred it such that.

All carriages were to be stopped - then searched
by order of and all trains weren't
to pass through until 12 PM approximately.

Above me hung a sky, horribly drawn really,
dialled down to shades of radio-grew; its
thin threads would continuously float past me, coming undone
and

"Now this class, is a genuine Giorgio Armani
painting of the serande of 1862, Can anyone tell
me what the clouds symbolise here?

To be truthful I believed the whole art thing,
the modern art thing was a sham. A well thought out ponzi-rich-scheme
to get people out of paying their taxes.
more than splodges of paint on a clean artist's
platter and that the world
And the world seemed to be wrapped up in some state
of - constant involvement.
Where I was conveniently placed within earshot.
I would have it no other way.

No, today was the 29th of February.
I was one of many but the collective
output of Britannia's finest universities. I was
ready to be signed - and shipped of, to one of the
many yuppie office cubicles, safely
locked up in the big city.

Having contributed my share to the state's
parenthood. It felt only fitting, with
much boyish glee, show Father my final university
scores. He had insisted, that I- age 12,
sit London's toughest of secondary
exams and be it no sooner, was to realise,
that he had fostered a child who shared
little-to-no-interest in the scholarship
rat race of his.

So if poverty, all the worlds suffering
and the devil himself, had collectively
formed at our doorstep. He was telephoned from
work; told to keep a cool-head and let known
- his "son" hadn't the guts to enlist
in this great teutonic exam after all. That he had
withdrawn and with no prior warning
removed himself from all
exam lists for the upcoming month.
For better or for worse, his eyes never really
met with mine anymore, except when guests
arrived and he toasted me the occasional
innocuous shine. So, after many years, of missed
fatherly.. Oh something. I became immune
to man's need to invest himself in hypothetical
discussion.

In the latter of my fraternal years, I was
due to visit one of England's most
prestigious boarding schools - to which I did.
And it was then. That I learned. I had no place.
Or interest, in high society.

It felt all to easy, to emulate wealth
in London. Especially, the Jews
who could trace their roots back
no less 2000 years.
It was the capital after all and being
adorned with Her Majesty's watchful stamp,
there were always great glimmers of poverty's
mixed with glimpses of fine grandeur,
dancing the sooty night away. Given this,
I Thomas Amby have never felt more foreign
to this city in my life.

The newfound school, was a grand building,
encompassing several large acres of land, its main
hall jutted out from the neat
mini-buildings to its left and right.
A large rugby field sat past
the school, with acres upon
acres of forest scrummaging
in from behind and lavish dormitories flanking
in from the left
And upon arriving, I was
assigned a host, a "buddy" to speak. He
was 3/4 of an inch taller than me - but -
perfectly chiselled and gave of sort of a
greco-roman appearance. His name was Will.

It had rained horribly that morning,
and under my gratitude, had I stowed
a mass-production pen,
directly into the heart of my blazer,
only for it to spoil - And bleed,
all over the inner lining of my
suit. So it was decided that upon
departing from the coach, equipped
with three of five essential items:
an ill-fitting black suit, oil-stained
hands and frizzy dark hair. I was
to feel as though, I had come out of the
ground, than my own respective school.

It wasn't my shyness to the world's wealth,
or better yet my lack of exposure to it.
Nor was it Will's friends, with their
long grains between each chortle or
the snobby boys that tethered past you
as if you was a vestigial twin,
that through some horrible accident
had become stuck to one and other.
No, it was something else that had left
an impermeable stain on my young
and impressionable mind.

Before the new year, I had gained
a fixed interest in all things mens-shirts,
so after called homeless-looking by
a coloured fellow at school, I took
it upon myself to stake out a staggering
amount of shirts. Fabrics, were mostly cotton
or linen. And no matter the season
all shirts were long-sleeved.
I wasn't hurt by the way, and then it
was more of an insult to our city's local
vagabond community.

At the same time, but a few months prior, I
started to fall for a fair skinned girl.
I did everything correct. Wear period-appropriate
clothing, use the right perfume, hold the
door open for her, listen to her
problems, sing her son - yet no gesture of mine
was ever seen in goodwill.

Through the course of my final academic years,
I developed what Chief Army Medical Officer,
Major Charles Lee Boeswurp could only
describe as, "an incurable and unreserved
scorn, to every next man and woman I was
to meet". Yet one man was to slip from
my reel of judgement.

Akbar Ali, second lieutenant in command
of the poofta batallion.

This was only partially true, but Akbar
like all us others, had contributed
his fair share to the war effort.

So I'll start again.

Akbar. Yes Akbar, was exempt. "Akbar, swaggers
round the corpses of the Hun, revolver
dripping with black smoke,
his heart locked up forevermore
in young ecstasy" is what his platoons
men would choristically repeat, with
the staff sergeants parade stick
teetering dangerously close to
their shined shoes.

To me Akbar, was nothing more than
a democratically elected dictator.

In my worst of temperaments, I snapped
and yelled, ``What the fuck,
is it you want? Sniff, Broads, Money?
A seat in the bloody war room, oh wait,
your own fucking island seated of
the coast of Galipoli?''.

Sniff, was what the lower ranks referred
to as what I thought to be cocaine.
I knew Akbar wasn't a druggie
and putting him on bar with them,
seemed to be my only regret of my
stint inside the war machine.

"Oh I don't know.. You see! I want
something that isn't thi-

This annoyed me to a great extent
and I was just about done with
his sort of character. But just
as all moths, are due
to set sail for light in the morning
and return in the night to dip
their wings in tender flame,
this only drew me closer to him. I knew
what wasn't this. And I knew never
to ask again. No-Akbar, had
turned alright in the end and I made
sure that all archives published
in his name were to be - kept
accurate and factually honest. And
if not for her, well then I'm sure
his character could be taught
in some.. I don't know rudimentary
junior officer's seminar. He was a
gentleman, in every sense of the word,
capable soley for her.

As the war was nearing closure,
I became prone to assign utility to each
and everything I was to do. No matter,
how infinitesimally small it seemed.
I took it upon myself to pull others
from the wreckage of war, extract information
from them, and leave them to drown if I chose
them if need be
to. I went on a religious pilgrimage, spent
several days in the wilderness, understood
to which all stars owe their light to and
realised.

I am not who you think I am.\\\\

\textbf{Chapter 1}

Each morning, I contributed to the growing ashtray
army, watered all outdoors plants, fed all outside-birds
and checked outside.

A letter had arrived. They always arrived - addressed
to three. Amby, Akbar, Shelby. And each letter was posted
three times -to be exact and to three separate addresses.
Akbar, insisted that's how our mail
ought to be sent, ``You know old bean, in case of a sudden
dire emergency'' played his voice in
old-timey antipodean recording. I could have sworn
there was a fourth name. But it ended in
-by and something was written over it, so it
didn't strike me as strange.

Some plants required feeding only once or twice a week but I
still would fed them. I would use a pipette, or
a fountain pen syringe (made
for refilling) ink cartridges, if I didn't have one - I always
thought ink converters added too much
complexity to a pen. I would
add a drop of water to each leaf,
so that no one could go hungry.

The prettiest of birds was the
robin, not because of its
sparkling or wings but because
it fought of all the other birds
and didn't take shit from no one
not even me.


I escorted the letter, to the living
room, where it sat. Alone and slung
over an empty armchair. And it wasn't
until I was amply satisfied with
this morning's press that I made
the decision to cut it open. I was
looking for a fountain pen, the
drawers of the houses were all
filled with packing peanuts
or newspaper clippings,
so when the police wouuld
eventually show up
and ransack the place, their
ordeal would slow down by 1 minute.
A clipping I saw read

The letter was a careful shade
of cream and I was more concerned
with the red of our fireplace
than its big bold type.
The font was a sans-serif,
Times New Roman most likely.
Powdery
white coals flickered as my eyes
trailed the letter's type,
I mused at the thought of
the fireplace swallowing
the room whole.

So I looked upon the letter
for guidance.

\textbf{BAIL SET FOR Mr Percy Shelby
12/11/1920}

I threw the paper in the fire.

I quietly exited through curtains
of dawn, out through flowery
fields, in an automobile
and back once more into fading
city spotlight.

In this dog-eat-dog world,
there seemed to be no place
I seemed to call home more
than the hideout of XYZ. This was
the Cradle of Judah, where
the walls of Jericho
containerised everything.
Where the souls of empty men,
came to hang their hats, wandering -
before being whisked away to wherever
else. Where darkness
knocks on the door of each man.
Subsequent smoke rushing in through
the pores sots, stumbling through
the thick air, seeing their own hands
being sieved into the sooty air.
This was the last outpost of Ancient
Rome. From ash-to-ash, dust-to-dust,
bone-to-bone -no one seemed
to stay for too long and everything seemed
to break on its own. A place,
so destitute and overdue of all
things concerning natural-disasters -
I understood it grew on to me like a
vistigial twin. Airbrushed faces,
mute streets, clad with windowless
stares, no longer bothered me.
Darkness too had knocked on my door.

The general goods store which ran beneath
an old disused railway, was a large shop
- really. A thin strip of concrete,
that I had been following gave way;
several holistic herbs had began
to root in its sides and the strip later
meandered safely around a street corner.
An old sofa was positioned 3/4 of
a way down the road, opposite,
springs hanging out and all. Adjacent,
an old grandfather clock
was on watch, standing
to the door, vigil with both
hands stuck at 11 - its grand
presence ushered an
evermore need to be inside,
especially in times such as this.

As shop bells rang, a scratched-up
head turned halfway to the side and
greeted me with a half-assed
smile. "Smart this copper".

``No'' I corrected, ``stupid you''.

Fifteen minutes prior, to last
night's events, Mr Shelby in
a habitual drunken manner
had gotten hold of a telephone,
rang up the dockyard and
gave advanced notice that under
the seventh seat of every isle
in a ship, was to be a bomb
so deadly that it was capable
of wiping out a... And wasn't
to safely undetonate it until
he was granted immediate passage
to Papa New Guinea and guaranteed
safety from hungry human cannibals.

If only he was to know, a certain
ship had happened to be transporting
a Mr Winston Churchill, Perhaps,
then the events of last night would
have transpired differently. And maybe
it wouldn't, I was affected
indifferently eitherway.

One arm of his was busy with a basket of goods
and the other still not sure what way to go.

I ignored his indecesiveness and thought aloud,
``My name had always precedented first,
then Akbar and then Shelby'' and it
was that sentence that lit the day's
eternal smile. I knew it sounded better
the other way but it was indifferent
regardless. Perhaps, its for letter bombs I
finally said. the three seperate addresses,
that way he could arrange disposal
of both of both of us - at any time. I chuckled.

After a brief laugh, I resumed my place in the
mortal world, only to see Shelby rummaging
through a crude-looking magazine, turning it
upsides-down and then sideways, all in a routinal
manner. A woman was plastered on one of the pages
orally imbibing what I refuse to describe. Her
red eyes looked deep into mine.


\newpage
\textbf{Chapter 3 - Notes}\\
1. Men came in and went. But the
men in suits stayed. An audible
hush fell. And we were all seated.\\
2. It looks expensive I said. Yes, Shelby
muttered obviously oblivious to what
I was referring to.\\
3. "Ah this is the mark of a man,
who is in complete control of his
material" he beamed at me.\\
4. Woman leaves. She had broken
him like glass.\\
5. I had distilled my words
into a fine cocktail/scotch
and was ready to dish it all
out on him, When I felt
a cold and frail hand place
itself neatly over my shoulder
lape.\\
6. The slipknot had passed
and Akbar had returned.\\
7. Look, she's waving at you.
Shelby is very happy. No, quick
reply. She doesn't know who I am.
I quickly muttered.\\
8. Red-churned eyes.
9. You know I was just talking about Shelby, I never notic-
He's dead I said, with growing ensemble.
I tend not to look my best in death. Your not dying I said,
yes ia m.
Her friends made fun of her for talking to me.
I want you to be My gatsby I sulked
I cant
Why not.
There are some things I want you to know Tom,
I dislike you. I never liked you.
But I don't hate you. I think a man like you
carry8ing around a conviction like that
ought to be made an example of, perhaps in some
rudimentary junior officer's seminar.
Nouveau riche
If theres a way in theres a way out
he said dangling keys and a wad of fat cash.
we read a collection of artificats.
it was a social commentary,
i concluded one liking of morality
for everyone and one
for him.
lets rifle through his things
why not i hesitantly replied

dear mohter,
theres something i want yopu to know. I killed a man
I didnt regret it one bit.

i gathered my things scribbled on the chalk board.

i slipped on the coarse rough and scratchy tie
and just like akbars
wealth had insulated him from the troubles of this world i put on my tie.
i closed my eyes and in the extremitys of their
corners saw the world in a beauty I had nver seen before.
Some fine days later i awoke in a garden saw god george herbert
:
Roy was such a maths nerd and
I always had to bite the inside
of my tongue, to stop me strangling him.
at him whenever he did one of his..
``don't say 360, when actually
you meet 180 a full
circle gets you back
to where you started, whereas
a 180 is moving in the opposite
direction, I don't love correcting
people so I don't often say anything,
but I hope you learned something today bud.
Look, just call me.
last time i called you didnt answer,
then knock,
what at the house, he said house like it was haunted ha,
las time i knocked, you werent there it was like no one was there,
THERE IS NO ONE THERE, YOU DIBSHIT MORON.
your right patrick, there is no one there.
\end{document}
