%%%%%PREAMBLE%%%%%
\documentclass[19pt,openany]{book}
\usepackage{microtype}
\usepackage{ulem}
\title{\textbf{D}ar\textbf{k}ness \textbf{K}noc\textbf{k}s}
\author{In honour of \textbf{P}at\textbf{rick} Bateman}
\date{}
\begin{document}
\pagenumbering{gobble}
\maketitle
\tableofcontents

%%%%%CHAPTER 1%%%%%
\pagenumbering{arabic}
\chapter{Rabies Fox}
Hope is like a drowning dog.

Whose owner strands the
poor thing at the middle
of a frosty lake. With
a cinder block tied to its
leash, the block - now - resting
comfortably on cracking plates of ice.

And a bowl of kibble mirages
from the lake's edge, the dog now
scooting, pushing of the glass
sheet with numb-cold paws. Almost
as to think another man,
perhaps a passerby, someone kind
with a spare room - will take
it in - \textbf{and love the dog}, shouting
``Here boy, almost there!''.

Its food, the only reason
it's still moving, comes closer.
But the ice is soon to crack -
and the cinder block is soon
to follow - and the dog is
soon to drown.

Making this moment in the
dog's life, futile. Very futile.
And I'm happy sacrificing parts
of my soul, each day, to the demon
that warrants my comfort in New
York City.

One hour prior and you'd
see me outside some hick part
of town, heading towards 23rd
St.

The heavy worsted-wool Tom Ford
overcoat, sodden with rain,
now -remains slumped over a green
park bench, left for anyone's
take and my now-black chalk-stripe
Giorgio Armani suit, starts
to dry in the emerging sun.

Irregular glints from
various puddles, are catching
the velvety white
leaves of my Edelweiss
Boutonniere. And
although, I'm trying my best
\textbf{not} to look at it, my
face -\textit{has} been grabbed by
a deep section of still puddle.

-And although you could
say; my face is chisseled,
my skin is tight, my eyes
are \textit{still} young and
my hair is \textit{still} soft.
There is still, \textbf{no}
single point of attraction.

And as this horrible
unethical reminder of
my self-betterment program
is starting to erase itself
from fallen rain. Another
man would like to build himself
from the collapsed remnants
of my reflection.

- \textit{Some} - homeless nigger
is wanting to lurch towards me -
used Starbucks Stryofoam
coffee
cup in one hand (fresh
bright-red lipstick
running of its rim),
nothing in the other and
water beads from his brow
trickle on in. Either
he's a cross-dresser,
\textbf{or} its been
snatched out of an another
ladies hands.

His face, solemn, naturally
blurred by various warts
and ailments, creeps
dangerously close to mine and
a used cleaning rag wraps
tightly to the brim of his
forehead, leaving
an effeminate look to the
naturally skinny face.

He starts to say something - but
\textbf{I don't} catch it.

``I'm, -I'm-I'm ve-ry c-c-c COLD
Mister'' he starts - by spluttering,
like he's some shitty Honda
or a used diesel. Shaking -
perhaps expecting to extract some
sort of sympathy from me, the rest
only unintelligible murmur.

Wiping residual powder from
my nose, thinking whether
or not I've left the oven
on, or whether the Chinese
exiting the cab could be
my ex-girlfriend, or
whether I've forgotten to tape
{60 minutes} - Irritated. I notice
the bum is still standing.

``What'' I say sharply,
emotionless, with my hands
stuffed deep into my trousers,
staring at the guy's shoes.

``Amb-ba-ba Mista, you've got to
c-call me one.'', moving
closer, his eyes practically
about to pop out, like
he's just seen his entire
family murdered. And he grabs onto his heart,
as if in doing so will help his current situation,
``Quick Mista, I-I ain't got much time left''.

``Jesus Christ'' I mumble, not looking
at the man but at his gangrened toe
sticking out from thread,
wondering why it hasn't fallen out yet
and at his shoes, wondering where
had found them. \textit{And if he would
recommend them}.

And after a long - neglected - pause,
start looking side-to-side at the
various
passerby's wondering, if I was to hit
the man. Would they scold me?

``Do you even know what you're
saying?'' I continue.

``Amba, LANCE. CALL AN AMBA-LU-LANC-

Preparing a softening of my voice,
the readying of my tone and restraint
of my fist - I pinch my nose. And I
meet with his eyes. For once I'm trying
to compose myself.

``Ma-ma ma body. Oh my g-gawd''

Dissuade, annoyed, slightly
angry I start reaching into the belly of my
jacket - searching, for something
stiff and pointy to shut the
fag up.

And I discreetly fold a 20,
making sure no-one is watching,
slotting it into the Styro cup,
safe, where it will sit with
\textit{buddy's}: Lincoln,
Jefferson and Roosevelt.

Red is brushing up on Andrew
Jackson's face and I sense
he is starting to ease up a bit,
although the not-so-thankful
\textit{What the fuck are you doing?}
look comes of as a bit unwarranted.

Cataract. I think there's a cataract
or two in his left eye and a parasitic
worm thingy, fetal in the right.

He is now coughing up blood, and
something foul-smelling
and very chunky trickles down his
throat.

Raising my cuff to my nose, I trudge
on past him, muttering,
``Keep the change'' I exit the park hearing
the words, ``OAWHHH MAnnn''.

And I bump into someone,
who says he knows me - but
I don't know him.

And a nerdy white dude,
fat, unapologetic looking,
bearded, fat, is exiting
a GameStop on 24th, his
hand gripping a Nintendo
title - that looks vaguely
familiar to me. And his brown
sandals slap on against
white concrete.

And this is
all starting to remind
me of when I was 7 years
old and Mother had decided
to punish me severely.

The punishment for
vomiting this morning's
breakfast, which had
consisted of grey eggs
and sour milk was to have
my Nintendo thrown down
our apartment's dirty trash-chute.

As \textit{extra-punishment},
I was to hand over all
my games, their cases
and any assorted manual/slash
charger - all bundled into
the same creased Walgreen's
bag.

But I hid, my favourite game,
knowing full well
it's no use to me without
its designated console.
Thinking, I had gotten
away with murder, I diverged
some tears 0 knowing all hope
would not be lost. My save
files were still infact.

And my mother grabs me by the lapels,
knowing wiser, forcing the case open,
closing it, throwing it like it's
a frisbee at the wall - the case
shattering. And I retrieve the game,
walking over bits of broken plastic.

And I can no longer see the
plastic bag, as it falls
down 30 blocks of 70's soviet
looking stairs.

The school day that followed,
felt like my birthday because
I never wanted it to end.
And I spent time talking to
my teachers when the bell volunteering
to wipe the boards and
tuck in the chairs.

When mother, came to pick me
up she was gleaming with bags of
sweets and toys, in both
arms and told m e on the walk
home how she had rescued the device
before it was thrown in
the garbage collector An-

What the fuck was the point
of my punishment.

- God - \textit{You
could have gotten it for
an absolute steal, an
absolute steal} -if
used, my mind is now racing
and I bite sharply at
flies coming out of a bin.

Giddy but also ready with vocal disappointment
disappointment, I shimmy through sideways
traffic, preparing my lecture on the many
merits of
saving. His confused head, unable
to comprehend the words I
am saying or why I am
wagging my finger in front of his
eye is simply bobbing to a yes-no-yes-no
type beat, provided by Beats from Dr Dre and
the song I do not know.

I'm shouting at him, stressed,
frustrated, bit angry, that what
I'm saying isn't getting across.

``No, not good luck - here's some
advice - \textbf{YOUR} a \textit{fat fuck}, I wanna
gouge out your eyes''

``Hey thanks man, its actually
for my kid'' he says
and
the song which I now know
to be, \textit{Gangster's Paradise}
blares
from his headphones.

\textit{Tell me why are we so
blind to see, that the
ones we hurt are you and me}
is what I now hear.

This leaves me disappointed
and dejected and I continue
down 24th, soon to approach
Times Sq-42nd.

Maybe - he learned something - or - if
not who cares. I'm drawing
out the words I said to him,
trying to not
make my voice appear sad.

Reaching, the subway,
slightly earlier than expected
I lock eyes
with a hardworking Mexican
teen,
giving him my nod of approval.

And some punk
shoves into him, which
causes his
hands to lose grip of the
bun he's been working on.

I can hear him shout, ``Hey
ese, watch out man'' in an
accent I thought couldn't
get any more stereotypical.

And the once pig, once
chicken, once lamb - dog rolls
down somewhere
into the gutter, where
it will most likely
float into the Hudson river
or be chewed on by rats.

The man, not paying
attention is wearing a
dark ensemble. His jeans,
ripped denim, not sandblasted,
are held up with a loose
Hermès H buckle belt. His
shoes are designer, probably
Gucci or Louis Vuitton in perforated
leather with tassels and above
sits a darker, black -
disproportionate,
\textit{720 fill power},
\textit{DIST certified}, glossy
Moncler puffer jacket.
Which - is obviously, too
expensive and
ruins the outfit making
it look cheap. And he fades
of into the subway.

Directly opposite
a Glenn's pharmacy, is a
lone white
supremacist, balding, old,
semi-tall but strong-looking -
And he yields
a large white placard with
neat red
letters that read, ``With
Jews we Lose''  or was it,
``Whites for America''.
Either one, either one.

``Well'' I say rubbing my
jaw. ``I'm just not one for
the cause'' I shout through
busy traffic.

``Whaat'' he shouts, wind pushing
his eyes.

``I said - I'm just not one for the cause''
I shout back.

And a native American
woman, glares
at him, does nothing pushing
a baby in a pram -
who wails ferverously at its
birthgiver, hurling
various unintelligible insults
into the air.

Another hobo is
Wearing a
yellowy-white stained tee
- no jacket, grey
sweatpants with the word
NIKE smeared on the seams
in big bold type and
ripped leather velcro shoes
sits under a nearby intersection.

Where automobiles throw
coins and trash at the ground he
calls home. And he begins
contorting his skeletal
frame around a
burning trash can
desperately grabbing on to any heat
being let of from the
plastic flames,
extending his arm
and callused hands to
sift through the thin
layer of dirt-dust gravel
for something, just
something, to shield his
eyes with. The plastic flame,
knowing this, shifts
direction,
causing him to
cough - seek cover - cough and
covers a pair of burning red-eyes
eyes in a thick black blanket of misty haze.

Another hobo, who MAY have
been a gambler in his past life,
is wearing a decrepit banker stripe
Dolce \& Gabanna double breasted
suit, with side vents and looms
non-chalantly over side-ways traffic.
Hoping to hitch a ride home. I'm rattling
my fucking brains here, wondering
as to where I've seen this guy before
and it hits me. He was my former
teller at Trump Plaza

And I imagine he sings,\\
\textit{
	I was never homeless,\\
	I had a homestead,\\
	5 children, that I fed,\\
	Each one, I put to bed.\\
}
``Hey John, it's me Preston'' he shouts, waving
his entire body around, the pong of
cheap cologne slapping me - I never even called his name.

``I'm not John, I say'' smiling back, with cold feelings
devoloping in the back of my head.

``Well...'' he says raising his arms in a \textit{you've-got-me-look}
``Look I really need a rid-

The traffic picks up and
various hardbodied Romani
Gypsy woman emerge, who try
to sell me flowers,
picked - illegally from
various different
9/11 and Iraq war memorials, that I'm impartial to.

And I swat them away,
with my back poised straight
observing a group of negroes
who've staked
propietary claims
to rows of city bench's
just outside a 711
and sprawled over uncomfortable sets
of steel I notice several rounded-
spikes installed on the ends of
each bench - most likely
installed to curb the city's
rough sleeping epidemic. And
the men sit and gossip.

A few feet up seems to be a buddy
of theirs,
who shouts loudly

``Man,
this dat SAME drug that killed Michael
Jackson'' pointing openly
to a lit joint in his right hand. An orangey-red ring forming at the end of the joint,
which appears to be wrapped from a
variant of the original RAW classic
rolling paper.

The group paying little to no notice.

The sound of my heels on rough concrete are masked by
youth's shooting hoops at
a nearby court, the rim having no net and
the ball soon to be run over by traffic.

That same homeless nigger,
that I gave 100 bucks
to? He's now spazzing out on the grass, 2
feet away from me. \textit{Is
this motherfucker really going
to OD next to me?} Is all
I can think.

``Hey, hey buddy'' I yell,
snapping my fingers at his
frozen face.

But he just stares blankly at
my general direction.
Dude's system is probably
overloaded with methampthetamines. His skinny
sirloin
hand is posed like Michaelangelo's, \textit{Creazione di Adam}.

Foam dispenses
from the mouth, the froth generating
a deep and rich lather which
coats his skinny-smooth face in a layer of
one million bubbles each juxtaposed and some are
even shiny, like dish soap. And the guy's eye's
still frozen in place, convulse, pulsating - his mind
probably, no, must be thinking one thing. Whether or not,
I will call an ambulance.

The banality being, I couldn't
even if I wanted to as Cricket Wireless, my service provider,
has recently refused all payments from my account, due to
a series of suspicious payments from abroad. They
are also not answering any of my calls.


And he reaches towards me.

My Eagle Claw cufflink from
Fort Belvedere, silver with onyx ball is briefly in contact with his fingertips.
And he grabs on to the Luigi Borrelli, two-fold cotton, shirt's cuff
immediately staining it in a deep crimson red.

I quickly pull out my gun,
which is a Colt 1851 36 calibre and yell quietly, ``fucking
stay six - feet
away from me.''

``You got that?'' he mouths yes, still frozen, the barrel
feeling up and down his mouth, I fire a warning
shot and a flock of pigeons flies of in the distance.



\chapter{Kissing Bus}
I'm now on bus,
on route towards the SoHO part
of town, my cuff still red, my fingers
still shaking and I'm watching pornographic film on
the pocket phone - volume up on \textit{\textbf{MAX}}.

A guy is getting his cock sucked by a Thai woman, tall, no ass,
perky tits and the guy is buckling at the knees.

The woman is making unnecessary glugging noises even though
the cameras stopped panning to her 5 minutes
ago and is now showing a much
taller woman -also Thai, with a tasselled whip and 12 inch
Jimmy Choo platform heels. And the lady starts whipping
at the guy's balls.

Kneeling due, to the pain and shrieking as she steps all over
his toes, leaving them bruised battered and purple she laughs
into the camera, as it pans to a shot of her spitting
a fat loogy in the guy's mouth.

His shrieks of agony, only glorified and projected
by this red rubbery ball thing, held
in his mouth with two leather straps and at this point
I'm so worried that the guy \textbf{won't} be able to get of,
I -. Nod nervously at a kid, about 12, thinking he too realises
the woman's moans are deeply perturbing and I slam the screen
onto my thigh, wavering a sigh of relief winking at the boy.

The seat in front of me, empty,
half scratched with initials
of couples and dates
has an old sticker on the back
of its headrest, advertising a
Lulu's massage, a name I should remember
but - I have no recollection at all.

Behind me - an old lady,
confused, frail, White
- American looms over the seat
behind me,
adjusting her eye-glass, trying
to see a piece of the action.
And I think on whether
or not I should show her
the latest stash of cartel murders
that I have archived, maybe
\textit{Sinaloa} or \textit{CJNG},
\textit{Los Zetas} works
although their new stuff is pretty tame - but the driver,
a man in his 40s, Egyptian probably has something to announce.

``It don't go no further''

And though I'm unprepared
by the woman's genuinely
cheerful glare and the good deeds
I have accumulated for her
to look so happy. And the way
she is looking at me with two
tennis-ball sized eyes and
an open happy jaw, albeit not
whatever she's thinking of - I help
her get of the bus.

Exiting the portal, last,
I walk past this group of noisy
teens, dressed loudly. And I shoot
them all death glares
but their eyes are glued
to either pocket phones or passing
windows with bright coloured jackets
and similar coloured sneakers. I think a Footlocker
at 31st St.

A girl in their group,
listens to \textit{Poker Face},
by \textit{GaGa}.
And I know this because the
music's too loud. And the group
later poses in front of a George
Floyd mural on 91st, painted by immigrant artist
Ash Barker, all happy-eyed, flipping
peace signs, all wearing airpods.

And \textit{Lathyrus linifolius},
a herbal suppressant which wards of hunger, shoots pangs
of un-relief down my stomach lining. This is all because
I've been eating nothing but it for the past 5 days after
reading an article about it's dietary
effects on the body fat of field mice.

I now weigh, 224 pounds an impressive corresponding
figure for Men with BMI's of 27.4. And although
this number looks and feels colossal, I am very muscular
all round.

The enclave of land,
draws further and further towards me,
like a snapshot from the magazine \textit{Pride Weekly}.

Various new shops have propped up, with different
coloured pride flags sticking out from window-corners.
And multi-ethnic people are all stopping to talk to each
other, Fashion I'm guessing or what shampoo they use
for their dogs.

I touch my nose by mistake and
my fingers come back wet.

Women are outnumbered by men, 3:1 in SoHo.
I walk past men in moustaches, wearing large mink
coats holding other men's hands and going into
men's-only-bars. And I've accumulated a
sufficient amount of compliments, from how
well I'm dressed, how-formal, how-proper,
how-tuned I look.

The ones I care about
are all from Wall Street Yuppies, who
are all on lunch break.

The sun is hanging low and casts
its turning glaze over me and passerby's
who are otherwise all happy
are starting to stop, gather, murmur
and I start chewing nervously on a
dry-cleaners ticket and some wall street
jerk starts looking at me
like all I've eaten
for the past year or 2 has been
\textit{\textbf{XANAX}}.


Something is throbbing in my chest, wiping residual
snot from my nose, exposing
my nostrils to the now-cold-air,
taking
long calculated breaths, whispering
in a dental way, looking to my left and feeling to my right,
I stop at a salon to catch myself in one of their mirrors.

``You've had so much plastic surgery, I wonder
if it would even be possible to go back'' I start
to hear, from a raspy
couple walking behind me, and
the words,

``POSSIBLE TO GO BACK, POSSIBLE TO GO BACK''
quickly play
around in my head, trying to figure out which word
should be emphasised first.

And for a fleeting moment, I look past my reflection
and wonder if there ever was a time, where
I wanted to go back.

What I guess I think is a passionate
moment, I dig into, my jacket
searching for my gun - because I don't
feel safe.

Levying my fingers on the
trigger, a sense of relief
swoons over me and I loosen
the grip on its handle, retrieving
my hands from my pockets and flick
of sweat from my brow.

``You're a weasely little shit, aren't you'' a disgusted
sounding voice
parses out from behind.

And as the words, possible to
go back - possible to go back
can no longer ring themselves
out. I've just
understood that \textbf{this}, this
epicentre, is where all sin has originated from,
and the air above
me begins
to grow dark in a sepulchral gloom.

``We two, are seperated by
God, from God and when the end comes, we shall
be slain and served as food
for all those deemed righteous''
the voice behind me says,
calling out to me, in monotone.

And the woman behind me,
saying these cruel, cruel words
lifts her arms in an
\textit{I'm going to get you
look}, although this isn't
a movie and I'm fairly
certain her only intention
is to kill me.

As if guided by sunlight, hearing
the laboured voice of constructioners
egging me on, I look back - No, no time for that
and run through the darkening
street, my jacket flapping through the
wind like a cape my leather shoes slapping up
against new concrete and the woman
screams like a banshee - and the
voice follows me down my path.

The woman lifts her arms
even more
and gives into the game
of chase.

A dull thumping beat
is obliterating all
forms of monologue in
my head and my legs
are weak.

She holds both arms out,
and the skin on her
face, looks as if its
melted, then been reapplied
like clay, hanging loosely,
all her teeth are fully
visible though her mouth is
closed and what looks like slow
motion - she takes a jump
towards me and passerby's
are clapping her performance.

Behind her, behind
her body, looks
truly exquisite.
Azaleas are
creaking towards warm
pastures filled
with all animals.
And man
can laugh and play,
breathe without worries
of being hunted, eaten or taunted.

I find an unguarded bike,
raising my leg over the
seat which is too high,
not checking to
see if its rideable,
I start pounding on the
pedals, down the wrong side
of an one-way road.
And I see the faint glow
of the woman's face from the
bicycle bell - her nails - just
touching the rear tire.

As I'm forced of my bike, from an enormous
gale, knocking the bike into rows of new-steel
cars. Crushing 5 more tablets into my mouth,
oh my gosh, is all I can think as my teeth
chomp down on what I think is an ibuprofen.

My vision is all but one
enormous kaleidoscope of colour
and I've hit my head hard. So
hard, that I'm certain the pain
signals are delayed and my mouth
is teething in angst.

I hear the woman draw
closer and my heavy unwarranted
breath is being masked by the siren
of a cop car and I'm certain I'll shit
my pants if she comes any closer.

Realising, the sirens aren't
for me, thrashing on the rough concrete,
knowing I've fucked up my only pair
of black brogues, the woman's finger,
skinny -skeletal like
trying to pry my mouth apart,
her nails now clawing at
my tongue, a new-formed crowd applauding
her and I'm certain that I've vomited
back up some of the medication.

But an idea flashes through my head and
as her woman approaches my half-sprawled body,
perhaps readying to sodomise me pulling of
mirror-shined patina half-brogues and throwing them
into the air, she starts to fight with me as she unbottons
my jacket.

Remembering, \textbf{I am the one
with the gun} I quickly pull out the glock,
almost dropping it, fiddling with it, although
it's just \textbf{one-shot} to knock her out.

``Hey-hey lady'' I shout
snapping my fingers through
reindeer-skin gloves
but the sound is totally
muffled by a mix of
leather and warm sheepskin lining.

Almost wanting to warn her of
the impending bullet, so she
can escape to whatever cavern she
crawled out of.

Irritated, I continue snapping
until one glove
produces a rubbery sound but
the woman doesn't stop the rape.

``Look at me
when I address you.''' I start
to yell, in a sing song voice
then in absolute, yell
``\textbf{YOU DUMB FUCKING BITCH}''.

The short stationary burst of
movement ruins the drape
of the Armani suit, and
a blue crimson fiery ring is placed
on her forehead and the body collapses onto
my arms.

Pushing her off of me gently, her hair being
picked up by the wind, weaving into it like
they're sticks of corn.

I flag down a cab, running after the
Armenian behind the wheels, yelling
``Stop, Stop'' then proceeded
by ``holy shit, holy shit''
but he is driving faster than I can run.

And startled, from unwanted
glares that begin to accumulate
from onlookers, I
tear through my ostrich skin
wallet, by
Hermès, and begin
throwing crisp 20's at her,
most not even
reaching her
as she's like 50 feet away and
some even being picked up by the
wind, where they will most
likely flutter down somewhere
up-town.

And she lays there while a
puddle of thick brown blood congregates on the floor,
her hand which otherwise - Could aid her in standing,
struggles to grip onto the stuttering concrete
so it lies there, feeling around
the surrounding ground
for a while and then stops - revealing
manicured nails - dipped in
red french tip.

When I'm all out,
I quickly jog sideways,
careful not to work up a sweat,
back and forth across
upper 91st, pointing
my gun
at various stone-faced
onlookers, threatening
to shoot if the sound
level raises past 25 decibels.

The exodus, which I cause
provides me with sufficient time
to rush into a Wells \& Fargo,
I lock myself in a small
secluded cubicle and then
prop my back against its cold metal door,
exhaling endlessly.

After many hours
shopping in the mall,
making futile chit-chat,
antagonising minorities
tasting free-samples
of gluten free bread and
buying expensive perfume
I finally leave.

Opposite a children's
book shop, an incident
has taken place, from
where there is police cordon tape
and white sheets draping over
an unmarked woman's slumped body with
white
chalk surrounding her.
Unfortunately, there is no CCTV
where this incident took place
and I proceed with my day,
changing into a new Luigi Borelli
shirt I purchased for 95 dollars
at Macy's
leaving the old Borelli
at a nearby McDonald's
the cufflinks still in it.

Leaving upper 91st, amex still in hand,
this Ebola-looking nigger tries to sell
me his CD. Although I do own a player,
so I buy
four. And smile at him, taking his Instagram
promising to listen to them as soon as I get
home and high five him, shouting something positive.

And the puddle of warm stagnant blood
which starts
to dry, wets the wind,
her body fast-frozen
the white chalk conserving her remains.
And arbitrary bits of trash
whistle by me.

I meditate on what I had just done.

Realising
I would also need to discard my reindeer-skin
gloves, which are also from Armani.

Shouting, ``you stupid stupid stupid
bitch at no one in particular'' flagging
down another cab that doesn't stop for me, wondering
what would happen if all the LGBT flags in SoHo
were suddenly replaced with white-defeat flags, I fall
to my knees crying and a wan reflection is loosely
visible in a broken mirror.

Joining other bewildered officers on the scene,
of unimiganibale mayhem. And my mind pans over the scene.
There is no resolve.
\chapter{Apartment}
My head is heavy.

Unable to move, head no longer guarded by \underline{\textbf{\textit{XANAX}}},
head no longer guarded by me.

Chin cradled into stuffed giraffe gifted from Sarah, \sout{a} my
secretary from Pierce \& Pierce. The Omega \textit{La Magique}, is the only extension
of my body actively facing sunlight, which pours in through window-walls
onto the Matthew Hilton \textit{king}-sized bed and a throbbing
sensation pulses down my chest, whilst the sunlight creeps through
shutter gaps. Alligned into perfect panels on persian rug.

Arms, legs, sore - clambering onto plush
fur carpet by Gina Napoli, pulling an
Egyptian-cotton blanket
and Burmese-silk pillow covers,
all by Geneva, with me I lie
on the floor.
Dazed, unable to recover any
recollections from last night's
activity's I extend my arm,
clumsily trying to open
a bedside dresser. My slim-cold fingers,
hitting the brass knob several
times before, clutching, pulling,
gripping. My fingers rifling
past various fountain pens,
all by Montblanc, finally grabbing
prescription eye-drops.

The drops trickle down my face -
some going into my mouth.

Startled, I start
seeing yesterday's
Armani suit-jacket
on a mannequin, given
to me by a friend who works
at Hermès. Its trousers, hanged, on
a valet stand, given by someone who
works at Trump Tower and the shoes,
with its correct shoe-trees
neatly to the side.

And through
the loose eye-drops that drop
from my lash,
flecks of blood
are visible on its lapel. Fabric
and threads stick out making
the garment look like a horrible
scarecrow. Examining the weave,
in sniper position rubbing the
wool and silk lining
with two fingers, breathing
in it scent I look at where
the fabric's been torn then at
my own body.
But my bodys fine. And
I'm confused as to whether I was
the one, who put it on the mannequin
and if so why was there blood on it.

Pulling myself up,
my cock swinging whilst doing so
and hearing the
landline ring I answer it
without checking the senders name
and head towards the toilet with
a towel hoisted on my shoulder.

``PATRICK, PATRICK'' the
voice blouts out.

The room is black and gold. Mainly
black, some gold. Who my Korean
friend, helped design last fall.
Venetian curtains, are tucked
into the rooms corners,
exposing the room and its glory
to the many skyscrapers outlining
the city.

Realising, the voice
is belonging to Paul Norman, my close-friend
who I met at work, few years back I
go back to the landline, placing the
towel on its rack.

\textbf{``What the fuck happened downtown?''}

Panic. Desertion.

An odd tingly
feeling creeps down my nails and
I begin staring at my fingerprints,
wondering if any two swirls can be
the same.

Four compact discs, which
I must have bought are
sitting neatly stacked on a drawyer.
\textit{Perhaps a rare
artifact in my search for immortality,}
Carefully putting them in a protective
sleeve cover, examining the various black
cover artists, opening and closing
the case, thinking WOW this is really
cheap.

``You'' the voice blares in an
accusatory tone, ``were supposed to meet with our
Japanese friend's at Effes''.

And the unknown panic swoons over me.

Reruns of \textit{60 minutes}
are playing in the living room.

\textit{``Tonight's coverage is of an
11 year old boy, who shot his Neo-Nazi
stepfather, point-blank whilst
sleeping''} can be heard.


``\textbf{Patrick}, \textbf{Patrick} ehmm are you even
listening?''.

``Yuh, Uh, One second Paul,'' I shout back,
still staring at the black musicians.

``Jessica, Rosie - Natasha and
I are thinking of Nell's.
Jess is getting her hair and nails
done first and I have
a meeting with the Japanese. I'll put you
down?''

``Uh Sure'' not sure if he heard,
``Nell's?'' I shout back.

``Hey how long would it take me to
\textbf{die} from
this''.

Placing them in a protective sleeve,
next to the Michael Jackson section.

Something is rattling
from the landline. Pill probably.

There is music playing
from the apartment upstairs,
probably John Lennon.

And a mixture of Paul Norman's
voice and the televisions
is coming in through the bathroom door.

``Listen, Paul I'm a bit occupied.
I'll catch you later okay'' I shout
from the toilet.

``What? You're breaking up''

\textit{``Neo-Nazi Jeff Hall's son has
had a history of violent outbursts at school''}.

After an interim of radio-static I
hear the landline click.

I own an extensive archive of DVD,
Bluray, VHS, laserdisc almost every
film format except old film reel.
Because old film reel is very
flammable.

Everything is meticulously
organised in A-Z order
Shows, Movies,
Documentaries I particularly
enjoy are set as assignment
to interns who shadow me. And I
later probe them on what about
film/show moved them.

I am Not a collector and
anything I do not gain utility from.
I have my secretary, give
away and write it
of as charitable donations.

That night, I had a dream
where I was being killed,
slowly, by a small man-child
who I had insulted and not gotten
away with.

The closet I'm walking into has
A large Julius Caesar bust, on top
of a quartz pillar, I had
commissioned last June  directly opposite
me.

One side of the room is partitioned
for my many sets of bespoke suits
on steel poles. The
other for tailored off-the-racks, all
designer or Saville Row.

Then rows upon rows of drawers,
with clear glass cases, hold:
silk, wool and mohair Hermès ties.
All 180 bucks a piece.

Shoes, by John Lobb and
George Cleverly, too many too describe
are on shelves, mirror-shined.

In the corner, are pens
owned by Harry Truman, Richard
Nixon and Donald Trump.

And several large cedar blocks are
in the room to stop moths.

Putting on a Corporation
of London, charcoal grey
double-breasted slack-cut
suit, shirt in french
cup, silk-mohair
socks from Tom Ford and
Cleverly black brogues I
exit the room, flicking
the switch off.


\textit{``When he was taken
into juvenile hall,
he was so little they
didn't have shoes
to fit him
so they had to buy him a pair
of tennis shoes''}

And I dissolve into the sofa,
temporarily tuning into shots of the
now dead Neo-Nazi, Jeff Hall's
exploded brains and I switch
channels to a more cultural one.

But all that comes out from the soundbar
are eerie african drums and sweet preruvian panflute
and snapshots of different groups of indigenous
people.

A monk who killed and tortured various black protesters
but wasn't really a monk, just a bald
white-supremacist, who looked Thai
is being held in custody in New Jersey
and will also be the topic of next episode's
\textit{60 minutes}.

And at the front-lobby
of my apartment, the
man today is looking at me
like I'm an anaconda who's
just swallowed a large goat,
whose horns are still wriggling
inside of me. Like he's
some horrible part of my past,
who's been brought back
by God to punish me.

And I sign my name on the log.
\chapter{End of Month}

The remainder of the month's
days are uneventful.

I meet and confer with various
homosexuals, to discuss
what perfume is best to
leave a good impression,
whether certain shades of
brown can be worn for formal
occasion, to shave
with or against the grain and
other normalities.

Liane Williams, the escort
is calling me, asking if I'd
like to meet or whether
I enjoyed the Broadway show
we saw last Tuesday.

I bump into a faggot,
outside
a bar on 6th street,
some fat chinese wearing
horn-rimmed Oliver People's
glasses a brown-patina'd
atache briefcase by DH
Sanders and a beige suit,
by I'm guessing Hugo Boss. who
is wearing a pink and
blue polyester
bow-tie.

And I tell him, stretching my
jaw, exaggerating the
word love - ``I-looove-it'' stabbing
at the bow-tie with my finger.

When in reality I actually
hated the bow tie.

And I look down at my wrists
wondering if I were to
cut them of with a high-powered
chainsaw would I either \textit{A}
bleed to death, \textit{B} pass
out from the shock of not having
hands or \textit{C} run down
a one-way road screaming,
``I have no hands, I have no
hands'' over and over again
raising my arms at passing
cars, blood gushing out from
cartoon limbs coating frost-covered
 windshields.

I am still unable to get a phone
provider and also am now
unable to get a credit card -
not that I need one, just
that it's nice to have.

I also grabbed and french kissed a girl,
I walk past everyday. She is
startled and might file a report
on me or mace me next time. But I
have my wits.

\chapter{Personality Test}

``And how often do you think about race?''

``No''.

She looks at me sideways from
the monitor.

``No, I mean I never. Never think
about race''.

And she starts typing something.

``How often do you think about
gender?''.

``Seldom''.

``Age?''.

``Never''.

``And how often do you think abo- she
pauses, laughs nervously, ``Sorry
not allowed to ask you this'' blocking
her ears with cupped hands
saying, \textbf{ha-ha}.

``No please do'' I say confidently,
feeling an upper hand, although not
sure why.

``Patrick'' she says surprised, expecting
me to know something that is universal
knowledge, that the whole world and
its minions should know. ``It's -
illegal''.

Sarah, my secretary - a
little softbody who
just graduated from NYU, a woman
I plan on making a move on and one that
is capable at her job, stares at her
keyboard, maybe wondering why the first
row starts with \textbf{Q},\textbf{W},\textbf{E},\textbf{R},\textbf{T},\textbf{Y} or why
the space is so big.

I exhale her name, softly , smiling, ``S-a-r-a-h''
And I place my hand above hers, which
cups a mouse, raising her chin
to mine.

She doesn't really look at me and turns
the monitor to the side and the
cursor hovers over the sentence,
and I can almost hear
through the screens pixels,
in a singy-enquiry voice ``Are
you a homosexual?''.

\chapter{Dinner at Nell's}
``Alright...
what about college girls''
starts Timothy Price.

``Congested'' comments Van Patten,
rubbing his brow.

``No - a good athletic girl
is what you want, someone
whose pussy \textbf{needs} a good
stretch'' McDermott adds.

``Wants -guy'' Price corrects.

I'm sitting by myself at Nell's,
joined by Timothy Price, Craig
McDermott and David Van Patten -
all because Paul Norman's cab
broke down and the girls are late
as usual.

Mcdoofus is sitting cross-legged,
sipping on a J\&B, wearing a pale
blue Valentino suit, navy Hermès tie
and a Patek Phillepe watch. And I can sense he
is going to ask me something because
the way he has been uncomfortably
eyeing the Omega La Magique.

``So.. Bateman you've been
awfully quiet what's
emm, your type of woman''

``Jeez aren't you quick to
know McDermott'' Price
says coolly, folding up a
German cigar case.

``Well.. I mean'' Craig
coughs, ``lets \textbf{all}
be on the same page here,
what do you look for in a girl''
expecting the others to take him
seriously.

I'm a bit stumped by the genuineness
of his question not before
he adds, ``A little hardbody
no-less, easy women'' grinning
endlessly.


``Well...'' I say taking a pause
longer than I should.

``Go on Bateman, \textbf{blow}
our brains out here'', Van Patten
says pretending to have his
mind-blown with his fingers.

``I-'' start
by saying, unsure
where this is going to go.

``I like a girl
who has a clear career path''
I say crisply. ``
But also someone who is not afraid to
explore their options,
diversify in a way.'' I
stop, stirring
my martini. ``I like a girl who is
also not too sexually active - someone
who can share a common ground with me
- but not too common - so that
we lose interest and eventually fall
apart. Someone who is so desperate
for the lost art of male satisfaction,
she is completely oblivious
to the M2.50 caliber rifle, wedged deep inside
her pussy, which will send shockwaves
of pleasure up her spine
-\textbf{no-doubt}'' and I
finish my JB.

Something seems to have
been lost in what I say
and Price is looking
at Van Patten and McDermott,
who both look back uncomfortable.

``Anyone hear about the escort
girls-up North, who went missing'' McDermott
chirps, breaking the silence.

``Prostitutes go AWOL all the time,
guy''. Price mutters under
a J\&B.


``Look, look imagine that
guy'' McDermott
says pointing Price's eyes to a
tall, burly black guy.
``That nigger over there,
could hear what you've been
saying about the black Race''.
``Ha'' he squacks.

Craig is right I have to admit,
the guy is huge, swollen, probably an actual
African.

``Imbeciles'' Price mutters, looking
at me and I nod my head.

``If - McDermott stops, evaluates
what he's about to say, ``If aliens
hunted humans, for food, what race would
they prefer''.

Van Patten is about to say something but
I get to it, quicker.

``We'd die first'' I say not looking at them
but at the squid calamari, which is dressed
with light and

``How so'' Van Patten says, leaning in -
looking intrigued.

``We're pink, we look more like pigs'' then
I add ``Oink, Oink''.

``Bateman's right'' Paul says
before leaving for
a business meeting with the Japanese, not
before leaving a hundred dollar bill,
smirking saying ``Lack of currency'' to us.

Tonight's topic on
60 minutes was about choir boys, who were
castrated so they wouldn't lose their voice.

``Women don't believe in marriage'' Van Patten says
suddenly.

``Really'' Craig, says disinterested.

``Yup, it's just an economic reuinion to them'' Van
Patten says, although I'm unsure what
that meant.

``Hey, if I give that Maître d' 1000 bucks,
do you think she'd marry me'' McDermott points.

``You'' he says, examining Craig's face, ``I'd
say 5 grand''.

``Say that bit again'' I say leaning in forward.

``5 grand?'' Van Patten asks, head confused.

``No...'' I say coldly, ``about the economic
reunion''.

``What about it'' McDermott responds, then
after a pause, ``the reunion?''.

``Yes, explain. Why is
it a reunion and not a
\textbf{union}'' I say coldly.

``Well... as girls,
women are economically
reliant on their dads.
When adulthood kicks
around - marriage - this
reliance comes together
again... joint bank
account, mortgage,
kids, did I say marriage?''

``So then it's a union?'' Van Patten
asks.

``No, it's not a union''
I say annoyed, then
confused say to myself, ``Is it?''.

``Well yeah it can be both''
McDermott says.

``No - but that's not
as commonplace - both
women And men are preferring
separate bank accounts,
joint mortgages are
more common,

I interrupt whatever
McDermott is about to say,
``While yes,
marriage spurs other
socioeconomic benefits,
a-much-better chance
of getting a loan or
credit card, greater
general economic gains,
a better reputation
in the community - that's
not to say we are no longer allowed
to view marriage from a more conservative
standpint - which
is a gift from God''
and I finish, saying
softly, ``Something
that shouldn't
be taken for granted''.

And Craig starts to clap softly,
very softl and I swear I can hear some faggots behind,
from JP Morgan start to jeer.

Before Paul arrives,
Van Patten and McDermott
both leave 100 for the
bill.

``So long shlomo'' Craig
says, slapping me on the
back and I wave a goodbye
to the two of them, staring
at the Maître d who is
attending other customers.

Dinner with Paul Norman
and the girls.

``My call in life,
is to kill the people,
kill the people. Did
you get that Jessica''

``Yes yes Patrick kill the peace,
might as well kill the world.
Why haven't you touched your
lobster escargot?''

``Do you want to be a fantasy''

``Yes Patrick I want to be a fantasy''
\chapter{Halloween Party}

``Patrick?''.

``Yes Sarah?''.

``You have a paper bat on your back'' she giggles


\chapter{Vomitting Food}

``Are we aware Price?''.

``What, that we're
horrible human beings?
Yeah, I'm aware'' he
says, face morose, sitting up
from the backseat of the cab
as it passes the chemical bank
on the corner of Eleventh
and First.

``Well, yeah not
that but''

``Gram?'' Price offers,
whilst doing a bump himself.

``Price what if you had
some super-sensitive ability
that others would exploit'' I ask,
ignoring, staring at the cab driver,
making sure his eyes \textbf{are} glued on the road.

``What you mean like those
math olympiads from China they got working at
JP Morgan'' he says
all the whilst sniffing - all in one breath.


``No'' I sigh, ``Don't those
kids hate their lives?''

``Eh, its what they do,
\textbf{What} gets them paid,
\textbf{What} makes
their parents proud, \textbf{What}
gets them through this city..'' he
stops, leaning his head out
the window, making sure the Armenian
is taking
the shortest route. ``Saw
an article about the ethics
of Rolex ownership''

``Ethics? What does ethics
have to do with a watch.'' I say
sharply.

``Well...'' he says, rolling
up the window, ``It's
easier to buy a Rolex,
than not buy one, - if you
have the currency -''.

``Right'' I add, ``You'll
think about it all day, so
you might as well pull the
plug.''

``Right- but, 15K on a watch.
I mean. Can't you dump that amount
on something. I don't
know a char-

``Price a Rolex is an investment,
a \textit{commodity} - that holds
its value incredibly well.
Not only, is it a smart
financial decision to own
one, you could, theoretically.
Pass it to your kids...''

Price doesn't respond,
gazing into the fare meter
and just as it hits \$19.80, the cab in stalemate
the traffic thick, a bum moves clumsily
spraying some think neon-blue liquid onto the windshield.
Wiping it with some dirty
rag. And Price doesn't respond. And the driver honks.

``What model is it, that you're
looking to buy Tim'' I say,
my voice soft, my eyes caring
but Price doesn't respond.

Then after we pass
D'Agostion's Price
finally says, ``Jeez, would you take that
diaper of Bateman'', he's
referring to the blue surgical
mask I've been wearing all day,
for no particular reason.

Aerating the cab,
with my slow breathing,
I rip of both the straps, tossing
it out the
back window, watching
it expand like a kite
across Eleventh and First.


When we get to my apartment, Price
is wanting to ransack my
refrigerator - because
he's been sobre \textit{for
too long}.

``Bateman, why's your fridge so fucking empty''
Price shouts, sounding genuinely concerned, his fingers
probably rifling through cans of tinned peach,
moving them - only to find
some ladies fingers and a head of lettuce, that
I've been saving for later.

``Check in the cabinet''

``Won't they be cold''

``Wait. I'm coming''

I enter the kitchen,
discovering Price on his
knees examining the contents
of the fridge and he's positively
startled when I slam a cabinet
to get his attention.

``Fuck Bateman, why'd
you do that for''

I guide him to a mini-fridge
on a bottom cabinet,
covered in a dish towel.

``Woah, where'd you get that from''.

\textit{Don't say Trump tower,
Don't say Trump tower,
Don't say Trump tower,}

``Trump tower'' I say proudly.

``Woah ho-ho'' Price says, examining it.

it's cold and i'm cold, which makes me colder

'You make a mockery of the law itself.'

``gifted price, i didnt steal it,
a bell boy was gonna throw it out,''
i mutter

he nods.

I nod no
 emo pinata
recruit more tissues,
for the snot on my nose

conjur where the extra-weight
will go, my thighs, stomach,
face oh god not the face
is all i can think in the lobby
of

A searing piece of hunger
is ripping my side
waffle iron,
tossing a whole kitkat
in there and eating it
whole the molten chocolate
running down my Borelli
shirt
cereal pools into my belly
button

Children of the second world
war was the topic on

\chapter{Dinner at Barcadia}
Slash or Sty is sitting half-sprawled at our private
booth in Barcadia, Sty is a moniker I've recently
invented for him because he looks like a stye and probably
lives in a sty too.

``I \textit{won't} be having the
abbatoir slurry in bleached bun.'' he says,
without looking up, his voice resolute, low and
drool, his long black acrylic nail poking
at something on the menu.

``That's okay'' Sarah says quickly, ``I checked
beforehand... let me see.

Slash stares at the walls of the booth, which are soft
and padded - red velvet. Maybe the only commonality between
us - is that we both know they look like walls of a psych
ward.

``Okay, so they have roasted hazelnuts, celery root soup with
apples, creamed onoins, puff pastry, vegetable tarts, vegetable
strudel, vegetable soup - and her voice fades of into classical violin.

Slash doeesn't seem to listen but yawns, stretching a long
crinkled arm, revealing several tattoos, a burnt out Casio watch, not metal, not quality, several horrible looking rings, probably
all from Hot Topic
and I kick him hard under the table, which causes him to splurt in
his black faux leather jacket, probably H\&M.

``I'll have the ginger root and the his voice trails of again, probably, not because of drugs but genuine disinterest and his eyes fade of
into other people's booths.

``Why the fuck are we here with this turd'' I whisper to Sarah.

``Patrick'' she whines whispering, ``Slash is one of Evelyn's
friends. Evelyn was called away last minute. Price wasn't able
to come. And emm you asked me t-

``I-know I-know'' I interrupt, which is quite rude of me, ``Thank
God you're here'' and she smiles.

Her lips peel away as she chuckles, revealing naturally white teeth,
no whitening, no UV and her lips are lined
with a faint red lipstick, which
is neither too slutty and ne-

``Excuse me, does this have gluten'' Sty says, his voice dull,
drawn.

And I gnaw on a breadstick.

When our entree's arrive, Slash leaves for the rest-room,
doesn't excuse himself, and as he leaves our booth I can
feel every eye focusing on while black attire, black hair,
black eyeliner and I laugh at the thought.
pale red and bloated

Tonights segment of \textit{60 minutes} was solely
dedicated to \textit{SNICKERS} chocolate.

Sarah is the only person I know who consistently watches 60 minutes, the second person I know who watches it but not as much is my best friend Timothy Price. A twitter account, I asked her to make, that
I posted a selfie of me received 23 likes, 1 comment telling me
\textit{how hot I look} and I looked furrowingly at the little
avatar, then realising its some total fag who retweets
a bunch of political shit and gay porn - I block the account.
The last porno, I watched completely was titled, ``The Stars Cum Out'', where women with abnormally large clits, were eaten out. Drowned
migrant babies and migrant ships turned away from ports, will be
the topic of 60 minutes next week. Sarah, has scheduled a meeting
with me and Marcus tommorow and the shades I ordered will arive tommorow.

``Patrick, Evelyn left a message saying she arrived at Geneva. I booked
reservations for Newport. Kathey, told me to tell you she won't be coming to the...
And Ma-

``Sarah''

``Yes Patrick''

``What's emm.. What's emm - I stop, pause, sit straight
``Is there anything that's made you laugh or giggle the last
few days''.

I take a large gulp of the wine, studying her. Thinking, how plump her breasts
must be under that sparkling white dress. Really good, really good I think.
The concealing blouse, blazer and skirt she wore today is replaced,
her breasts swelling against and the cloth swims beautifully, creating little divets
where her collarbone is. It's her face which mystifies me, something so beautiful, white,
freckled, her eyes brown, her chin somewhat pointed, her voice meliflous. natural not a lot of makeup, noe
at allexcept a bit of eyeliner.
her brown eyes liquid, but penetrating, as though she could see into his innermost thoughts.”

I have an ok sense of morals for someone my age, so I stop staring at her breasts.

``Well, what about you'' I say cooly, gazing of into a booth where I think is Mark Anthony but
I'm not sure.

``Well when I graduated from NYU.. Someone from careers office, was able to find me a job, at
a credit card firm. But I didn't like the environment there. It was really hostile Patrick''

``I bet'' I say, not sure how to react.

She smiles, a sad smile, and looks dimly at her hands, ``And then after 1 or 2 years, I decided
to quit, I left everything behind and went job-hunting on online, And that's when - She pauses
and drinks some wine, ``I found you'' she laughs and smiles.

``Me?'' I reply, jokingly.

``Don't you remember'' you created the job listing, ``silly''.

``Oh yes'' I muse, ``Gosh it's been so long''.

Then Slash returns, literally disolving into the booth and a violinist starts to play
and Slash, starts to clap very slowly.

``Welcome back'' I say, for no reason.

And he shoots him a look so hateful
sara=hooper young england
wait your not white, no silly, im algerian oh.
\chapter{Red Mist}

%This triggers the release which causes confusion centre of gravity what way he will fall if the wind will pick up on.

%when i cross the road between im stopped by a cop who asks me why im so hot sweaty and bloody and i pin the blame on
Another morning,

Nobody notices what I
have in my front pocket.

\textit{Nobody} notices the homeless women,
crawling up my leg - who I've
maced several times.

\textit{Nobody}, notices I've done something good -

 And \textit{nobody} notices how
\textbf{I've} just stopped a shoplifter who's walked
out of D'Agostion's with several-several
high-price wagyu steaks, all up in her coat pocket.

``Why did you steal these?'' I enquire,
quietly getting down to her level,
which means kneeling onto cold-wet
concrete, soaking the Armani trousers in it.

The woman's face is pale and
sad, like scrunched up
paper -but
isn't old and she
wants to cry but
because of the excess
amounts of mace and the governance
of -I'm presuming
lithium? Is unable to.

She's in her late 20's \textit{\textbf{MAX}},
dressed in some chic trench coat, which is beige-
now brown and wearing a crude skirt, which
I'm guessing is Armani along with faded Chuck
Taylor Converse, the sole flapping of the shoe
and because she doesn't or cannot wear socks, her
heel is all scratched up like some dusty pole.

I soften my voice and ask her again.

``Why did you steal?''.

She doesn't answer
and just as she is about to look
up, a bus with an advertisement
for Les Miserables as it
passes by Fifth street.

Pulling herself up,
positioning her cold frail
hands onto my hip,
clinging,
feeling my warmth,
like we're something
out of a romcon, only
for it to fall because
of the cold, and reverse her
hands on my suede boots,
which are from John Lobb.

\textit{Stop playing God, Bateman,
just kill her already or torture
her for Christ sakes}.

Pulling herself up
again, letting
go of my calf, looking angered,
bitter. She glazes into my eye.

``Fuck you, you evil man'' and
then she coughs.

``Woahoho, you're an American?'' I
say, exaggerated, surprised - but
not surprised at her
lack of articulateness.

The woman doesn't answer and
uncomfortably fidgets with
herself, as the bus drives
away.

``Doesn't it hurt'' I say
flicking residual mace, of
her cheek, shaking the
can like its spray paint,
laughing hysterically in the alleyway.

The woman is young and
incredibly pale like some mysterious
apparition and she makes my skin
look way darker due to how pale she really
is. In an alternative universe,
where she hadn't fallen
victim to whatever horrible
behind the scenes decision
that led to her position.
Led her to meeting me in the
alleyway. Led her to stealing
the wagyu beef. Led her t-
I'll never know I'll never
ask where she came from.

Thinking that the woman
is very pretty, thinking
that the woman has a nice
body and if - given a financial
prompt could get back
on her feet - could sense
a role in society and even
contribute to the economy.

Unfortunately this is where
the plaudits end and I let
my head hang back as if
hypnotised by the low hanging
moon and laugh even
more hysterically at the
advertisement for Les
Miserables, as it comes
to an halt - allowing all
passengers to leave -
something I do not let the woman
do.

In some twisted logic,
what I'm doing is right,
what I'm doing is removing
a leech from the pond of koi,
and I'm giving the women,
now gasping for her breath
a chance to fight back.
And I'm
bittered by how the woman
is watching my face contort
with the moon, bittered
by the woman's
bruised and how it
is still bleeding
from the punch I delivered
earlier, bittered
by how our eyes
are still strong
watching for what
I do. I bite into her
neck.

Knowing, my incisors
can't, won't do any damage
and the woman fearful - scared
I will kill her - rolls with me
for a while in the large
cold puddle of dark grey
liquid, like we're two alligators
doing a death dance.

When I sense, I have
at least punctured the girl
I immediately start
suckling on her warm irony
blood, forcing
her face into the
ground to stop her
from squirming and
when I allow her to
twist, my knuckles clamp
her cheeks so that her scream's
lost voice and the heavy
gasping become one breath.


The woman is shaking, flapping
about like a fish, in the puddle.
And  because her movements are so uncalculated,
so floppy, I'm able to maneouver jk
her	\textit{And I} into a much more comfortable
position. Still splashing, our
cloth's wet, covered in filthy
water.

When the woman is tired, can't
go on any longer, won't
go longer and breathing
hard, I roll her so her
beautiful face can see the moonlight,
see the stars that are tonight and I
swear I lay next to her, not caring
for the Zegna suit or my Allen
Edmonds.

It's doubtful, I'll kill her
but I stick around anyway, hiding
in a corner, leaving the woman
who is too cheesed out to move
to dry on a cardboard sheet I
dragged from the back of a McDonald's.

She is now lying on a
her eyes puffed out af
from mace, looking like an outstretched anus.

Leaving her there, but not leaving the vicinity
I hide my shadow inside a large cardboard box, my
eye's occasionaly peeking through a slit in the top,
eyeing the lady, ignoring the cold all around me.

After 30 minutes, a bum who looks like has a
tumour/lump on his right leg, lurches towards her
like he's a zombie and the woman poises a hand towards him, as if this is her calling to be rescued by him.

on her atleast i think but
he takes his cock out and tries
to dip it in her mouth,
like it's a McDonalds french fry.
mouth, knowing what he is
doing is silly and wont work he gets
down on his knees, looks like he's
praying in happiness that he finally
will be able to get of, unbuckling his
pants clumsily and
please explain to me what
at my watch,
not caring if the Omega
La Magique is damaged, not
worrying if the band is ripped,

The apartment
is dark when I enter and
I don't bother to turn
any of the lights on.
Dissolving into my sofa,
feeling cold from the
wet suit, I turn on
the televison. Tonight
on 60 minutes is about
a man who.

I stare out

in some twisted logic,
what I am doing is right,
by prolonging her suffering,
causing her to believe
her death is near, then showing
her there is hope I'm doing good for the world.

When I cross the road between
upper 5th and 11th,
I'm stopped by a fat cop who asks me why,
I'm so hot, why I'm so wet and why I'm so sweaty
and I pin the blame on a Jew named Richard,
who has stolen my pot of gold and the cop shoots me
a confused sideways glare, scratching his bald head
and walks away muttering something about men of our
generation.

And I pretend my fingers morph into pistols,
shooting at back of his fat bald head, wondering where
his centre of gravity is as I make bang bang noises
with my  mouth.

Ripping the Armani jacket of,
tossing it God knows where,
hastily undoing the Hermes
silk jacquard tie, running my fingers through my hair, oiling
them, I dart down broadway,
clothes flapping fitfully in the wind and after I vomit some chow
from earlier, on a woman's shoe I escape into a McDonald's.
Panting as the revolving doors close on behind me.

The franchise is so busy, no-one notices the freak
who's just walked in looking like a zombie who
just fell in cement and I track the nearest available
seat and immediately dissolve into it. Pulling
out a cordless phone, from again God knows where
I punch in the numbers to a made up pizza place.

Shouting, Do you SEE. Do you SEE
at fat cunt next to me, halfway through
a BigMaC.

``emm i can see your orderin a pizza''
he offers cheerfully, confused, stunned.

``Hello is this the Pepperoni department. Hi yes, I would like a
large extra thick pizza'' my tounge salvates
grossly as I say thick, like I have a speech impediment. ``With extra asbestos''.

And the man, intrigued, slurping on a chocolate milkshake
which I am eyeing madly wanting to lunge for it but
after noticing the straw leave his mouth and see his spit
ringing around the straw's opening I quickly lose interest.

``Quick I need more toppings''
I shout, waving the cordless phone.

``Ginger root?'' he says thinking it is a joke,
thinking I will not order a pizza, that the
both of us will love and enjoy.

``Yes Yes'' I say delighted, ``Cut evil
from the root, cut evil from the root''.

Then pretending I am Edward Scissorhands,
I shift my weight towards him - pretending
to cut locks of thin-oily hair with my
fingers, going \textit{snip} \textit{snip}
alst whilst singing, ``I want to break free''.

i croak you have your mothers eyes as the blade's edge skims
past thinning neck hair.

hummina hummina as i jam a knife in the back of his neck, his whole body
immedietaly seizing up And the-

\chapter{GQ Magazine}
\textit{People are eating too much
food when they are not hungry. This is wrong}
was the topic of 60 minutes last night. As
it explored the routines of America's fattest men.

``Hey if a trans chick, has a bigger
cock than me, is that a fault on my
part or hers'' Craig says setting
the mood for the rest of the day.

``What?'' I say, sharply annoyed.

``I mean'' McDermott sulks, in the chair,
``ya know, hormones should reduce penis size''
then after a pause, ``it's only reductal''.

Price coughs, ``It's a fault on your part -guy, one you
shouldn't be hooking up with trannies, two
y-

``Not all trans women, are on hormones'' I tell
McDermott, trying to not fidget in the
Valentino suit, wondering who dressed
me in the morning and what I had
to do to get so hungover, ``Also, trans
women probably have enough in their lives,
to contemplate who has a bigger cock size
between you to''.

Just as I say this, a fat caterer
walks through the conference room, with
a tray of sandwiches and the leather shoes
she is wearing, Doc Martens the model
I do not know start to belch.

``Hey Bateman. Why do shoe's belch'' Price
asks, jokingly.

``What'' I croak, ``Oh emm'' then
resuming my place``- Shoe's
belch for two main reasons, one friction
between the tongue and the laces -
which can be remedied with saddle soap,
or the boot may not be broken in, which mean's -'' I pause
unsure what my next point is, gazing
at McDermott who is leaning to hear my
next point.

``Which means the leather is stiff and has
an extremely -dry surface, usually
remedied with mink oil/ leather conditioner/softener,
-or that there is excess material, a wider shoe
will cause air gaps if you have thin feet which
pushes the air out with every step you take
causing an air gap in the shoe'' Van Patten
says walking into the room.

``Van Patten 1. Bateman 0.'' McDermott squacks, ``You've
lost your edge Bateman, you've lost your edge'' he
mutters.

I've decided if there was to be a nuclear fallout,
I would kill Craig first, to conserve
the room's oxygen
and make cute little wallets and
trinkets from his skin and bones that I would then
use to barter with bandits for food money and
drugs.


Today's agenda, is whether or not we should continue
investing in Japanese business's.

Sarah, sneaks into the room, scanning the sea of
suits for me and when she does, looks relieved
and hands me a stack of neatly organised items.
Postcards from Mom and Dad after their holiday
in Boca Raton, a letter from Lianne
Williams and a copy
of GQ magazine Price ordered using my card.

``Is he wearing sneakers with a suit'' McDermott
croaks peeking at the
stack in my hand, ``Oh god he is''.

``I think it's hip to wear sneakers with a suit,
display your casual side once in a while''
Luis butts.

Staring at the male model, at the bright green
two piece suit, which I'm guessing is Gucci
or Louis Vuitton and at the white sneakers on his
feet, I feel every. Like I'm on death
row, .


``No it is NOT OKAY, to wear sneakers with a suit''
I yell, causing Sarah to freeze and I tilt my
head smiling at her as she leaves. ``

``




``Well'' Price croaks, ``That is not on the itinerary''
amused by my outburst
softening his voice adds, ``But I don't see why they wouldn't like it''

``Bateman?''

``Huh -oh, smoothie's would be great,
really smooth and chewy...''

``Are you even fucking listening'' McDermott
shuns ``He asked
if it's culturally
appropriate to invite a Japanese to sushi,
or as a guest should we be pointing them towards
American cuisine?''

``I don't see why not'' Van Patten says.

``What if it turns out it's actually
really horrible sushi and we've
been ordering and tasting shit
all our lives because we've never
been to Japan or indulged in the actual thing.
We wouldn't know, would you'' he
says pointing to no-one in particular, ``Guys,
I've heard them speak MANDARIN in the kitchen''

Both Van Patten, McDermott and I
stare in disbelief at the mouthful
that's just come out of Price's mouth.

``Have you been'' Van Patten asks
actually concerned, ``
doing cocai-

``Fuck you'' Price says.

``Look'' I say, more alert, ``Let's just
pick a non-specific non-ethnic restaurant.''

\chapter{Rolodex}
My stomach literally boils, this total bitch
from JP Morgan, keeps calling, asking why I called her and her friends a bunch of skanks as they exited Barcadia and I fail to mention
that one of them, tossed a shoe at me.

``Gosh, Bateman is that a rolodoex? Oh my
God, get rid of that'' Craig McDermott says strolling into
my office. Then as if it is the funniest thing in the world says,
his voice high and pleased, ``Hey Van Patten Bateman's got a rolodex''.

``What's wrong with it'' I say, spinning it.

``Get rid of ittt'' he laughs, ``Jeez Bateman, it's like your stuck in the 80's.''.

when the japanese, come to your office and look at it slanty eyed what are you gonna say
wht is he going to say
wht is he going to say
van patten says stunned looking at it perplexed like its something pulled wrongly out of a time capsule
rolodex? Price says walking in hands in his pockets, wearing a
\chapter{HOMELESS MAN}
Tonight's topic on \textit{60 minutes} was about
city bins which would overflow, leading to a ``rat 'n mice''
outbreak and featured sewermen who waded through New York City fatbergs.

I find myself wading through the antique district just below Fourteenth streeth,
wading because the fog pools low and wading because the sky is dark and heavy.

Cartoon stinkmark trills surround bums passing up Fourteenth street,
their shopping cart wheels, struggling to grip onto its unpaved concrete.
One even falls and his buddy picks him up.
Black guys and faggots shimmy
past me, offering either crack or sex. I choose neither. I walk by an
abandoned newsstand, barred up by spidery rusted steel and
a faded 1989 edtion of Time magazine is visible through
the gaps. The heading, ``This may turn you green with envy -
or just turn you off. Flaunting it is the game, and TRUMP is
the name''.
A woman in a dry-cleaners, neatly folding some sort
of grarment -stops and sets a cold accusatory glare onto me
and doesn't seem to stop until I'm out of her radar. A baptist church, is
open and kids sprawl in and out of it, all dressed in suits,
all black-American, all suits and when I set the Serpina atache case down, its
steel feet bashing the concrete - they all scamper.
Coming out of a diner, another bum can be seen being
\textit{``shood''} out with a broom and when the waitress
see's me, stops and closes the door.

Bags of frozen garbage, sit outside broken-down apartments, most abandoned,
most hosting crack-whores and meth addicts. The bags have been ripped by rats,
but still hold their structure due to the cold, the rats pour literally
inside the bag, their two long yellowish teeth pulling and bringing lumps of rotting
food out and I swear one brushes past my shoe.

I stand there for 10 minutes, quietly observing the neighbourhood as the fog
pulls around me.

A bum, not a white bum, not a black bum, or even an Asian bum. But a bum
whose skin was so dirty, darkened, dirt-filled it was impossible to identify
his race, on skin alone, sits sprawled on the curb. His trousers drop several
inches below his ankles and he starts to sob. Perhaps,
crying over things, that relate in no way to his life.
I laugh at how ridiculous he looks and every movement he makes - I see a jibe.
Any-any desire to work or contribute to society inside the bum
has probably burnt out like lighter fluid left too long - in the air.

The street is quite, the day young and just as Patrick's watch hits
11, a man not too far
away from Patrick huddles up in filthy bedsheet, using crinkled
newspapers to wipe the sweat trickling
from his brow. A shopping cart, bestowing the few items of value he has, sits
next to him: a backpack, some books, all tattered and rain-stained, some
cloth's and ratoins for the night. And dim shadows seem to float beside Patrick and
the man, as car headlights catch the metally mesh of the cart.

Looking at the sobbing man, Patrick smiled and kneeled on a patch of concrete,
which gave way for the weeds and ocassional dandelion to grown in.
As a child the man, was reared on spoonfuls of rum or gin at night, because
his mother had grown old, too tired to wean and hoped he would sleep early, to wake
up for the long school day ahead.

The bell of a bicycle rings and the man begins to detect Patrick.
A high pitch squeal breaks loose from a frozen garbage bag and rats scurry out
and bound towards it, instantly 5 or 6 more appear from aloft a wall, immediately
syncing sharp incisors with the loose black material, biting hard and ripping at it
until more rats are exposed to the cold air. A rat frenzy.

Tonight 4 other of his friends would gather, safe, in the confines of
the desolate road, safe in numbers, safe from college kids who would
throw rocks at them from their trucks and safe from crack dealers that
would try peddling them low-grade product at a low-price, which was actually
laced with fentanyl as it would be cheaper to produce but still could give the same high.
They had all reached the same sensory deprivation, they had all reached the singularity
in their lives, where nothing else had mattered. They would rarely speak but the warmth
they each provided was better than the combined smell they each gave of.


``Hello'' Patrick says, with a wan smile, his knees patchy with dirt, the same
dirt the man was oh so accustomed to.

The man grumbles something and slowly raises his head.

``My name's Patrick. Pat Bateman. What's yours''.

The man lifts up his jeans and spits into a cup,  but doesn't respond.

``It's dark out, do you have a flashlight, something to see with'' Patrick whispers,
his hand shifting through the loose dirt and gravel, his manicured nails brushing close
to the man's thighs.

The man fumbles with his coat pocket, a cheap black nylon shell that looks sort of like the
garbage bags that Patrick had walked by and pulls out a thin flashlight.

One click, second click but the light doesnt go.

The man grumbles again.

``Must be the batteries'' Patrick jokes, ``Lemme guess AA right, Alcoholics Anonymous,
just kidding, let me see what batteries it takes, I have a few''.

Patrick saunters towards him and when the man see's Patrick's double-breasted
suit and mirror-shined wingtips, his mind automatically suggests relaxing.

The man unscrews it carefully, allowing one existing batteries to hit the concrete,
rolling down the street, the other is a triple A.

``Okay so two triple A's'' Patrick says, unzipping his backpack, ``Here ya go''.

Patrick carefully drops them into the mans hands, careful not to make contact.

One click and a thin strobe of light, finds its way onto the dark curb,
illuminating weeds and flowers nestled in its holes and Patrick's mirror-shined
wingtips.

The man smiles and splutters, ``Th-an, Than- not before breaking out
into a serious cough.

``No need'' Patrick interrupts, offering
his handkerchief, which the man grabs tentatively,
placing his hand on the man's shoulder, something
which jolts the man, because no-one had done this since he was a child. ``Listen what's your name''.

``Colm'' he says.

``Colm? Listen Colm, I'm just going to ask you a few questions''.

The man looks up, meeting Patrick with a sulken stare and sniffs,
blowing his nose into the same crumpled newspaper which he
wiped his brow.

``How'd you get here Colm?'' Patrick says, his voice low, curious and morose.

``I have no self-respect'' Colm sulks.

Tears start forcing their way through Colm's cracked skin
darting down, the long and matted beard.. The pores of Colm's
nose were clogged and corkhole like, every part of his face was dirty.

All you'd need now is fur, though Patrick and everyone would think your bigfoot,
he mutters to himself.

Colm's monastic habitance of crackdens,
shelters, streets and parks, meant he seldom spoke
to people apart from the occasional police officer, telling him to move along
so when Patrick asked him, ``How'd you get here Colm'' his instinct was to
say, ``no self-respect'' because that was what everyone he met growing up would tell him.

``You're damn right Colm, you have no self-respect. You
need to start respecting yourself'' Patrick says, with a hopeful gleam in his eyes.

``You're right, you're right'' Colm says, retreating into
the nylon shell, ``I should think like you more mista, you're a kind-kind m-

``Colm?''

``Yes mista''

``Do you know why you have no self-respect Colm?''

Colm, stops, not-thinking, but holding onto the wheels of his shopping cart
as another bum, someone he'd seen around, walks by.

``Because I've got no job, no savings, no ca-

Patrick cuts him of, momentary sobs still escaping through
Colm's now heavy breath, ``No people like you, are absolutely
not worth respecting, let alone acknowledge''.

Colm starts to stiffen up, the last of his tears running down
his hardened cheek and a car flashes its headlights on both the men.

``I walk past you on the street and all I can wonder is what
deity, up there - Patrick begins gazing into the clouds pointing
at a few clouds, which look like faces, ``is keeping you alive!''.

Patrick begins to back away a few feet, ``Why would a self-respecting
person allow bacteria and odour to allow themselves such a pungant
stench''.

``I have no job Mista, no home, no access to running water''.

I know you do, I know you don't have a job, or home, or fucking water. You wanna know something Colm, here let me blow your mind.

Patrick sets down the atache case, unclasps it but clasps it again.
``I always think you should be executed, no really, What do you
Colm bring to the table. You are a net less to society, You are the
sty in my eye, Colm''.

I bet you change your clothes less than once a year, you fucking disgusting
thing. Who do you pass the blame on to, Do you tell yourself you get a pass
because you have no home, do you tell yourself you have a pass
because of some made up m ental disease, the fact you had some sort of difficult
childhodd. because drugs are like catnip to you.


i dont even pity you colm, none of us do, we all wish you'd just pack your bags
and go. but nowhere will take you colm, i mean why should the locals
here have to tolerate your stench. noone wants to be around you colm,
your parents think your dead, the government stopped getting social
security checks, people you knew in highschool will probably think
once in a while, i wonder whats going in in colms life. tell me
what went wrong all those yearsk, bck, i really do despise you

i haven o purpose  You know what’s a great purpose in life? Feeding your family.
"my life is over." Cop: "it wasnt that great to begin with." That is fucking awesome!

``But you know what Colm?''

``Wh-a What'' sulks Colm.

``Our lives, you and I, are a satire of the people we surround ourselves with, HA,

Another car passes by, which looks a lot like the ones
college kids would drive, chucks out several beer bottles
 when it passes, Patrick
seizes the man by his throat, grabbing the flashlight from his eye,
bludgeoinign both his eyes in a deep bloated purple.

Unable to register, Colm covers his neck instinctly and raises both hands
to his eyes, now bloody and raw.

Patrick peels back, his palm in full contact, with the raw red loin-like skin,
his skin lierally peeling from the side and patrick peels his eyes.

and as if his eyes were photo-lens, they snap, capturing the macabre eye
in timeless imbolity, the embelem.

%The baby began to cry with horror as she saw her beloved playmate
%writhing mass.
%When Paula Blakely rushed into the room, she screamed in horror and
%utter panic. The scene didn’t quite register in her brain. All she saw was
%a room teeming with bestial, furry shapes, tearing at something bloody.
%And then a small white shape. A tiny hand quivering above the mass of
%black.
%‘Karen,’ she screamed.
%She ran into the room, kicking, screaming, her blind panic giving her
%added strength and speed. She clutched at the arm and pulled. The little
%body came up but with two of the monsters clinging. Paula beat at them
%as she made for the door, her own legs already covered in blood from the
%bites she’d received.
%The two rats fell away, not from the blows, but because the soft flesh
%``Hello'' Patrick says
\chapter{df}
Tonights topic on 56 minutes was about homeless people who were pushed into the hudson river and drowned because they didnt know how to swim or because their tacky green jumpsuits filled with water
palidrome prostrinatoin
\chapter{Zoom Call}

Pierce and Pierce, have agreed to tour and
host a select group of seniors around the office's,
having one-to-one meetings with them, detailing
the managerial aspects of their positions,
what suit's they should first buy and how
to get their head in.

``Ask questions, volunteer information, explore
different avenues, better yourself -these are all
things you can start doing to get ahead in life''
I say proudly, examining my face in crisp HD.

Then add, ``Of course a good GPA is a criteria
and getting into a good university, involves
a huge element of luck, yet you should also
ruthlessly seize the opportunity when it calls''
A girls face turns on the camera and she look's
happy to what I've just said, like I am Jesus
Christ, and I've come down to eath.
absentate

``Bateman sells. Good looks sell. Money sells'' Van Patten says, patting
my back after I've hanged up the call.

``Anyone worth knowing, is worth at least 100 thousand dollars'' he adds.

``That's true'' Craig says.
And although this mock-politeness should infuriate me
\chapter{Army of One}

A woman's face is stitched to the body of a rat -
it still alive and wriggling - the woman
still alive and squiggling. And the smell
of decay is soaking into everyone.

- \textit{Homeless man} - who I found rotting in the back
of an alleyway, sits at the head of the tub, just
where the hot and cold water pipes jut out, his
arms crossed, looking sort of alive and the
woman lies just bellow his nave, her heels resting
on the guys shins.

I begin pouring heavy amounts of lyle and powder
into the tub, the powder close to my face,
I really should be wearing a mask but the faces of the two warrant me otherwise.

If the lights were off, the rats eyes, orange,
would look like two floating balls of fire. Pupils scanning
the room like radar.
And I begin feeding it anything I can muster up from my pocket,
McDonald's french fries, McDonald's ketchup, a napkin from Wendy's,
tortillas from Taco Bell and a used condom I found in an alley.

sweat drenched, delerious
I experience a sickening moment of fear as if
the bottom of everything was falling away from the bottom of my
feet as it starts nipping and licking at my fingertips, and i pinch
the rats face for a bit, uncontrollingly wanting to vomit

``Bateman Bateman''
croaks the man, which
causes the rat to

which causes me
to let go of the rat his skin literally melting from his arms, his
hand digging in his jacket pocket, ``take the watch, take the watch''

shocked, at the man and at my own eyes, at the watch

``It's a datejust, you can
tell from the steal and
yellow gold jubilee braclet''

``W-what'' I ask genuinely afraid, as if harassed, trying
to smile, on the verge of vomitting.

``The dial is factory set and it's automatic movement''
and perhaps a gesture of sincerity, the man unstraps the
watch, holding it out towards me like for him this is a -normal
jesture.

And I stand in horror as his body dissolves, the rat fades
breaking free of his stitch crawling into the woman's mouth,
disappearing by the tail.

``The rolex datejust holds its value
better than the submariner because datejust's are always in''

``Because datejust's are always in'' we repeat in chorus.
\chapter{xx}

``You took pharmacology very far Price'' warns Van Patten.

``Lay off him'' Craig exhales ``It's already
enough his bullshit wife won't give
him head'' he says, eyes peaking through shutters, ``Shit,
where are those motherfuckers''.

``What'' moans Price, ``Hey, I
have a luxurious king sized bed from
The Hamptons, fro-m
Christ I forget, Hey!'' throat sore,
hair slicked stiff but ruined from all the
movement, too dazed to do -or know anything.

``I said you're depressed and in an unhappy marriage'' Craig
shouts, still looking through the blinds.

The effectiveness
of \textit{To catch a predator} was the
topic of 60 minutes today, the show's most apologetic
men made statements to the public on why what they did
was wrong and why they will never do it again.

As I stare through conference halls, my eyes
adjusting to the various shades of Mexican,
Chinese, Indian, Mexican who cruise through company
hall's - all recently hired, some direct grads even.
Sarah who
is wearing a really nice Louis Vuitton suit,
double breasted, tight skirt, is bending
over to talk to a little boy who is Paul Owen's son
who is decked out in Polo by Ralph Lauren and is
visiting for the day. And the
amount of corduroy on Sarah really makes me
want to fuck her. This causes an erection to build and to kill it, I force myself to think of three cringe things.\\
1. Aiming a gun at your teacher, only to reveal at the last moment, that it is in fact a bb-gun and not capable of firing live rounds.\\
2. Wearing a non purple label Ralph Lauren suit.\\
3. Having your credit card declined at a restaurant.

Luis Carruthers and Van Patten are now discussing
60 minutes after Craig confirms the Ford
that's now pulled up outside Pierce and Pierce belongs to the Japanese.
Luis is wearing a pale cream coloured and a brown herringborne
tweed bowtie from Brooke's brother, slightly prettier than the
reverse silk-wool black mohair one he wore yesterday. And Van
Patten is wearing a two-piece.

``To catch a predator'' Van Patten scoffs,
``What if they're all predators''.

``What'' McDermott squacks and then leans back
on the office chair,
brushing lint of his dark grey pinstripe suit, from Brookes Brother.

``Well'' Van Patten stretches, ``How'd you know'' he says quickly, ``Bateman
might be a predator''.
And then raising his hands in self defence, says ``Relax,
not here to arrest you bud'' winking- his Rolex Submariner in view.

``Yourrr a lawwman?'' Price asks, still dazed, at Van Patten then
at me, like we are the last two people on this planet
and have come to kill him -saying
abruptly, ``Bateman isn't the problem.
It's you. Mister Predator. Your the problem.
Yep. You are God's problem. Your going to hell.
''
he says all in some raspy breath.

``Don't joke about things like that Price. It put's me of''.
Van Patten says sternly, watching as Price's eyes
fall back and out his sockets.

``Bateman's not a predator, he's the boy next door''
McDermott whines, then adds, ``all -grown up''.

``Awww who's all grown up, no longer cute and wubbly'' Louis
says, the one-liner all in baby talk, his
face purred up like some gross old man, his cock probably
fidgety and his hand leaning on his cheek.

Craig looks grossed out and I do to.

Then Van Patten breaks the silence,
``It's the digital age''
sitting up from the chair,
``Everything you'd wanna know,
everything I'd wanna know -
About who's fucking your ex and who
your mom is cheating on your dad with -
it's all out there''.

We all, move in on Van Patten listening
attentively to everything he has to say -

``I knew a guy'' then corrects himself, ``My
mom knew a guy, he'd been over the apartment
a few times used to watch dateline all the
time with us, Chris Hansen and To Catch a Predator.
Always used to joke how fucking dumb
those retards that got caught where. Punchline,
you guys ready for it''.

``What, he got caught, he went on the show?'' I ask,
intrigued.

``You'd think that, no he went on to fall
in love with one of the decoy's, obviously
they don't list any of their personal info
in the credits or shit. So he scoured some
modelling and acting sites and you'd guess it.
He found her'' his voice is very soft as
he says that bit.

``How'd she die'' Craig interrupts, heavily
interested but unsure when the Japanese
will arrive.

``She didn't''

``Oh'' Craig says.

``Guy found out where she lived,
where she worked, who she dated 5 years back
and who she wanted to get married to, raped
and tortured her, burnt her quite a bit,
said it was for all the guy's lives she
ruined''

``Poor girl'' Craig says, looking genuinely
upset.

I'm silently murmuring, \textit{There is no punchline, there is no punchline}
but calmly in resolute
ask, ``What was his name?''.

``Hogg''.

After the meeting with the Japanese, Craig
McDermott, David Van Patten, Christopher
Reeve's and Marcus Halberstram go sushi
with our asian friends, where they
will probably end up doing a lot of cocaine
afterwards and karaoke.

Luis, Price and I are now the only one's
in the conference room.

``You coming, Bateman? Price?'' Reeve asks.

``We're alright'' I reply.

``Suit yourself'' then, remembering Luis
is also there, also there sitting
right with us, nods and Luis tips the trilby hat.

Luis who had been listening attentively to the
dialogue between whether or not American business's
could ease Japanese deflationary pressures prior has something
to say.

``It's psychological guilt Patrick''

``What is'' I reply.

``You know, what David was saying'' his voice
is hushed, ``I heard half of those men
who go on that show, go on to kill themselves
or others because of the guilt''.

He looks scared and I almost want to hug
him before remembering the remark he made on
me earlier, which causes my body to tense.

Sensing, my silence, he coughs, softens
his voice, which makes him sound even
more like a fag, ``well, I watched
the Jimmy
Kimmel show the other night an-

``Jimmy Kimellll'' Price groans,
resurrected from the cross, ``I-hate-Jimmy-
Kimmell''.

``The talk-show?'' I say amused..

``Yeahh, he's awful Bateman'' waking up,
still dazed, Price says once
more now awake
, ``Luis?''

``David''

``What are you wearing, you look like a fa-.

I cough.

``Van Patten'' Luis says.

``Yello''

``David'' Luis says
once more, looking
down at his perforated brogue's which
are probably bespoke, as no brand would
quantify something so hideous.

``Price isn't feeling so well, so his
sartorial judgement is a bit clouded,
You look fine Luis, just lose the bow-tie
and wear black slash grey coloured socks''.

Luis smiles at me and I smile back.

``So David'' Luis says, smiling at me but not looking at him,
``Why do you hate Jimmy Kimmell''.

``Jimmy Kimmell'' Price begins, disgusted,
``I fucking hate that show it makes American's
look stupid, -Well we are stupid, -Not we, or atleast not me''.

``I agree' I say honestly, ``The Jimmy Kimmel show is anti-Am''

\chapter{Bird trapped in glass cage}

I'm staring at a budgie in a cage,
outside a shop window on 860 broadway and
the bird starts making a sound, I know
birds are not mean't to make \textit{this}
sound and I step forward, not before looking side-to-side
at the various pedestrians making sure I am not seen.

And the bird hands me some paper, it was holding
with its claw.

``How did you write this'' I ask, my voice curious,
my stare cold.

``I used a Montblanc M fountain pen, with gold
carot nib and turquoise shell casing'' the bird
croaks, his voice dehyrdated and parched.

The note repeats, itself in big bold type,
``DIE YUPPIE SCUM. DIE YUPPIE SCUM. DIE
YUPPY SCUM.''

And I read instead, ``Die hippie scum'' walking
away, my shoes slapping on concrete.

``Wait'' his voice croaks out.

I decide to adopt the bird, paying just \$10
dollars for it, the cashier some skinny Mexican kid,
getting all excited when I hand him a 100, thinking
I'd give him the change.

I try to swallow the bird whole,
or bite its head of in one fell swoop
but something is stopping me from doing so and the Mexican
starts to shake.
\chapter{fd}
Liane Williams, the escort has called again asking if I could pick her up from a client's house.

``Why what happened?'' I say into the pocket-phone.

``P-Patrick, just come please, th-this Is the last time I'll you ask you this, I promise'' her voice blares,
sobbing from the other end.

When I kill the man, Lianne watches in horror but a thankful horror because I have saved her life and I tell her I need
to dispose of the body when in reality I will torture the body, scraping away fat from the man's bones, enscribing my initials
into the bone, then chewing and licking the bone, allst while I stomp up and down on the man's nose, breaking the cartilage,

asking why I haven't
\chapter{df}
Tonight the budgie doesnt talk but just looks dimly at the other bird ive bought for it to play with
the other. bird skips around in the cage, looking merry-eyed and the other budgy looks at its feet

``So... you brought me a Mexican'' the bird mutters, voice heavy, eyes tired.

And I almost spit out my J\&B.

Factoring in what the bird has just said
and whether I ams stil
Tonight's topic on 60 minutes, was about the Strangeleer's a boy band
gone rogue which strangled various female fans backstage, their tools
varying from fiber wire, amp cords, guitar strings and skipping -rope.

``Hey when I \textit{bought}, I didn't want a racist bird''.
\chapter{Shoplifting}
While fucking this total hardbody I picked up outside a ...
, I start whispering cruel hate-filled words
into her ear, ``You slut, you total ugly slut''.

Then I'm back at it again, shouting low-effort hate-filled slurs, as her body
moans into mine, twitching
in static as I cum and when done. I push her of me. Ragdoll-like, not caring for her, I toss some 20's at her and she scampers away, picking up every bill.

Tonight's topic on 60 minute's wasn't really a topic, but a discussion with a panel of experts, all from various vields of law enforcement, some judges, a couple
cops, a lawyer, some host girl; which was conveniently titled, ``Got a guilty
conscious?''. And people would phone in, confessing all the bad things they did.
Some of the confesions were more rational, admitting to making illegal
U-turns, however some were more scandalous and involved people admitting to
keying neighbours cars and committing insurance fraud. The segment ended with a bleak but stark message, ``You will not get away with this''.

The porno playing is titled, ``Love 2 Fuck'' starring Jessica Ashley, Britney
Maddis and Judith Callice. However, unlike thte title would suggest there
is no love and Jessica is harping on about how she loves being fucked, whilst
Britney plucks at her clit and Judith bounces her tits up and down.

The smell of perfume is intermangled with the smell of burning hair, which
is sort of like the smell of burning feathers, but that is sort of like
the smell of burning pubic hair.. But it's all very hard to explain.

The constant hubbub of the television and the constant rush of traffic outside, pisses me of and I roll of my bed, hastily putting on my suspenders.

Whilst at a Target, outside the buildings.
im sd knowing the only way id be arrested if i was to walk through the doors
[12:39]

\chapter{S}
While it is possible to skate
on park benches, it is not possible
to walk through walls - was the topic
of 60 minutes tonight, as it explored the lives
of America's poltergeists.

McDermott looks denatured.

And some ugly Indian girl sits with her legs
crossed, her face literally looking just like
a skull, in fact her whole body looks like a prune.
Like some shrivelled up 90 year old buddhist monk left in
the son. Ugly Bitch.

And McDermott is probably thinking ``Ugly hateful bitch,
why the fuck am I paired with you''.

A fat girl is dressed up in a floral dress, probably
Belarusian, the flowers stretching
at her sides, so what would look like a dandelion looks
like, \textit{I don't know a pancake}.
In fact Price looks sad he's been paired with her, but
I can't tell because he's leaning on his hand and I can
see he to is wearing a Rolex submariner.
Her whole
getup is basically the same as putting lipstick on a pig.

``But that's not the point'' I
say outloud, accidentally.

``It's not?'' Price says, voice morose, low and cold like something
out of a movie.
Everyone in my department, has been paired up with a senior
for the remainder of two months, the good thing being we get Friday's
of because of this, the bad thing - \textit{I don't actually know}.

``Do you think my coat looks bad?'' Luis asks, raising a raccoon coat
to my eyes.

``No Luis.'' I say, slightly in awe because i-

``It cost a pretty penny'' Luis jokes, ``You know I
picked it up at an antique store. When I saw \textit{it}, I
knew! I just had to have it, oh but the lining was fraying
so I had it relined.''

``I bet'' I say, slowly losing interest, thinking about the
steak slice I will eat when I get home, which is really
nice because it is steak and onion wrapped inside a-

``Patrick
where's your student'', Luis says tapping my shoulder.

As my eyes begin to scan the room, I can
see Luis has been assigned to the only boy in the
room and Luis looks positively flushed.

Craig is squinting as the indian chick starts
talking about true crime tv shows with the belarusian girl, and i swear his face can't get any
more shrivelled.  ``Bateman'' he croaks ``help me''.

``O-M-G'' the Indian actually says omg, but says it in a way
you'd think she is white, American, blonde, dumb. ``Did you
see the the episode about the guy that poisoned all the evians''

``Yesss'' the other replies, looking heavily interested and
for a second I think I have a common interest with them, not before
they quickly change topics talking about, ``the weather''.

``You girls see \textit{60 minutes}'' I say to them.

``No? What's that'' one of them replies.

``Nothing'' and I swear Craig is eating his own hands.

Case study I am thinking. True crime I am thinking. I am a future
case study I am thinking. When I was in college and took philosophy,
I used to quote from Ted Bundy and the Unabomber as my key thinkers,
which my teachers thought was not appropriate.

``Patrickkk'' Luis sings, his voice
high and faggy, ``Where is your student Mr Bateman?''.

``Oh right, my student'' I reply.

``Well'' Luis says, ``Looks like someone is all by themselves''

A girl is standing with her back flat to the wall, opposite to me,
both hands clutching a leather bag, definitily designer, definitely
good-quality, definitly designer, but the logo has been removed and
looks conditionied. Her eyes and hand look soft, her face warm, but
looking down, her hair neat and in a bun. Her skirt and jacket, pinstripe.

The corner of a room is a place
for a child who has little say in the constitution of a wider world.

``Is everything okay, I wont bite'' I say softly, getting up from
my chair kllkkj

\chapter{Devil}
The greatest trick the Devil ever pulled on the Earth, was convincing everyone he didn't exist.
Or that it within our metaphysical remit - it was possible to even fall in love with the devil.

Kenneth Copeland is the last person - I've decided to kill, for a while. Because after
my dinner at Newport, with Tom Riddlestone, Alexander Macab, James Newman, the remote
at my hotel broke and I was stuck watching the religious channel all night.

``Why do you have a rolex'' I ask at the tv, half-expecting a response.

``Yes Bateman, why do I have a rolex'' the tv blouts back.

I'm not sure what 60 minutes was about but Price tells me it was about surrogate mother's who
died in childbirth and Sarah tells me it was about mothers who find out their
daughters were still alive after school shootings. June shooted me an email, saying
she was sorry for her nervousness and would like to schedule coffee, if thats okay with me -
and i send her a single emoji back saying, ``Send me the deets''. McDermott texts me saying
how much of a bitch the indian is working with, ``Christ, Bateman the girl has all A's and her
gpa is a 6. What the fuck am I meant to mentor her about''.

``Tell her she's an ugly bitch, and you'd much prefer she'd die''.

``I tried that Bateman, I really did. But the bitch keeps insisting I reveal
some sort of trade secret. That I'm under some sort of oath not to.

``Then try- harder '' I say, gulping down some ibuprofen.

Price, texts saying although his mentee is a bit irritable at times she seem's willing to learn
and I can imagine Price and the Pig.

Killing Kenneth Copeland is not an easy task. This will require copious amounts of heavy
thinking, hard heavy thinking maybe paired with the new Taylor Swift CD. Kenneth
is a televangelist, as I've come to know.

\chapter{June}

\chapter{fs}
Mothers who found out their daughters were
alive after school shootings was the topic
of 60 minutes today. As it panned to the

\chapter{Who am I?}
Tonight I walk in on the bird doing cocaine wiht Yogi Bear
and Woodsy Owl. I wear a dogtooth check tweed Armani coat, armani
socks and slcaks, socks which are probably Ralph Lauren, shoes bespoke shirt and tie all RL

My desire to die is constant, like a pure thought in
the mind, devoid of emotion. Yet I needed to feed.
my existence is to excercise a morbid fascination with the accult and to this day no attempts have been made to reconcile my anti social behaviour by others
I am surrounded by those who only serve to mock
me, and even the people I love the most are only
there to laugh
Sarah is lesbian
\chapter{Pitch out}
When Aliens do DMT they see \textbf{P}at\textbf{rick} Bateman.
When Aliens do cociane they see Timothy Price.

``Jesus, someone call him a cab'' McDermott shouts through
the exiting evening crowd.

``No segment of the population is immune to drinking'' Van Patten
coughs, hoisting Price up with one arm, I the other.

``He's not drunk'' I say, feeling Price leaning to my side, hearing
literal friction between his course stubble and my armani overcoat.

``Will someone call our buddy Price a fucking cab'' McDermott shouts again.

``Why don't you'' Van Patten barks, struggling with Price.

``I'm not calling him a cab'' Craig barks back, ``especially
after what he said to me abo-

``Fuck you'' Price says, jerking, his voice fading in and out
of palindrome.

``Bateman?'' Van Patten asks,

``Can't, left my wallet at home''

``That's alright, I think I have a fifty''

``No-no, it's alright, I'll walk him''

``You sure''.
you saud you dint work
[03:02]
i work irregular hiurs


Then suddenly, like miracle
\chapter{MR FBI}
The bird doesn't speak or do anything notable today,
just shift through play-sand I bought it and stare out the apartment window.

\chapter{Handsome Faggot}
The bird hands me a ring today.
its okay patrick your safe, your safe with me, and i love you
and just as i touch her, the rolex drops from my wrist and the dial shatters.
``I love you to, June''.
\part{Homeless}

\end{document}
%\part{How I met, Patrick Bateman}
%tell hazel about dad turning 50 want to buy him present
%\chapter{test}
%Lorne working = more beer money = driving under the influence Jeez
%Price have you been drinking, guys i say interrupting, and whisper, do you wanna step out bud, have a sit in my office price nods yes and i walk him to my room, where I place him softly on a bean bag

%When I was 15 I used to promise ugly girls I'd marry them if we were both 30 and single, many have and i dont answer
%Because strangeleers was the name of the movie I rented but because movie rental shops have been closed i vaguely shift the cursor onto netflix where i will setup a subscription using a stolen credit card
%of all the bull shit
%coming out his mouthMy english is degrading every year like a melting candle in the wind at Jim Rauch's wake.
%"GET THAT VENN DIAGRAM OUT OF MY FACE --"
%"No, I can't John! The diagrams job is to depict the proportions of commonality and difference. So, don't get tough with them"
%My name is June Lee, birth name June Li. SHE IS HER.
%I like flowers, fashion
%and taking care of others.
%men who trapped bees along with their chastity cages was the discussion on 60 minutes tonight
%I wasn't even supposdo you not know bowling alley etiquette”ed to be in that class.
%60 to bible,, minutes to bible, 60 to bible
%Can I wear the same suit for multiple days in a row? Does a different shirt colour each day qualify as a distinct outfit? Will it look unprofessional if I only have two different suits? ELI5 or a young person who never intended to work in a professional office.
%Never wear the same shoes 2 consecutive days. The best shoes have leather soles - so much more comfortable than rubber soles because they glide a little and help reduce fatigue; forget gel inserts, just the regular thin leather of the shoe insert will be enough once you break in the shoe; leather soles will wear better and can be repaired.
%why, some cocky kid asks
%If I'm going to be sweating in a suit either way, I'm definitely going to wear an undershirt to avoid ruining a $100+ dress shirt with pit stains. the cocky kid says
%wool is more breathable than polyester0
%as he is pissing i whisper do not turn around,
%i have a gun, i will shoot and kill you, you do not know who
%i am because of the voice i am putting, you do not know my face because
%i am wearing a mask you will leave in 6 minutes, and stand still
%otherwise i will shoot you. You do not go until those 6 minutes.
%I completely understand where you’re coming from, but trying to do the bare minimum to meet the required dress code is a good way to look bad. I work with a lot of guys who think and say the things you’re saying and they are always dressed sloppy in a way that everyone can tell.
% Do not wear the same suit on back to back days
% price and van batten both say
%I’m not saying you should change the way you do things. Just keep in mind that maybe you look different than most of your coworkers and not in a good way.
%soprani wool jacket, pleated pants from brookes brothers

%Besides, we're talking about wearing a wool jack, wool pants, wool socks, and leather shoes; I hardly believe that a super thin cotton shirt is going to be the difference between comfort and boiling alive in that outfit.
%June stares at me proudly
%everyone stares
%IM NOT IN A POSITION TO GIVE YOU A RIDE HOME PRICE I SAY DRUNK WHAT CANT HEASR YOU
%one-liner
%Murder on wall street was the title for the time
%i painted it i lied
%why hasnt anyone fucking taken out trump yet
%or the queen or nelson mandela, shit hes dead i forgotS
%Digging up corpse fbi agent
%Which is like catnip to people
%a slow caravan of cars creeps through the georgia roads
