\documentclass[19pt,openany]{book}
\usepackage{microtype}
\title{\textbf{D}ar\textbf{k}ness \textbf{K}noc\textbf{k}s}
\author{}
\date{}
\begin{document}
\pagenumbering{gobble}
\maketitle
\tableofcontents
\part{Post-Modern Post-Insanity}
%CHAP1%
\pagenumbering{arabic}
\chapter{Rabies Fox}
Hope is like a drowning dog,
whose owner strands it in
the middle of a frosty lake.
A cinder block is tied to
an old leather leash and the
block rests j
on cracking plates of ice. A
bowl of kibble mirages from the lake's
edge and the dog is scooting with its
butt pushing of glass sheets
with cold-numb paws. Almost as if to think
another man, perhaps a passerby, someone kind
who will take in - and love the dog, is shouting
``come on boy, almost there'' its
food, its only reason for moving
draws closer. But the ice cracks and
the cinder block is soon to follow,
making this moment of the dog's life,
cold, calculated, futile. Very futile.
And I'm
happy sacrificing parts of
my soul, each day, to the
demon that warrants my comfort
in New York City.

A hour prior and you'd
see me outside some hick part of
town, heading towards 23rd St.
The heavy worsted-wool
Tom Ford overcoat, sodden with
rain, now remains slumped over a green park bench,
left for anyone's take and my
now-black chalk-stripe
Giorgio Armani
suit, starts to dry in the emerging sun.

Irregular glints from various puddles
are catching the velvety white leaves of my Edelweiss Boutonniere.
And although, I'm trying my best \textbf{not} to look at it, my face
has been grabbed in a deep section of
still puddle. -And although you
might say; my face is chiselled, my
skin tight, my eyes young and
still youthful and that my
hair is tidy and laid-back.
There is still, \textbf{no} single
point of attraction.

And as this horrible unethical
reminder, of my self-betterment
program is starting to erase
itself from fallen rain. Another
man would like to build himself
from the collapsed remnant of my
reflection.

- \textit{Some} - homeless nigger is \textit{wanting}
to lurch towards me -
with a used Styrofoam Starbucks cup in
one hand;
fresh, bright-red lipstick running
of its rim,
nothing in the other and water beads
from his brow trickle on in.
Either he's a cross-dresser -
\textbf{or} its been snatched out of some
ladies hand.
His face, solemn, naturally
blurred from various warts and ailments, is coming
dangerously close to mine and a used cleaning rag
wraps tightly to the brim of his forehead, leaving
an effeminate look to his naturally skinny face.

He starts to say something - but I don't catch it.

``I'm, -I'm-I'm very cold Mister'' he
starts spluttering, like an old engine.
Shaking - perhaps expecting to extract
sympathy from me, the rest only
inferable as unintelligible murmur.

Wiping residual powder shards
from my nose, thinking
whether or not I've left
the oven or whether the Chinese
exiting a taxi could be
my ex-girlfriend or wondering
whether I forgotten
to tape \textit{60 minutes}
- I notice
the bum is still standing.

``What'' I say sharply, emotionless,
my hands
stuffed into my trouser. And I
begin staring
at his shoes.

``Amb-ba-ba-ba Mista, you've got to
c-call me one''

``Jesus Christ'' I mumble,
not looking at the man,
then looking side-to-side
at passerby's who I wonder
would scold me if I was
to hit the man
and then
after a long neglected pause
say, ``Do you even
know what you're
saying?'' looking at his
worn-out shoes. Looking at his
gangrened toe, wondering why
it hasn't fallen out yet and
looking at his shoes, wondering
where he had found them and
if he would recommend them.

Preparing to soften my voice
and meet with his eyes,
I try to compose myself.

``Ma-ma ma body. Oh my g-gawd, GLUAH''

Reaching into the belly of my jacket -
searching for something stiff and pointy
that will shut him up.
I discreetly fold a 20,
making sure no-one is watching.
And carefully place it in the styrofoam
safe, where it will sit with
\textit{buddy's}: Lincoln,
Jefferson and Roosevelt.

Red brushes up on Andrew Jackson's face
and I think he is starting to ease up a bit,
although his not-so-thankful look
comes of as unwarranted. \textit{Admittedly}

cataract He is now coughing up some foul-smelling fluid,
blood I think. Well, \textit{could it be
blood?}. Blood isn't as chunky, nor is
it as smelly but it doesn't matter as
the foul-smelling liquid is percolating
down an Arab looking shawl.

Raising cuff to nose, I trudge past him,
exiting the park

And I bump into someone,
who says he knows me - but I don't know him.

A nerdy white dude,
fat, unapologetic
looking, bearded, is
exiting a GameStop on 24th, his hand is
gripping a Nintendo Switch title - with
a cover I am vaguely familiar with.
And his brown sandals slap on against
white concrete.

I was a small child
when my Mother, had thrown my Nintendo,
down our apartment's dirty trash-chute, after
I had thrown up that morning's breakfast,
which had consisted of grey eggs and sour
milk. As extra punishment, I was
to hand over the game's case
and any assorted manual or charger,
which was all bundled into the
same plastic bag. But I hid, the
game, knowing it would be no use
without its designated console. Thinking,
I had gotten away with murder I diverged
some tears knowing all hope would not be
lost - as my save files were still intact.
But Mother, had known wiser and forced
the case open, demanding for me to go back
into our apartment and retrieve the game.
When I could no longer see the plastic bag,
as it fell down 30 blocks of 70's stairs
, I thought if i was to ever
have a child - i was to never be as so cruel
to it. The school day, that followed,
felt like my birthday - because I had never
wanted it to end, so much so I took extra
time talking to my teachers asking if
they needed any extra-help cleaning the rooms.
When mother had come to pick me up,
she was gleaming, with bags of sweets and
toys in her arms and told me on the walk
home how she had rescued the device, from
the binman as he was ready to throw it in his
collector. What was the point of the punishment,
is all I had thought

- God - you
could have gotten it for
an absolute steal
an absolute steal - if used,
my mind is now racing.
Giddy but also ready with vocal disappointment
disappointment, I shimmy through sideways
traffic, preparing my lecture on the many
merits of
saving. His confused head, unable
to comprehend the words I
am saying or why I am
wagging my finger in front of his
eye is simply bobbing to a yes-no-yes-no
type beat, provided by Beats from Dr Dre and
the song I do not know.

I'm shouting at him, stressed,
frustrated, bit angry, that what
I'm saying isn't getting across.

``No, not good luck - here's some
advice - \textbf{YOUR} a \textit{fat fuck}, I wanna
gouge out your eyes''

``Hey thanks man, its actually
for my kid'' he says
and
the song which I now know
to be, \textit{Gangster's Paradise}
blares
from his headphones.

\textit{Tell me why are we so
blind to see, that the
ones we hurt are you and me}
is what I now hear.

This leaves me disappointed
and dejected and I continue
down 24th, soon to approach
Times Sq-42nd.

Maybe - he learned something - or - if
not who cares. I'm drawing
out the words I said to him,
trying to not
make my voice appear sad.

Reaching, the subway,
slightly earlier than expected
I lock eyes
with a hardworking Mexican
teen,
giving him my nod of approval.

And some punk
shoves into him, which
causes his
hands to lose grip of the
bun he's been working on.

I can hear him shout, ``Hey
ese, watch out man'' in an
accent I thought couldn't
get any more stereotypical.

And the once pig, once
chicken, once lamb - dog rolls
down somewhere
into the gutter, where
it will most likely
float into the Hudson river
or be chewed on by rats.

The man, not paying
attention is wearing a
dark ensemble. His jeans,
ripped denim, not sandblasted,
are held up with a loose
Hermès H buckle belt. His
shoes are designer, probably
Gucci or Louis Vuitton in perforated
leather with tassels and above
sits a darker, black -
disproportionate,
\textit{720 fill power},
\textit{DIST certified}, glossy
Moncler puffer jacket.
Which - is obviously, too
expensive and
ruins the outfit making
it look cheap. And he fades
of into the subway.

Directly opposite
a Glenn's pharmacy, is a
lone white
supremacist, balding, old,
semi-tall but strong-looking -
And he yields
a large white placard with
neat red
letters that read, ``With
Jews we Lose''  or was it,
``Whites for America''.
Either one, either one.

``Well'' I say rubbing my
jaw. ``I'm just not one for
the cause'' I shout through
busy traffic.

``Whaat'' he shouts, wind pushing
his eyes.

``I said - I'm just not one for the cause''
I shout back.

And a native American
woman, glares
at him, does nothing pushing
a baby in a pram -
who wails ferverously at its
birthgiver, hurling
various unintelligible insults
into the air.

Another hobo is
Wearing a
yellowy-white stained tee
- no jacket, grey
sweatpants with the word
NIKE smeared on the seams
in big bold type and
ripped leather velcro shoes
sits under a nearby intersection.

Where automobiles throw
coins and trash at the ground he
calls home. And he begins
contorting his skeletal
frame around a
burning trash can
desperately grabbing on to any heat
being let of from the
plastic flames,
extending his arm
and callused hands to
sift through the thin
layer of dirt-dust gravel
for something, just
something, to shield his
eyes with. The plastic flame,
knowing this, shifts
direction,
causing him to
cough - seek cover - cough and
covers a pair of burning red-eyes
eyes in a thick black blanket of misty haze.

Another hobo, who MAY have
been a gambler in his past life,
is wearing a decrepit banker stripe
Dolce \& Gabanna double breasted
suit, with side vents and looms
non-chalantly over side-ways traffic.
Hoping to hitch a ride home. I'm rattling
my fucking brains here, wondering
as to where I've seen this guy before
and it hits me. He was my former
teller at Trump Plaza

And I imagine he sings,\\
\textit{
	I was never homeless,\\
	I had a homestead,\\
	5 children, that I fed,\\
	Each one, I put to bed.\\
}
``Hey John, it's me Preston'' he shouts, waving
his entire body around, the pong of
cheap cologne slapping me - I never even called his name.

``I'm not John, I say'' smiling back, with cold feelings
devoloping in the back of my head.

``Well...'' he says raising his arms in a \textit{you've-got-me-look}
``Look I really need a rid-

The traffic picks up and
various hardbodied Romani
Gypsy woman emerge, who try
to sell me flowers,
picked - illegally from
various different
9/11 and Iraq war memorials, that I'm impartial to.

And I swat them away,
with my back poised straight
observing a group of negroes
who've staked
propietary claims
to rows of city bench's
just outside a 711
and sprawled over uncomfortable sets
of steel I notice several rounded-
spikes installed on the ends of
each bench - most likely
installed to curb the city's
rough sleeping epidemic. And
the men sit and gossip.

A few feet up seems to be a buddy
of theirs,
who shouts loudly

``Man,
this dat SAME drug that killed Michael
Jackson'' pointing openly
to a lit joint in his right hand. An orangey-red ring forming at the end of the joint,
which appears to be wrapped from a
variant of the original RAW classic
rolling paper.

The group paying little to no notice.

The sound of my heels on rough concrete are masked by
youth's shooting hoops at
a nearby court, the rim having no net and
the ball soon to be run over by traffic.

That same homeless nigger,
that I gave 100 bucks
to? He's now spazzing out on the grass, 2
feet away from me. \textit{Is
this motherfucker really going
to OD next to me?} Is all
I can think.

``Hey, hey buddy'' I yell,
snapping my fingers at his
frozen face.

But he just stares blankly at
my general direction.
Dude's system is probably
overloaded with methampthetamines. His skinny
sirloin
hand is posed like Michaelangelo's, \textit{Creazione di Adam}.

Foam dispenses
from the mouth, the froth generating
a deep and rich lather which
coats his skinny-smooth face in a layer of
one million bubbles each juxtaposed and some are
even shiny, like dish soap. And the guy's eye's
still frozen in place, convulse, pulsating - his mind
probably, no, must be thinking one thing. Whether or not,
I will call an ambulance.

The banality being, I couldn't
even if I wanted to as Cricket Wireless, my service provider,
has recently refused all payments from my account, due to
a series of suspicious payments from abroad. They
are also not answering any of my calls.


And he reaches towards me.

My Eagle Claw cufflink from
Fort Belvedere, silver with onyx ball is briefly in contact with his fingertips.
And he grabs on to the Luigi Borrelli, two-fold cotton, shirt's cuff
immediately staining it in a deep crimson red.

I quickly pull out my gun,
which is a Colt 1851 36 calibre and yell quietly, ``fucking
stay six - feet
away from me.''

``You got that?'' he mouths yes, still frozen, the barrel
feeling up and down his mouth, I fire a warning
shot and a flock of pigeons flies of in the distance.

%CHAP2%
\chapter{Kissing Bus}
I'm now on bus, on route
towards the SoHo part of town,
my cuffs still red,
watching pornographic
film on my
pocket phone - the volume
on \textit{\textbf{MAX}}.

A guy is
getting his cock sucked
by a Thai woman,
tall, no ass, perky tits and
begins buckling at the knees.
The woman is making unnecessary
glugging noises
and another much taller woman
appears with a tasselled whip,
wearing 12 inch Jimmy Choo
platform heels- who is now
whipping at the guys ball's. The
guy now kneeling due to the pain
and shrieks as she steps on his toes.
Whatever he is saying is muffled by
a red rubbery ball thing, held
in his mouth.
And at this point I'm so worried that the
guy wont be able to get of, I nod
nervously at a kid, about
12,- thinking he
too realises the woman's moan's
are deeply perturbing and I slam
the screen on my thigh, wavering
a sigh of relief winking at the boy.

The seat in front of me, empty,
half scratched with initials
of couples and dates
has an old sticker on the back
of its headrest, advertising a
Lulu's massage, a name I should remember
but - I have no recollection at all.

Behind me - an old lady,
confused, frail, White
- American looms over the seat
behind me,
adjusting her eye-glass, trying
to see a piece of the action.
And I think on whether
or not I should show her
the latest stash of cartel murders
that I have archived, maybe
\textit{Sinaloa} or \textit{CJNG},
\textit{Los Zetas} works
although their new stuff is pretty tame - but the driver,
a man in his 40s, Egyptian probably has something to announce.

``It don't go no further''

And though I'm unprepared
by the woman's genuinely
cheerful glare and the good deeds
I have accumulated for her
to look so happy. And the way
she is looking at me with two
tennis-ball sized eyes and
an open happy jaw, albeit not
whatever she's thinking of - I help
her get of the bus.

Exiting the portal, last,
I walk past this group of noisy
teens, dressed loudly. And I shoot
them all death glares
but their eyes are glued
to either pocket phones or passing
windows with bright coloured jackets
and similar coloured sneakers. I think a Footlocker
at 31st St.

A girl in their group,
listens to \textit{Poker Face},
by \textit{GaGa}.
And I know this because the
music's too loud. And the group
later poses in front of a George
Floyd mural on 91st, painted by immigrant artist
Ash Barker, all happy-eyed, flipping
peace signs, all wearing airpods.

And \textit{Lathyrus linifolius},
a herbal suppressant which wards of hunger, shoots pangs
of un-relief down my stomach lining. This is all because
I've been eating nothing but it for the past 5 days after
reading an article about it's dietary
effects on the body fat of field mice.

I now weigh, 224 pounds an impressive corresponding
figure for Men with BMI's of 27.4. And although
this number looks and feels colossal, I am very muscular
all round.

The enclave of land,
draws further and further towards me,
like a snapshot from the magazine \textit{Pride Weekly}.

Various new shops have propped up, with different
coloured pride flags sticking out from window-corners.
And multi-ethnic people are all stopping to talk to each
other, Fashion I'm guessing or what shampoo they use
for their dogs.

I touch my nose by mistake and
my fingers come back wet.

Women are outnumbered by men, 3:1 in SoHo.
I walk past men in moustaches, wearing large mink
coats holding other men's hands and going into
men's-only-bars. And I've accumulated a
sufficient amount of compliments, from how
well I'm dressed, how-formal, how-proper,
how-tuned I look.

The ones I care about
are all from Wall Street Yuppies, who
are all on lunch break.

The sun is hanging low and casts
its turning glaze over me and passerby's
who are otherwise all happy
are starting to stop, gather, murmur
and I start chewing nervously on a
dry-cleaners ticket and some wall street
jerk starts looking at me
like all I've eaten
for the past year or 2 has been
\textit{\textbf{XANAX}}.


Something is throbbing in my chest, wiping residual
snot from my nose, exposing
my nostrils to the now-cold-air,
taking
long calculated breaths, whispering
in a dental way, looking to my left and feeling to my right,
I stop at a salon to catch myself in one of their mirrors.

``You've had so much plastic surgery, I wonder
if it would even be possible to go back'' I start
to hear, from a raspy
couple walking behind me, and
the words,

``POSSIBLE TO GO BACK, POSSIBLE TO GO BACK''
quickly play
around in my head, trying to figure out which word
should be emphasised first.

And for a fleeting moment, I look past my reflection
and wonder if there ever was a time, where
I wanted to go back.

What I guess I think is a passionate
moment, I dig into, my jacket
searching for my gun - because I don't
feel safe.

Levying my fingers on the
trigger, a sense of relief
swoons over me and I loosen
the grip on its handle, retrieving
my hands from my pockets and flick
of sweat from my brow.

``You're a weasely little shit, aren't you'' a disgusted
sounding voice
parses out from behind.

And as the words, possible to
go back - possible to go back
can no longer ring themselves
out. I've just
understood that \textbf{this}, this
epicentre, is where all sin has originated from,
and the air above
me begins
to grow dark in a sepulchral gloom.

``We two, are seperated by
God, from God and when the end comes, we shall
be slain and served as food
for all those deemed righteous''
the voice behind me says,
calling out to me, in monotone.

And the woman behind me,
saying these cruel, cruel words
lifts her arms in an
\textit{I'm going to get you
look}, although this isn't
a movie and I'm fairly
certain her only intention
is to kill me.

As if guided by sunlight, hearing
the laboured voice of constructioners
egging me on, I look back - No, no time for that
and run through the darkening
street, my jacket flapping through the
wind like a cape my leather shoes slapping up
against new concrete and the woman
screams like a banshee - and the
voice follows me down my path.

The woman lifts her arms
even more
and gives into the game
of chase.

A dull thumping beat
is obliterating all
forms of monologue in
my head and my legs
are weak.

She holds both arms out,
and the skin on her
face, looks as if its
melted, then been reapplied
like clay, hanging loosely,
all her teeth are fully
visible though her mouth is
closed and what looks like slow
motion - she takes a jump
towards me and passerby's
are clapping her performance.

Behind her, behind
her body, looks
truly exquisite.
Azaleas are
creaking towards warm
pastures filled
with all animals.
And man
can laugh and play,
breathe without worries
of being hunted, eaten or taunted.

I find an unguarded bike,
raising my leg over the
seat which is too high,
not checking to
see if its rideable,
I start pounding on the
pedals, down the wrong side
of an one-way road.
And I see the faint glow
of the woman's face from the
bicycle bell - her nails - just
touching the rear tire.

As I'm forced of my bike, from an enormous
gale, knocking the bike into rows of new-steel
cars. Crushing 5 more tablets into my mouth,
oh my gosh, is all I can think as my teeth
chomp down on what I think is an ibuprofen.

My vision is all but one
enormous kaleidoscope of colour
and I've hit my head hard. So
hard, that I'm certain the pain
signals are delayed and my mouth
is teething in angst.

I hear the woman draw
closer and my heavy unwarranted
breath is being masked by the siren
of a cop car and I'm certain I'll shit
my pants if she comes any closer.

Realising, the sirens aren't
for me, thrashing on the rough concrete,
knowing I've fucked up my only pair
of black brogues, the woman's finger,
skinny -skeletal like
trying to pry my mouth apart,
her nails now clawing at
my tongue, a new-formed crowd applauding
her and I'm certain that I've vomited
back up some of the medication.

But an idea flashes through my head and
as her woman approaches my half-sprawled body,
perhaps readying to sodomise me pulling of
mirror-shined patina half-brogues and throwing them
into the air, she starts to fight with me as she unbottons
my jacket.

Remembering, \textbf{I am the one
with the gun} I quickly pull out the glock,
almost dropping it, fiddling with it, although
it's just \textbf{one-shot} to knock her out.

``Hey-hey lady'' I shout
snapping my fingers through
reindeer-skin gloves
but the sound is totally
muffled by a mix of
leather and warm sheepskin lining.

Almost wanting to warn her of
the impending bullet, so she
can escape to whatever cavern she
crawled out of.

Irritated, I continue snapping
until one glove
produces a rubbery sound but
the woman doesn't stop the rape.

``Look at me
when I address you.''' I start
to yell, in a sing song voice
then in absolute, yell
``\textbf{YOU DUMB FUCKING BITCH}''.

The short stationary burst of
movement ruins the drape
of the Armani suit, and
a blue crimson fiery ring is placed
on her forehead and the body collapses onto
my arms.

Pushing her off of me gently, her hair being
picked up by the wind, weaving into it like
they're sticks of corn.

I flag down a cab, running after the
Armenian behind the wheels, yelling
``Stop, Stop'' then proceeded
by ``holy shit, holy shit''
but he is driving faster than I can run.

And startled, from unwanted
glares that begin to accumulate
from onlookers, I
tear through my ostrich skin
wallet, by
Hermès, and begin
throwing crisp 20's at her,
most not even
reaching her
as she's like 50 feet away and
some even being picked up by the
wind, where they will most
likely flutter down somewhere
up-town.

And she lays there while a
puddle of thick brown blood congregates on the floor,
her hand which otherwise - Could aid her in standing,
struggles to grip onto the stuttering concrete
so it lies there, feeling around
the surrounding ground
for a while and then stops - revealing
manicured nails - dipped in
red french tip.

When I'm all out,
I quickly jog sideways,
careful not to work up a sweat,
back and forth across
upper 91st, pointing
my gun
at various stone-faced
onlookers, threatening
to shoot if the sound
level raises past 25 decibels.

The exodus, which I cause
provides me with sufficient time
to rush into a Wells \& Fargo,
I lock myself in a small
secluded cubicle and then
prop my back against its cold metal door,
exhaling endlessly.

After many hours
shopping in the mall,
making futile chit-chat,
antagonising minorities
tasting free-samples
of gluten free bread and
buying expensive perfume
I finally leave.

Opposite a children's
book shop, an incident
has taken place, from
where there is police cordon tape
and white sheets draping over
an unmarked woman's slumped body with
white
chalk surrounding her.
Unfortunately, there is no CCTV
where this incident took place
and I proceed with my day,
changing into a new Luigi Borelli
shirt I purchased for 95 dollars
at Macy's
leaving the old Borelli
at a nearby McDonald's
the cufflinks still in it.

Leaving upper 91st, amex still in hand,
this Ebola-looking nigger tries to sell
me his CD. Although I do own a player,
so I buy
four. And smile at him, taking his Instagram
promising to listen to them as soon as I get
home and high five him, shouting something positive.

And the puddle of warm stagnant blood
which starts
to dry, wets the wind,
her body fast-frozen
the white chalk conserving her remains.
And arbitrary bits of trash
whistle by me.

I meditate on what I had just done.

Realising
I would also need to discard my reindeer-skin
gloves, which are also from Armani.

Shouting, ``you stupid stupid stupid
bitch at no one in particular'' flagging
down another cab that doesn't stop for me, wondering
what would happen if all the LGBT flags in SoHo
were suddenly replaced with white-defeat flags, I fall
to my knees crying and a wan reflection is loosely
visible in a broken mirror.

There is no resolve.
%CHAP3
\chapter{Apartment}
My head is heavy.

Unable to move, stiff, chin
cradled into a stuffed
giraffe gifted to me
by a female colleague.
The Omega \textit{La Magique},
is the only extension
of my body actively
facing the window-wall adjacent
the Matthew Hilton king-sized bed and
a throbbing sensation pulses
down my chest whilst sunlight
creeps through
shutter gaps, aligning itself into perfect panels
on Persian rug.

Arms, legs, sore - clambering onto plush
fur carpet by Gina Napoli, pulling an
Egyptian-cotton blanket
and Burmese-silk pillow covers,
all by Geneva, with me I lie
on the floor.
Dazed, unable to recover any
recollections from last night's
activity's I extend my arm,
clumsily trying to open
a bedside dresser. My slim-cold fingers,
hitting the brass knob several
times before, clutching, pulling,
gripping. My fingers rifling
past various fountain pens,
all by Montblanc, finally grabbing
prescription eye-drops.

The drops trickle down my face -
some going into my mouth.

Startled, I start
seeing yesterday's
Armani suit-jacket
on a mannequin, given
to me by a friend who works
at Hermès. Its trousers, hanged, on
a valet stand, given by someone who
works at Trump Tower and the shoes,
with its correct shoe-trees
neatly to the side.

And through
the loose eye-drops that drop
from my lash,
flecks of blood
are visible on its lapel. Fabric
and threads stick out making
the garment look like a horrible
scarecrow. Examining the weave,
in sniper position rubbing the
wool and silk lining
with two fingers, breathing
in it scent I look at where
the fabric's been torn then at
my own body.
But my bodys fine. And
I'm confused as to whether I was
the one, who put it on the mannequin
and if so why was there blood on it.

Pulling myself up,
my cock swinging whilst doing so
and hearing the
landline ring I answer it
without checking the senders name
and head towards the toilet with
a towel hoisted on my shoulder.

``PATRICK, PATRICK'' the
voice blouts out.

The room is black and gold. Mainly
black, some gold. Who my Korean
friend, helped design last fall.
Venetian curtains, are tucked
into the rooms corners,
exposing the room and its glory
to the many skyscrapers outlining
the city.

Realising, the voice
is belonging to Paul Norman, my close-friend
who I met at work, few years back I
go back to the landline, placing the
towel on its rack.

\textbf{``What the fuck happened downtown?''}

Panic. Desertion.

An odd tingly
feeling creeps down my nails and
I begin staring at my fingerprints,
wondering if any two swirls can be
the same.

Four compact discs, which
I must have bought are
sitting neatly stacked on a drawyer.
\textit{Perhaps a rare
artifact in my search for immortality,}
Carefully putting them in a protective
sleeve cover, examining the various black
cover artists, opening and closing
the case, thinking WOW this is really
cheap.

``You'' the voice blares in an
accusatory tone, ``were supposed to meet with our
Japanese friend's at Effes''.

And the unknown panic swoons over me.

Reruns of \textit{60 minutes}
are playing in the living room.

\textit{``Tonight's coverage is of an
11 year old boy, who shot his Neo-Nazi
stepfather, point-blank whilst
sleeping''} can be heard.


``\textbf{Patrick}, \textbf{Patrick} ehmm are you even
listening?''.

``Yuh, Uh, One second Paul,'' I shout back,
still staring at the black musicians.

``Jessica, Rosie - Natasha and
I are thinking of Nell's.
Jess is getting her hair and nails
done first and I have
a meeting with the Japanese. I'll put you
down?''

``Uh Sure'' not sure if he heard,
``Nell's?'' I shout back.

``Hey how long would it take me to
\textbf{die} from
this''.

Placing them in a protective sleeve,
next to the Michael Jackson section.

Something is rattling
from the landline. Pill probably.

There is music playing
from the apartment upstairs,
probably John Lennon.

And a mixture of Paul Norman's
voice and the televisions
is coming in through the bathroom door.

``Listen, Paul I'm a bit occupied.
I'll catch you later okay'' I shout
from the toilet.

``What? You're breaking up''

\textit{``Neo-Nazi Jeff Hall's son has
had a history of violent outbursts at school''}.

After an interim of radio-static I
hear the landline click.

I own an extensive archive of DVD,
Bluray, VHS, laserdisc almost every
film format except old film reel.
Because old film reel is very
flammable.

Everything is meticulously
organised in A-Z order
Shows, Movies,
Documentaries I particularly
enjoy are set as assignment
to interns who shadow me. And I
later probe them on what about
film/show moved them.

I am Not a collector and
anything I do not gain utility from.
I have my secretary, give
away and write it
of as charitable donations.

That night, I had a dream
where I was being killed,
slowly, by a small man-child
who I had insulted and not gotten
away with.

The closet I'm walking into has
A large Julius Caesar bust, on top
of a quartz pillar, I had
commissioned last June  directly opposite
me.

One side of the room is partitioned
for my many sets of bespoke suits
on steel poles. The
other for tailored off-the-racks, all
designer or Saville Row.

Then rows upon rows of drawers,
with clear glass cases, hold:
silk, wool and mohair Hermès ties.
All 180 bucks a piece.

Shoes, by John Lobb and
George Cleverly, too many too describe
are on shelves, mirror-shined.

In the corner, are pens
owned by Harry Truman, Richard
Nixon and Donald Trump.

And several large cedar blocks are
in the room to stop moths.

Putting on a Corporation
of London, charcoal grey
double-breasted slack-cut
suit, shirt in french
cup, silk-mohair
socks from Tom Ford and
Cleverly black brogues I
exit the room, flicking
the switch off.


\textit{``When he was taken
into juvenile hall,
he was so little they
didn't have shoes
to fit him
so they had to buy him a pair
of tennis shoes''}

And I dissolve into the sofa,
temporarily tuning into shots of the
now dead Neo-Nazi, Jeff Hall's
exploded brains and I switch
channels to a more cultural one.

But all that comes out from the soundbar
are eerie african drums and sweet preruvian panflute
and snapshots of different groups of indigenous
people.

A monk who killed and tortured various black protesters
but wasn't really a monk, just a bald
white-supremacist, who looked Thai
is being held in custody in New Jersey
and will also be the topic of next episode's
\textit{60 minutes}.

And at the front-lobby
of my apartment, the
man today is looking at me
like I'm an anaconda who's
just swallowed a large goat,
whose horns are still wriggling
inside of me. Like he's
some horrible part of my past,
who's been brought back
by God to punish me.

And I sign my name on the log.
%CHAP4
\chapter{End of Month}

The remainder of the month's
days are uneventful.

I meet and confer with various
homosexuals, to discuss
what perfume is best to
leave a good impression,
whether certain shades of
brown can be worn for formal
occasion, to shave
with or against the grain and
other normalities.

Liane Williams, the escort
is calling me, asking if I'd
like to meet or whether
I enjoyed the Broadway show
we saw last Tuesday.

I bump into a faggot,
outside
a bar on 6th street,
some fat chinese wearing
horn-rimmed Oliver People's
glasses a brown-patina'd
atache briefcase by DH
Sanders and a beige suit,
by I'm guessing Hugo Boss. who
is wearing a pink and
blue polyester
bow-tie.

And I tell him, stretching my
jaw, exaggerating the
word love - ``I-looove-it'' stabbing
at the bow-tie with my finger.

When in reality I actually
hated the bow tie.

And I look down at my wrists
wondering if I were to
cut them of with a high-powered
chainsaw would I either \textit{A}
bleed to death, \textit{B} pass
out from the shock of not having
hands or \textit{C} run down
a one-way road screaming,
``I have no hands, I have no
hands'' over and over again
raising my arms at passing
cars, blood gushing out from
cartoon limbs coating frost-covered
 windshields.

I am still unable to get a phone
provider and also am now
unable to get a credit card -
not that I need one, just
that it's nice to have.

I also grabbed and french kissed a girl,
I walk past everyday. She is
startled and might file a report
on me or mace me next time. But I
have my wits.

%CHAP5
\chapter{Personality Test}
``And how often do you think about race?''

``No''.

She looks at me sideways from
the monitor.

``No, I mean I never. Never think
about race''.

And she starts typing something.

``How often do you think about
gender?''.

``Seldom''.

``Age?''.

``Never''.

``And how often do you think abo- she
pauses, laughs nervously, ``Sorry
not allowed to ask you this'' blocking
her ears with cupped hands
saying, \textbf{ha-ha}.

``No please do'' I say confidently,
feeling an upper hand, although not
sure why.

``Patrick'' she says surprised, expecting
me to know something that is universal
knowledge, that the whole world and
its minions should know. ``It's -
illegal''.

Sarah, my secretary - a
little softbody who
just graduated from NYU, a woman
I plan on making a move on and one that
is capable at her job, stares at her
keyboard, maybe wondering why the first
row starts with \textbf{Q},\textbf{W},\textbf{E},\textbf{R},\textbf{T},\textbf{Y} or why
the space is so big.

I exhale her name, softly , smiling, ``S-a-r-a-h''
And I place my hand above hers, which
cups a mouse, raising her chin
to mine.

She doesn't really look at me and turns
the monitor to the side and the
cursor hovers over the sentence,
and I can almost hear
through the screens pixels,
in a singy-enquiry voice ``Are
you a homosexual?''.
%my call in life is to
%kill the people, kill the people
%did ya get that,
%yes yes patrick kill the peace,
%might as well kill the world
%CHAP 6
\chapter{Dinner at Nell's}
``Alright...
what about college girls''
starts Timothy Price.

``Congested'' comments Van Patten,
rubbing his brow.

``No - a good athletic girl
is what you want, someone
whose pussy \textbf{needs} a good
stretch'' McDermott adds.

``Wants -guy'' Price corrects.

I'm sitting by myself at Nell's,
joined by Timothy Price, Craig
McDermott and David Van Patten -
all because Paul Norman's cab
broke down and the girls are late
as usual.

Mcdoofus is sitting cross-legged,
sipping on a J\&B, wearing a pale
blue Valentino suit, navy Hermès tie
and a Patek Phillepe watch. And I can sense he
is going to ask me something because
the way he has been uncomfortably
eyeing the Omega La Magique.

``So.. Bateman you've been
awfully quiet what's
emm, your type of woman''

``Jeez aren't you quick to
know McDermott'' Price
says coolly, folding up a
German cigar case.

``Well.. I mean'' Craig
coughs, ``lets \textbf{all}
be on the same page here,
what do you look for in a girl''
expecting the others to take him
seriously.

I'm a bit stumped by the genuineness
of his question not before
he adds, ``A little hardbody
no-less, easy women'' grinning
endlessly.


``Well...'' I say taking a pause
longer than I should.

``Go on Bateman, \textbf{blow}
our brains out here'', Van Patten
says pretending to have his
mind-blown with his fingers.

``I-'' start
by saying, unsure
where this is going to go.

``I like a girl
who has a clear career path''
I say crisply. ``
But also someone who is not afraid to
explore their options,
diversify in a way.'' I
stop, stirring
my martini. ``I like a girl who is
also not too sexually active - someone
who can share a common ground with me
- but not too common - so that
we lose interest and eventually fall
apart. Someone who is so desperate
for the lost art of male satisfaction,
she is completely oblivious
to the M2.50 caliber rifle, wedged deep inside
her pussy, which will send shockwaves
of pleasure up her spine
-\textbf{no-doubt}'' and I
finish my JB.

Something seems to have
been lost in what I say
and Price is looking
at Van Patten and McDermott,
who both look back uncomfortable.

``Anyone hear about the escort
girls-up North, who went missing'' McDermott
chirps, breaking the silence.

``Prostitutes go AWOL all the time,
guy''. Price mutters under
a J\&B.


``Look, look imagine that
guy'' McDermott
says pointing Price's eyes to a
tall, burly black guy.
``That nigger over there,
could hear what you've been
saying about that black Race''.
``Ha'' he squacks.

Craig is right I have to admit,
the guy is huge, swollen, probably an actual
African.

``Imbeciles'' Price matters, looking
at me and I nod my head.

``If - McDermott stops, evaluates
what he's about to say, ``If aliens
hunted humans, for food, what race would
they prefer''.

Van Patten is about to say something but
I get to it, quicker.

``We'd die first'' I say not looking at them
but at the squid calamari, which is dressed
with light and

``How so'' Van Patten says, leaning in -
looking intrigued.

``We're pink, we look more like pigs'' then
I add ``Oink, Oink''.

``Bateman's right'' Paul says
before leaving for
a business meeting with the Japanese, not
before leaving a hundred dollar bill,
smirking saying ``Lack of currency'' to us.

Tonight's topic on
60 minutes was about choir boys, who were
castrated so they wouldn't lose their voice.

``Women don't believe in marriage'' Van Patten says
suddenly.

``Really'' Craig, says disinterested.

``Yup, it's just an economic reuinion to them'' Van
Patten says, although I'm unsure what
that meant.

``Hey, if I give that Maître d' 1000 bucks,
do you think she'd marry me'' McDermott points.

``You'' he says, examining Craig's face, ``I'd
say 5 grand''.

``Say that bit again'' I say leaning in forward.

``5 grand?'' Van Patten asks, head confused.

``No...'' I say coldly, ``about the economic
reunion''.

``What about it'' McDermott responds, then
after a pause, ``the reunion?''.

``Yes, explain. Why is
it a reunion and not a
\textbf{union}'' I say coldly.

``Well... as girls,
women are economically
reliant on their dads.
When adulthood kicks
around - marriage - this
reliance comes together
again... joint bank
account, mortgage,
kids, did I say marriage?''

``So then it's a union?'' Van Patten
asks.

``No, it's not a union''
I say annoyed, then
confused say to myself, ``Is it?''.

``Well yeah it can be both''
McDermott says.

``No - but that's not
as commonplace - both
women And men are preferring
separate bank accounts,
joint mortgages are
more common,

I interrupt whatever
McDermott is about to say,
``While yes,
marriage spurs other
socioeconomic benefits,
a-much-better chance
of getting a loan or
credit card, greater
general economic gains,
a better reputation
in the community - that's
not to say we aren't
to look at marriage from the
BLANK - which
is a gift from God''
and I finish, saying
softly, ``Something
that shouldn't
be taken for granted''.

Before Paul arrives,
Van Patten and McDermott
both leave 100 for the
bill.

``So long shlomo'' Craig
says, slapping me on the
back and I wave a goodbye
to the two of them, staring
at the Maître d who is
attending other customers.

Dinner with Paul Norman
and the girls.

``My call in life,
is to kill the people,
kill the people. Did
you get that Jessica''

``Yes yes Patrick kill the peace,
might as well kill the world.
Why haven't you touched your
lobster escargot?''

``Do you want to be a fantasy''

``Yes Patrick I want to be a fantasy''

\chapter{Vomiting Food}

``Are we aware Price?''.

``What, that we're
horrible human beings?
Yeah, I'm aware'' he
says, face morose, sitting up
from the backseat of the cab
as it passes the chemical bank
on the corner of Eleventh
and First.

``Well, yeah not
that but''

``Gram?'' Price offers,
whilst doing a bump himself.

``Price what if you had
some super-sensitive ability
that others would exploit'' I ask,
ignoring, staring at the cab driver,
making sure his eyes \textbf{are} glued on the road.

``What you mean like those
math olympiads from China they got working at
JP Morgan'' he says
all the whilst sniffing.


``No'' I sigh, ``Don't those
kids hate their lives?''

``Eh, its what they do,
\textbf{What} gets them paid,
\textbf{What} makes
their parents proud, \textbf{What}
gets them through this city..'' he
stops, leaning his head out
the window, making sure the Armenian
is taking
the shortest route. ``Saw
an article about the ethics
of Rolex ownership''

``Ethics? What does ethics
have to do with a watch.'' I say
sharply.

``Well...'' he says, rolling
up the window, ``It's
easier to buy a Rolex,
than not buy one, - if you
have the currency -''.

``Right'' I add, ``You'll
think about it all day, so
you might as well pull the
plug.''

``Right- but, 15K on a watch
can't you dump that amount
on something. I don't
know a char-

``Price a Rolex is an investment,
a \textit{commodity} - that holds
its value incredibly well.
Not only, is it a smart
financial decision to own
one, you could, theoretically.
Pass it to your kids..''

Price doesn't respond and
gazes into the fare meter
as it hits \$14.80.

``Jeez, would you take that
diaper of Bateman'', he's
referring to the blue surgical
mask I've been wearing all day,
for no particular reason.

Aerating the cab,
with my slow breathing,
I rip of both the straps, tossing
it out the
back window, watching
it expand like a kite
across Eleventh and First.


When we get to my apartment, Price
is wanting to ransack my
refrigerator - because
he's been sobre \textit{for
too long}.

``Bateman, why's your fridge so fucking empty''
Price shouts, sounding genuinely concerned, his fingers
probably rifling through cans of tinned peach,
moving them - only to find
some ladies fingers and a head of lettuce, that
I've been saving for later.

``Check in the cabinet''

``Won't they be cold''

``Wait. I'm coming''

I enter the kitchen,
discovering Price on his
knees examining the contents
of the fridge and he's positively
startled when I slam a cabinet
to get his attention.

``Fuck Bateman, why'd
you do that for''

I guide him to a mini-fridge
on a bottom cabinet,
covered in a dish towel.

``Woah, where'd you get that from''.

\textit{Don't say Trump tower,
Don't say Trump tower,
Don't say Trump tower,}

``Trump tower'' I say proudly.

``Woah ho-ho'' Price says, examining it.

it's cold and i'm cold, which makes me colder

'You make a mockery of the law itself.'

gifted price, i didnt steal it,
a bell boy was gonna throw it out,
i mutter

he nods.

I nod no
 emo pinata
recruit more tissues,
for the snot on my nose

conjur where the extra-weight
will go, my thighs, stomach,
face oh god not the face
is all i can think in the lobby
of

A searing piece of hunger
is ripping my side
waffle iron,
tossing a whole kitkat
in there and eating it
whole the molten chocolate
running down my Borelli
shirt
cereal pools into my belly
button

Children of the second world
war was the topic on
\textit{60 minutes}
\chapter{Red Mist}

%This triggers the release which causes confusion centre of gravity what way he will fall if the wind will pick up on.

%when i cross the road between im stopped by a cop who asks me why im so hot sweaty and bloody and i pin the blame on
Another morning,

Nobody notices what I
have in my front pocket.

\textit{Nobody} notices the homeless lady,
crawling up to my leg after I've
maced her numerous times. \textit{Nobody}, notices I've done something good -
\textit{nobody} notices how
I've stopped a shoplifter who's walked
out a store with
several high-price wagyu steaks,
which she is planning
to sell to hungry families at a high
markdown.

``Why did you steal these'' I enquire
quietly, getting down to her level,
which means kneeling onto cold-wet
concrete, causing my worsted
wool Armani trousers, to soak
up the foul stagnant water..

The woman's face is pale and
crumpled, like scrunched up
paper -but
isn't old and she
wants to cry but
because of the excess
amounts of mace and the governance
of copious
amounts of lithium, is unable to.

She is wearing
a filthy black, Adidas
jumpsuit, with several
noticeable ash stains.
And an odd pair of sneakers,
dangles loosely from her feet, which
are missing both their laces.

I soften my voice and ask her again.

``Why did you steal?''.

She doesn't answer
and she looks up at a bus
pulling up opposite the
alley, at an advertisement
for Les Miserables, as it
passes by Fifth street.

Pulling herself up,
positioning her cold frail
hands onto my hip,
clinging,
feeling my warmth,
like we're something
out of a romcon, only
for it to fall because
of the cold, and reverse her
hands on my suede boots,
which are from John Lobb.

\textit{Stop playing God, Bateman,
just kill her already or torture
her for Christ sakes}.

Pulling herself up
again, letting
go of my calf, looking angered,
bitter. She glazes into my eye.

``Fuck you, you evil man'' and
then she coughs.

``Woahoho, you're an American?'' I
say, exaggerated, surprised - but
not surprised at her
lack of articulateness.

The woman doesn't answer and
uncomfortably fidgets with
herself, as the bus drives
away.

``Doesn't it hurt'' I say
flicking residual mace,
shaking the mace
can like its spraypaint,
laughing hysterically in the alleyway,
knowing I could decide
her fate here.

The woman is young and
incredibly pale like some mysterious
apparition and she makes my skin
look way darker due to how pale she really
is. In an alternative universe,
where she hadn't fallen
victim to whatever horrible
behind the scenes decision
that led to her position.
Led her to meeting me in the
alleyway. Led her to stealing
the wagyu beef. Led her t-
I'll never know I'll never
ask where she came from.

Thinking that the woman
is very pretty, thinking
that the woman has a nice
body and if - given a financial
prompt could get back
on her feet - could sense
a role in society and even
contribute to the economy.

Unfortunately this is where
the plaudits end and I let
my head hang back as if
hypnotised by the low hanging
moon and laugh even
more hysterically at the
advertisement for Les
Miserables, as it comes
to an halt - allowing all
passengers to leave -
something I do not let the woman
do.

In some twisted logic,
what I'm doing is right
and I'm given the woman,
now gasping for her breath
a chance to fight back.
And I'm
bittered by how the woman
is watching my face contort
with the moon, bittered
by the womans
bruised and how it
is still bleeding
from the punch I delivered
earlier, bittered
by how our eyes
are still strong
watching for what
I do. I bite into her
neck.

Knowing, my incisors
can't, won't do any damage
and the woman fearful - scared
I will kill her - rolls with me
for a while in the large
cold puddle of dark grey
liquid, like we're two alligators
doing a death dance.

When I sense, I have
at least punctured the girl
I immediately start
suckling on her warm irony
blood, forcing
her face into the
ground to stop her
from squirming taking great pleasure
in the heat of the moment.

The woman is shaking, flapping
about like a fish, in the puddle.
And  because her movements are so uncalculated,
so floppy, I'm able to maneouver jk
her	\textit{And I} into a much more comfortable
position. Still splashing, our
cloth's wet, covered in filthy
water.

When the woman is tired, can't
go on any longer, won't
go longer and breathing
hard, I roll her so her
beautiful face can see the moonlight,
see the stars that are tonight and I
swear I lay next to her, not caring
for the Zegna suit or my Allen
Edmonds.

It's doubtful, I'll kill her
but I stick around anyway, hiding
in a corner, leaving the woman
who is too cheesed out to move
to dry on a cardboard sheet I
dragged from the back of a McDonalds.

she is now lying on a
her eyes puffed out af
from mace

a bum is coming to check up
on her atleast i think but
he takes his cock out and tries
to dip it in her mouth,
like it's a McDonalds french fry.
mouth, knowing what he is
doing is silly and wont work he gets
down on his knees, looks like he's
praying in happiness that he finally
will be able to get of, unbuckling his
pants clumsily and
please explain to me what
crime is going to happen
when pornography is banned

I look suspiciously
at my watch,
not caring if the Omega
La Magique is damaged, not
worrying if the band is ripped,

The apartment
is dark when I enter and
I don't bother to turn
any of the lights on.
Dissolving into my sofa,
feeling cold from the
wet suit, I turn on
the televison. Tonight
on 60 minutes is about
a man who.

I stare out



in some twisted logic,
what I am doing is right,
by prolonging her suffering,
causing her to believe
her death is near, then showing
her there is hope
I'm doing good for the world.

there is no benefit that has ever come from pronoga
it is entirely demonic
it is entirely destructive
everyone who it touches it destroys
without an execption
there is no safe use of it
there is no Oh im just going
to play with a bit of it -
this is just a bit of fun

were we made for artistic appreciatoin

\chapter{Handsome Faggot}

Human beings are eating when they
are not hungry, this is wrong

``Oh my gosh, oh my gosh, oh my gosh,
oh my gosh'' he says hysterically
fanning himself as his voice pans
out in the elevator.

``You should blot it'' I add.

I'm stuck in an elevator,
with some utter faggot,
from Morgan and Stanley
I'm assuming, who was
c

\textit{What I
want to say is blot it you idiot, no don't
rub it with your diamond ancient madder silk pocket square
in brown, that'll only make it worse}.

I grab my handkerchief, which is
from Luserna and blot gently.

``What are you doing'' he says half frightened
half scared and he instinctively grabs onto
the wrist of my hand but I grab
his first motioning him to let go.
His skin is soft and so is mine, I have
started using Evian rich aloe vera moisturising
cream that I picked up at Hermes for 290 dollars.
My watch passes over him and I think he has seen it
but his head is changing left to right
too quickly for me to tell and his wan
eyes scans the elevator floors which are
soon to reach 54.

He looks like one of those male korean boys,
girls universally swoon over now. His shoes
tassel loafer, the top of his feet
are beautiful white skin.

The spot of wine has now expanded 3 fold.
``Oh my gosh, oh my gosh'' he says again,
he looks like he is about to cry. ``I can't believe
this is happening, on the worst of days''
and the
rest of his speech is muffled. He takes of the seersucker,
which has now caused the spot to spread to the white
linen shirt he is wearing.
His head is small and his limbs long
He places a gucci snake wallet on the, entrusting
me with hesitant eyes and I point him towards a
drawer, where he bends over and exposing his behind.

I flop down on a sofa chair and light up a half-smoken
cigar.

``does ir ever stp raining``

``I am excited for the collapse of civlisation
and the

you sound like an evil movie villain he says laughing
placing his hand on my chest.

i want my mom to think shes pregnant so she stops drinking
``Oh so your a Computer
Scientist''

``I work in software''

you are
\chapter{Killing Kenneth
Copeland}

Patrick, your bleeding!
And he plugs my nose,

frozen like a snakebite
when i arrive back to the apartment,
my arms are full of baskets
of kentucky fried chicken
turning so he can see my profile
that me and Kenneth
Copeland will enjoy, whilst
we watch 60 minutees,
my arms are also full of toys
and gifts for the kind couple downstairs
who have been putting up with the noise
Kenneth and I have been making
\chapter*{Public M\^rDe\^r}
and how often do you think of me

I feel incognito.

Fog, which
sweeps inland from
New Jersey, pools at the
bottom of my torso. And
only my head is visible -
teeming with incandescent
thoughts for a better
future.

The pocket phone buzzes and I'm immediately
on red-alert.

Opera pumps, which I've ordered
from bespoke shoemaker Tony
Gaziano, that will go with my
bespoke tux from Joe Hemrajani,
peaked lapel - no shawl, silk cummerband,
pleated high waist trouser
and starched pleated shirt, are
set to arrive any minute and I check
the delivery notes. I have - mentioned
to leave them at the reception
of my apartment complex.

Liane Williams, an
escort I met last
Wednesday, who I'm
not sure why I haven't cut of,
has sent me several if not
a hundred messages at least,
asking why I haven't taken
her up on her dinner offer.

And connecting to public WiFi,
from Starbucks, I give her
the satisfaction of knowing
I've atleast opened her messages
and I'm immediately met with

\textit{I don't know why you've only
seen my messages}

follwed by
a thinking-face and pleading-face
emoji. But I'm simply not interested.


The SoHo centre of lower
Manhattan, is an odd area
really and I've only been three
or four times - the last 2
being in 2016. So for a minute,
I'm in complete contradiction
with myself.

Everything's
been revamped, apartment's,
shops, the breeds
of dogs, the kinds
of people -
gentrified. And
although, there are now
several if not hundreds
of pop-up shops,
containerised, crammed,
cramped blanketing
various rainbow-coloured
flags, I feel a loose breeze
compelling me to succumb
to the area's calling.

The word \textit{\textbf{LOVE}}
is etched on a shop sign,
two blocks down from
where I'm standing, a jaunty
salon which I think
sells fragranced pomade
and various sweet-smelling
hair products.

Stepping under
scaffolding, out-of-state
constructioner's
perhaps too disincentivized
to catcall make hearty
conversation, warm
facial-expressions
are visible
through the fog.

Now walking past
Iranian owned coffee
shops, hearing:
French, Spanish,
German, Korean, did I
say Spanish, Persian
and other languages
I wouldn't know.
And wanting to feel,
that my tongue is being robbed
of its native breath but
unable to, I make
warm conversation with two
Parisian women,
who I find out are
chemists. And
we discuss principles
behind kerosene, napalm and
sarin gas. Wavering me on with
burgundy and
tuscan-coloured leather gloves,
which I think are Armani, I regretfully
decline as I'm not sure how long
we would sit, how long we could
talk, how long should
I wait before asking to hang-out
some other time, place or day?

``Oh God, Oh God, Oh God''
I moan, pretending
to search myself for a
lost article of value. Stepping,
over a couple's lying
labrador, hearing the
automized ring of shop
bells, seeing well-groomed
homosexuals exit taxis
wearing mink-fur coats and
trilby hats. Maybe, I'll
take Liane up on her offer?
Oh God, what am I saying.

Something, horrible has
been compromised inside of
me.

Trying to trigger,
lascivious thoughts
of me fondling the
two women's breasts and
slapping my cock onto
their lips, I can't.

excuse me, what
are you doing
Something's been compromised
inside of me. And emm maybe,
I'll take up Liane's
offer? Too late to get back
to her text though,
I'm too far
from Starbucks to get a good
signal.


* I reprimand
him, taking satisfaction
thinking the gun
is still to his head and i'm a
good hundred feet away
from him.
take that motherfucker
gun in pocket
whith his hand up
like and idiot
talking to an elderly
man, knowing 1/3 of his life
in my hand. pretty
angular chinese face girl.

As I walk under scaffolding,
I can't help but notice
the bright colours that
peak through the steel bars.

Neon, bright, tweed, yellow,


This is all to change, I'm
met with an ethical dilemma.


A new art gallery has opened. I don't know if it's
new. Everything here looks new.
I don't plan on visiting. Or doing anything
with this fag horde. But a small group of grad-schoolers,
dressed normal
who are dressed
similarly, are walking up to it. So I do
the same and from what I know they're being led by
some old white lady, who looks like she
knows the place. Although I don't, get a good enough look at her,
to cast judgement.

And I march behind, casually fitting in behind a slot
of fellow tall white males, who are making idle conversation.
a tiny polite voice, from behind, says ``Excuse mee''.

A girl is tugging at my jacket sleeve,
signing if she can get through the gap between my shoulders
and of another students. And she extends
her arms, clasping them in a pistol shape,
which make her more streamlined and
she quickly lunges into the crowd, where
she will most likely reconvene with a group of friends.
\textit{Very cute.}

I smile at her and I think she smiles back, I try to focus
on her beige overcoat, leather backpack and Doc Marten boots,
before she disappears into the crowd.

We slowly shuffle in, filling in all possible gaps, edging'
of the curb. And a valet driver, Indian, South Indian?
His skin is very dark, yells something the block opposite
us - to a man - something about him forgetting his keys.
And the man beckons him to toss them, which he does -
which he misses - horribly and they slip into the gutter,
where they will most likely rest until the city water board
can arrive.

``This'' - I pause

``Is exactly why Asians can't be quarterbacks'' and I'm
stopping myself from laughing hysterically.

No - one laughs, except the sound of the now
pissed of driver half-laughing half-furious. But a woman,
who is not part of our group,
some stone-faced goth chick, whose feet walk
on road, turns and tosses, baring
her fangs at my face while also hitting me with some
sort of polyester fabric belonging to her
cape and a streak of hair is revealed,
which is cheap. Yonder and a ritual silence.



After some time, we slowly begin
shuffling in

and I'm soon face to face with
some spot-nosed prepubescent teen, gating me from the rest of my herd
and pointing to the disappearing crowd - arm leaning
on a front desk.

``I'm with them'' I say
coolly, smiling like an idiot,
pushing back my Oliver People's glasses, although they
fit me well and don't need adjusting.
disacknowledging anything
he has said.

``That'll be \$16.50 sir, \$12 if you're accompanying a small child
and \$13 if you're an existing member
of the V-

I cut him off, his geeky salivary
voice irritating me.

``Look'' I say, tempted to
grab the collar of the shirt
not wanting to mess up the
silk bowtie. But I notice it's pre-tied
and not silk, so I latch onto it
anyway, ``I'm (I say sternly) with them'' I laugh, smiling coolly again,
pausing to check the time on my
Cosmograph “Zenith” Daytona Rolex with Lapis Lazuli dial, which stopped working two days ago.

``Dude layoff'' he says nervously -
reaching for something.
Visibly shaken. He rubs of the
fingerprints that I left
imprinted on the collar.

``Their''
he says pointing
to the last member
of their collective fading
into red velvet curtains.
``group is booked for 16 of them,

``I'm with them'' I say
coolly, smiling like an idiot,
pushing back my Oliver People's glasses, although they
fit me well and don't need adjusting.

``That'll be \$16.50 sir, \$12 if you're accompanying a small child
and \$13 if you're an existing member
of the V-

I cut him off, his geeky salivary
voice irritating me.

``Look'' I say, tempted to
grab the collar of the shirt
not wanting to mess up the
silk bowtie. But I notice it's pre-tied
and not silk, so I latch onto it
anyway, ``I'm (I say sternly) with them'' I laugh, smiling coolly again,
pausing to check the time on my
Cosmograph “Zenith” Daytona Rolex with Lapis Lazuli dial, which stopped working two days ago.

``Dude layoff'' he says nervously -
reaching for something.
Visibly shaken. He rubs of the
fingerprints that I left
imprinted on the collar.

``Their''
he says pointing
to the last member
of their collective fading
into red velvet curtains.
``group is booked for 16 of them,
I counted 16 people''

He's in his teens, sporting
a pencil moustache, a wad of yellowish acne,
medium black oily hair.
And he counts the change that I begin
to throw at him one-by-one as
he opens the red ribbons for me.

He lingers for a moment,
as I offer up my hand, to which he accepts,
``Masturbate much''
I ask, whilst shaking his hand, which
is much weaker than mine.

``W-what'' he says, eaking out,

``Don't'' I say sternly,
``Not until you're 23. Causes excessive teenage acne,
imbalances in testerone and other problems
in adolescence'', I say as
my open-spread hand points and moves
downward motion pointing
to his body.

He is now even more shaken.

\chapter*{Turning Point}

Fuck. Cunt. Shit. Whore. These
are all words in the English language
which are deemed to rude to be
used in passing conversation.
When the Normans invaded England, they introduced French variants. Those who used the old words were considered vulgar.
For example, the old English word for Nose is Snotte.

``You fucking whore'' I hiss under my
breath to a contemporary
painting of Marie Antoinette,
inspired by Élisabeth Vigée.

And I whisper to the braided red rope, holding
me back, that in time
I - would be back.

Resting my Serapian overnight
leather bag on matted carpet floor, I
turn facing an oval mirror.

The aforementioned Giorgi
Armani suit that I am wearing
is now fully dry.

A twilight-blue, super 200s wool, 3 piece suit,
in sharp double-breasted cut, with subtle white chalk stripes
falling down the course of fabric, is accompanied by a tonally coordinated Tom Ford
contrast collar shirt. And underneath is a Hermès jaquard tie, in red,
which is buried by the Ford's sharp spearpoint. Only to be lifted by the rose gold
collar pin by Hermes, that provides the impression the tie is
always moving with me and
I'm wearing a silk Zegna baby-blue pocket square, which is slightly
undermined by the blue Ford shirt.I look extra dapper
\textit{And
I'm white, just so you know}.

My trousers, matching, high-waisted
with silver side adjusters
and twin pleats running down its side
are met by a pair of double monkstrap
Edward Greens in oxblood
with slight patina, which give
me a playful look - and those
are met with black Beau Brommel silk, cashmere-lined
socks.

That bombshell is still there but
I must admit my work friends
chastise me for using that
word so sparingly - but
my work friends are all married
to hardbodied native women, so
their opinion holds no weight
to me.

But she is.
Asian, east, crescent moon eyes,
red ribbon as a braclet and has now disappeared from
my radar..

I look for her but
I'm approached by two fat chicks, one of them is holding a full glass
of red-wine.
 \textit{I'm not
dressed for fat chicks am I?} I
think silently, feeling my shoulder
padding.

``You ask, him no you ask him.``
they both repeat, giggling with
arms interlocked.

``Hi'' I say coolly, ``Can I help
you two beautiful ladies?'' with
hands buried in my trouser
pockets to give me a slightly casual
oomf.

``Well'' she says with her
arms at the front of her
dress,
obviously flattered
by my comment just now
``I was just thin-

``She wants to ask for
your number'' the other -
larger girl quickly finishes.

I give her my business card,
``How's it feel'' I say
as I transfer card from the
holder to her fat paws.

``How's what'' she says with
confidence, not paying
the slightest attention
to the gold leaf
she was now in possession of.

``How's it feel to be one,
o, two?'' I say staring
at the card which is being
insulated by the cradle of her fat
hand.

``102...'' she says hoping
I finish to sentence, like
couples do.

``102 pounds close
to the US medical associations
requirement to be obese'' I say
with another cool smile.

Glass typically
has a tensile
strengh of around
7 megapascals, which is
similar to a high-heeled
woman stepping on a tomato
and I'm already calculating
how long it would take for her
wine to reach my clothes.

She still takes the card and
the gastropods jackhammer away.


\newpage
\chapter{test}
Unusual, unpopular, unlikeable,
unwanted. Above me hangs,
a sky, with hung clouds dialled
down to shades of radio grey,
with thin treads that float past
me like jellyfish legs. And men, women
and children are sucked into a tornado
as it shifts through the wreckage of a town.
And a eastern european name sits below it
which I don't know the correct pronounciation
for.

i'm reluctant to leave, she was really really cute i say

``Now class, this is a genuine
(she says the name again) of the
tragedy that took place in Armenia,
her voice slows, sighs.

``Now class, zis is a genuine
Giorgio Armani painting
of the famous seranade of '92.''
her voice slowed, ``Can anyone tell me
what the clouds symbolize
here?'' she pointed, pushing
me away from under the spotlight so the others could see
- the feathers on her hat, nearly piercing
my eyes..

``Observe how zat stroke is lighter
than the other, how zis cloud
is flying and
look! to how
zis one droopes, oh
he cries!'' this was the second
time she pushed past me
clouds mask the passerby's
busy faces and how the

her ugly voice would drool on.

To be truthful, I believed
the whole art thing, the
modern art thing was a sham.
A well thought out
ponzi-rich-scheme
to get people out of paying their taxes.
But it was more to it
than the splodges of paint or
random strokes of grey.
The world and -and all of
its people wrapped
themselves up in some
blanket of -constant
involvement with each other,
it was fucking disgusting,
reminded me of those
germ-free bubbles children
used to be kept inside.
how everyone became socially
insulated within their bubbles
and circles.
But I was placed conveniently
within it. And I would
have it no other way.

``On December the 11th
1988, Armani painted
his famous troubled sky
with only a day left
to finish Armani beautifully
and intentionally
[she quickly affirmed]
left several scenes here
unfinished pointing of to some...

No today wasn't 1988
and it certainly wasn't
16 days from Christmas.
Today was the 29th
of February, 1928. I
was one of many but
the collective output
of Britannia's finest
college. I was
ready to be signed,
shipped and stamped
to some yuppie-producing uni
out mid-west, where
I was to spend the duration
of my academia studying law.

I really contributed
enough to this state,
as it stood. Just as my old man did ,
he was turning 54 this week
so I made plans to go see h-

``Much to my sadness
class,
Armani died 3 days after
finishing Le Mont Riche.
He never even got to show
his masterpiece to Grand
Lukas Dievetri of Luxem-


This must have been the 100th time, she interrupted
my stream of consciousness and as I uttered
those words, I felt my words echo
of forgotten paintings and boom of ancient
relics. I felt a sea of relief,
sweep over me.

``You yabber on about this and
about that'' I said with exaggerated
swagger, ``but i dont see anything,
do you'' i continued but stopped
as I realised no one was listening.

``The walking man symbolises a
rooftop, the flower symbolising
a new hop-

"God - would you fucking shut up"
The curator stopped.
The class stopped. She stopped -
jaw-dropping and all. There
was a certain smug, self-absorbed
look to her I had seen her put on just
moments ago when
our tour group had
entered the exhibition... - but now it was gone,
all gone like it had been whisked
away someplace else - where
no one would think to look. I threw the toothpick
I was using a few moments
ago, when we were given appetizes
a few moments ago, at her.
It bounced of her beakish nose,
with large perforated pores.
I also made sure to leave
a few seconds pause between
the word God and the word
``would`` to avoid
any miscommunication.

Ill make you feel my pain.

What you think, I like
to kill, no he was
some doped-up old man,
some cuked up old lady
``Jeez,
now I can at least hear myself
think''.

Oh yeah, it was like being
born a kid all
over again, I tell ya. The day I went
up over to see him, he received
a phone-call from work,
from some jazzed-up schoolboard official
who wanted Dad to keep a ``cool-head''.\\
``Mr Amby, is it?``.\\
``Yeah, what's it to ya'' he said, probably
angrily, going through his weekly cigar.\\
``Well I'm Mr Timothy-Pierce, with the ISPCA
and I'm just calling to confirm you're aware o-\\
``The whoozies?''\\
``That your son hasn't enlisted in this years
annual teutonic exam! his overly excited
faggot voice probably conjured up. ``No worries,
no worries at all Mr Amby, just called to confirm
this with y-

You wouldn't believe the beating he layed down on me
when I got home. Stars and stripes thats what I saw
and my back looked like a tiger!
I'm not sure how the rest of the phonecall would
have played out, probably
involved one end angrily hanging up.
But the weirdest, thing is you know,
, his eyes never really
met with mine anymore.. except when his friends arrived
and he toasted me the occasional innocuous shine. It
was true though, I withdrew myself from those
stupid exams - withdrew myself into one of Earth's
corners where man was immune to
their mom and dad's hypothetical discussion.
``He's such a good boy. Go easy on him, so what
if he doesn't go to uni?'' my fat aunts voice would
plead from the second floor of my parent's 3 story house.
The walls were thin, so I heard everything. You'd think
the devil and poverty had a drink with my dad,
the way he'd swing his head up and down,
whenever he'd hear of me.

By the time I was halfway out the art gallery,
I already spotted two fat ladies, both wearing
mink coats, silk hats and wool gloves. Man,
did I want to push them, onto the
wooden floor, where they would roll
and collect dust as if they were cotton candy
and observe their struggles to pick themselves up.

Her ensemble reminded me, of when I was
sent of to one of the  naeveu riche,
no style at allSouth-East's most
prestigious of boarding academies - to learn
and pick up on what made the rich the rich.
To which I did. And it was then. That
I learned. I had no place. Or interest, in
high society.

It felt like everyone was getting a piece of
the pie in the capital. Especially, the Jews,
they traced their roots back no less than 2000 years
and climbed every high position of society before
you could even think otherwise. I liked Jews. A lot
of people my age didn't but they had never done any
harm to me, so why should I involuntarily hate?

When I had fully left the gallary, I sat
on a park bench, realised I was
in a light sweat and had to stop
putting pieces together in a hurry.
I wanted to make sure my story wasn't all
over the place. That
someone would listen to it.
No more jabbering or ranting. So whatever poor soul
that was to stumble upon it,
had some sympathy for me atleast. And wrote.
I wouldn't stop writing until the night had fallen.
I was just getting my story together afterall.

Once the teachers had taken a register of
us all onboard, the coach had begun
to set sail. It felt like we were pilgrims
about to charter of
into some fantastical wasteland.
As we approached the newfound school,
we realised it was a grand building
which encompassed several large acres
of land. Its main hall would jut out evenly
from the neat mini-cathedrals,
like it was a chess piece to its left
and right. A large rugby field sat past the school,
with acres upon acres of rich country forest
scrummaging in from behind and lavish -no spotless
dormitories flanking in from the sides.

I felt like a bag of shards, walking
out that musty rental coach, lungs filling
with new-country air - ready - to - snap
at any given moment, the only thing
which could hold me all together
was the cheap of-the-rack wool-blend,
90 percent polyester, 10 percent new-wool suit
I was wearing.
It had rained horribly that morning, and under my
newly-infinite gratitude, I had stowed away this
horrible mass-production
pen, directly into the heart of my blazer, only for it
to spoil - bleed all over the plastic inner lining
of my suit. So it was decided upon departure,
I was to be equipped with three of five essential
items; an ill-fitting black (schoolboyish) suit,
oil-stained hands and frizzy dark wet hair. I
was to feel as though. I had come out the ground,
rather my own respective school.

We were all rounded up, led into a hall,
chaperoned for a bit given tea, biscuits that
sort and then came the host. I was
assigned a host, a ``buddy'' to speak.
He was 3/4 of an inch taller than me - but -
perfectly chiselled and gave of a sort
of a greco-roman appearance. He wore a deep blue
windowpane suit, unbuttoned, with a light blue shirt
and black monkstrap shoes. His suit made mine
look like something spewed out of a Sear's catalogue.
His name was Will. I never found out his surname.

No Will was nice after all, it wasn't my shyness
to the world's wealth, or better yet my lack of exposure
to it all. And it wasn't Will's friends, with
their long grains between each chortle
or the snobby boys who sneered as they walked past
you. So as Will
toured me past his classrooms,
I thought what a horrible-freak
accident it must be if I was some sort
of vestigial twin who had attached itself
onto his friends. No, it
was something else that left an impermeable
stain on my young and impressionable mind.
Before the new year, I gained a fixed interest
in all things mens-shirts. Fabrics,
were mostly cotton or linen some even being a light
polyester blend. They were all patterned
somehow, or lightly decorated never plain. And
no matter the season, all shirts were long-sleeved.
This all happened, due to one of my own - my own college
I mean. A brown boy, asian-brown, of South-Asian descent, described
me as homeless-looking right to my face. I wanted
to punch him right then and there, yet thought
it'd be better if I distance myself from the city's local
vagabond community first.

At the same time, but a few months prior, I had
started to fall for a fair-skinned girl. I did
everything correct. Wear period-appropriate
clothing, use the right mens-perfume, hold the door
open for her, listen to her problems
offer to tie their shoes when they became undone
- yet no gesture of mine was ever fully appreciated.
Through the course of those final dying
academic years, I enlisted in the army as a junior
officer and developed what one recruitment
psychiatrist would go on to describe as an
``incurable and unreserved scorn, to every man
and woman I was to meet''. Yet one man was
to slip from this reel of judgement.
Akbar Ali, second lieutenant in command
of the poofta batallion.
This wasn't really true, Akbar
like all us other, contributed
his fair share to the war effort.
So I'll start again. Akbar. Yes, Akbar
was made exempt.
``Akbar swaggers round the corpses
of our enemy, revolver in hand
and woman in the other,
heart locked up forever more in
young ectasty'' is what his platoons men
would choristically repeat, with a staff
sergeants parade stick teetering dangerously
close to their shined shoes.

To me Akbar, was nothing more
than a democratically elected dictator.

In my worst of temperments, I snapped, yelled
``What the fuck is it you want? Sniff, Broads,
Dames, Women? A man of your calibre, ought
to be ashamed winging all the time. Here,
this loads downtown, I'll take you there
one day. Do a man like you some good''.

Sniff, was what the lowest of ranks would
refer to as what I thought to be cocaine.
Akbar, wasn't a druggie and putting him on par
with them, seemed to be my only regret of my stint
inside the war machine.

``No`` he said, rubbing his face like a woman does,
``Oh, I don't know.. You see! I want something,
that isn't thi

This pissed me of beyond it all, just another
silver spooned, honey-sounding officer. I
was just about done with his sort of
character. But just as all moths, are inevitably
due to set sail for light in the morning,
return for night to dip their wings in tender flame,
this only drew me closer to him. I knew what wasn't this.
And I knew never to ask again. No-Akbar, had turned out
alright in the end. I went out, made sure all archives,
medical records published in his name, were to
be kept accurate and morally honest. And if not
for me, well then I'm sure his character would
be taught in some, I don't know rudimentary
junior officer's seminar. He was a gentleman, in
every sense of the word, capable soley for her.
very sense of the word, capable soley for her.

As the war was nearing closure, I became prone to assign utility to each
and everything I was to do. No matter, how infinitesimally small it seemed.
I took it upon myself to pull others from the wreckage of war, extract in-
formation from them, and leave them to drown if I chose them if need be
to. I went on a religious pilgrimage, spent several days in the wilderness,

Polytheist, bigotist, murderer, lyer
all things horrid. Just know. I am
not who you think I am. I wasn't
always like this, unlike you I had to learn
to hate.

\part{NAME}
\chapter{Beach with broken glass}
Fort Tilden Beach, Queens

Sunday, June, August, 2019 - NYC, office block overlooking central park.

I don't own socks, I don't own
ties, I don't own suits I don't
even
own shoes.

``Hypothetically - the dollar
may - could - would - should''
he pauses here, softening
his tone
``fall'' Paul (
whose actual name is Saul) says, standing
on a fixed office
chair giving a speech.
He thinks he's at the Oscar's.

``Depreciation'' someone
shouts at the back, probably
Haman who works in HR.

``Depreciate'' he says shouting
back, it's like he's in bingo or something.
``So a man - or woman has
gotta have a side hustle.
I mean look here, Tom sells pot.
James - porn. Uncensored, (his teeth
are grinning now) overseas jap porn.
Nelson, seized lingerie from prostitutes,
Tabetha, hair clippings from
various upstream celeb barber shops
and Brianda God knows who, but she's
making a killing out there.''

``That's disgusting'' an employee remarks
as he closes the door, on his way out.

``I know!'' he says,
raising his hands like he's
half vexed half happy. ``We went
looking for the money and we found it,
or it found us, big whoop.''.

Tom sits genuinely ashamed,
faceplanting - he sells
super discreet low dose mints that
chums like us pop during work meetings - \textit{it's very nice}. James - who seems to enjoy it,
grins, his mouth unhinged, exposing two sets of ivy-stained teeth
to raw artificial air being pumped out by \textit{Hitachi Cooling Company}.
And Tabatha, who appears semi-interested hearing her name, quickly loses interest,
combs through extensions with extremely long nails and disappears into her latest copy
of hollywood hearthrobs.

I stand stiff for a few
moments, hoping Paul
does not swivel his chair and
meet my eyes but I speak to soon.

``Jesus how the hell are you''
Paul asks
swivellling
aforementioned
chair, in a perfect practiced
360 degrees spin - ``new suit?'' he adds.

``No Paul''.

``Hey'' he says sympathetically,
``looks great'' he says softly.

 Paul asks me this everyday,
without seeming to forget.

But what Paul is eulogising here,
is the swallowing black-mass
of wool-blend, polyester mainly,
no canvas two piece
button up suit I am wearing.

Paul doesn't even wear a suit, he wears this
maroon jumper, which he says
is cashmere,
a blue shirt spread collar, with a tie you can barely see

``Drinks?'' someone says tapping at my shoulder
gently but I'm too annoyed to figure out who.

``I can't'' I say genuinely apologetically.

I would have never known that running my fingers through
my hair became an unintended way of moisturising my hands. It's gross.

I have been evicted from my apartment for 2 months now.

That's right I am homeless.

\chapter*{Residence}
Fort Tilden, Beach, Queens.

Every once in a while, a cop
car comes crusing by, the officer
dispatching himself from the front
seat, shades to protect himself
from the harsh sun
and a holstered gun
which hasn't seen much
use. And every time
I shoot him down with
my apathetic
glare.

Fingering the sand, drawing
crude pictures of happy
families in large houses, one square
with a triangle on top and stickmen
outside I sigh looking back
at my makeshift tent.

A derelict army bathhouse,
which was my former place of
residence has been taken
over partially by rats
and various coke dealers.
Although there are rumours
it's being leased to film
some pornos.

My tent, which I picked
up donated from a local
baptist church, in
firefly orange, with
various tears around
the centre which
have been patched
up by ductape, large enough
for 2 people  is being
anchored down by several large rocks.

I suddenly get thirsty but don't
feel like refilling my bottle
at the standing shower, a few
yards away.

A couple is embracing in a tent
nearby, there shadow being made
public from a lantern they have
inside and they look warm.

Leaning, into the inner
compartment of my backpack I
pull out a Macy's catalogue
which I found on the seat of
a subway and do a quick
inventory of my remaining
supplies for the week.

Oat crunch biscuits,
ziplock bag of jerky
strips (which I traded
a schnapps for), noodles,
crackers, more noodles,
3 pairs
heavy woolen socks, 2 grandad
shirts and an empty water bottle.

casting my eyes, into the beach
I'd sit next to my tent more
often, if it didn't feel like
it was another person that
I could tell
about my bizarre obsessions and
current interests.

Opening, the Macy's catalogue
I spot this Cashmere tailored
jacket which costs 2,700 dollars.

Most New Yorkers, would either
scoff at the heavy price tag
or oogle at the handsome male models.
But I, knowing that some of the proceeds
will go to Cashmere farmers and designers
was unbothered.

It's easier to buy a rolex
if your rich than not to - I mean
you have to think about what it'd
be like having it, seeing your
friends wear similar watches.

Resting the catalogue, delicately
into a side compartment of my bag.

Paul and the others don't know
I'm homeless and neither do my
folks who think I've used
money they've been wiring
to rent property downtown, but
it's not enough to get by
so I redirected all payments
into a savings account which
I plan to send back to them.

The times have listed
a new property, roommate -
must be cleaner
The times have listed
a new property, roommate -
must be cleaner..

\chapter{Strip Club}

\chapter*{Chapter 1}

Each morning, I would contribute
to the growing ashtray army,
check the outside, water
all outdoor plants and feed all out
of bounds
birds.

A letter had arrived. They always
arrived - addressed to three. Amby, Akbar,
Shelby. And each letter
was posted three times -to be
exact and to three seperate addresses.
Akbar, insisted that's how our mail
ought to be sent, ``You know old bean,
in case of a sudden dire emergency''
played his voice in old-timey
antipodean recording. I could have
sworn, there was a fourth name. But
it ended in -by and something was written
over it, so it didn't occur to me
as out of the ordinary.

Some plants required watering only once
or twice per week, but I still would
feed them. I would use a pipette, or a
syringe (adapted for specifically refilling ink cartridges)
Other times, I would splice the droplets
in half, watching their social bubbles split
down the middle,
burst and trickle down the underside of leaves,
only for it to be wasted on brown soil.

Then came the birds.

Oh just let me wear something,
you have so much clothes he said
about to touch the metallic pole,
from which several suits rested upon.
but stops, looking for my approval
to which i scoff laughing

he sighed flapping his arms,
like he was a bird.
we have different bodies, but he
was in the bathroom by now, wiping of
any immediate sweat with a handful of
tissues.

i picked out my first suit, schoolboyish
no i put it back, I want to make a good
impression. Wait, he's a faggot, why
do I care. His dad is rich, I said.
how do you know that, probably?
the two voices in my head argue

ill let you feel my pain

no we spilled coffee
your bathroom is so nice as well,
who designed it? oh where do you keep the towels.

patrick, why is there a lock on the toilet.

use the sink, or the tub,
what if i need to shit!
then wrap it in a plastic bag,
the towel is n my room
oh my god, patrick, your bedroom - its gorgeous
i sigh, a cloud of relief wading over me
\newpage
Prison for me, was more a place
to network with other criminals
and I pretty much received
equal treatment.
On December the 11th 1988
observe how
"5 heavily armed masked men"
It was
all over again
met up with the devil
at the bar one night
some nerd
I shot him, so what he was some nerd.
The red circuit of life, that he was
firmly connected with, finally made him disconnect
and as the smoke of my revolver returned back to sender,
I kicked his skinny corpse to the side.,
touch me and i'll kill you
He was wan in apperance, cheerful but sweating.
What do you mean she doesn't know who you are,
I just saw her wave at you

By now my suit was heavily decorated,
bell shoulders, pinched in from behind,
cinched at the waist.

probably just an accountant, got caught up in it
all why would anyone care I care he looked like a nerd.
some mental excercise.
didn't regret calling her a fat bitch.
You’re just writing, stream-of-consciousness as fast as you can.
I would clear up any misconceptoins later.

she said things, they fires in my head
then with the glimpse of a smile
fell to nothing like cigarette ash.
``Why hello, Eric'', spoke Mr Anderson,
in an overly-cheerful morning voice.
Some faggot, who lived up on
54th street,
who wanted to get mixed up in
it all. He wore a
camel-brown cashmere
coat, with faux fur lapels,
dark-brown ascot and a
I walked past 5 other people,
this morning.

I thought the war on cannabis was an unjust one.
bad rap
off the rack
years of wear
biae brummel
Most importantly she stops.

man sells us raybans
the sun, it's never
looked so cool before

i take of my cufflinks, he stares at them before
accepting.
They're gold i say,
omitting the luxurious
french brand behind their
creation.

handm- handed to me by my
father i want you to have them.
his body leans in a way that
wants to shake me or my hand
but he is too afraid to and
obviously still shaken from before


i've had 7 fillings, you know
have you ever had a filling
rich man at his castle
poor man at his gate
whats that old sport
i live with two other
men one of whome
I've already mentioned
and the other who I hardly
know at all.

two freakishly long long
vampirish instruments
sits
upon a while
silk cloth
left on a cold wooden
black table.

I also think it’s shameful that Keir Starmer didn’t prosecute Jack the Ripper, Guy Fawkes, Charles I, and Edmund Blackadder
She writes a lengthy
social commentary
on yesterday's comments,
and i reply with a ``
I love you , kissy face emoji
and send her a 500 dollar
amazon coupon''
really, i say smiling?
\chapter{Handsome faggot}
``Oh my gosh, oh my gosh, oh my gosh,
oh my gosh'' he says hysterically
fanning himself as his voice pans
out in the elevator.

``You should blot it'' I add.

\textit{What I
want to say is blot it you idiot, no don't
rub it with your diamond ancient madder silk pocket square
in brown, that'll only make it worse}.

I grab my handkerchief, which is
from Luserna and blot gently.

``What are you doing'' he says half frightened
half scared and he instinctively grabs onto
the wrist of my hand but I grab
his first motioning him to let go.
His skin is soft and so is mine, I have
started using Evian rich aloe vera moisturising
cream that I picked up at Hermes for 290 dollars.
My watch passes over him and I think he has seen it
but his head is changing left to right
too quickly for me to tell and his wan
eyes scans the elevator floors which are
soon to reach 54.

He looks like one of those male korean boys,
girls universally swoon over now. His shoes
tassel loafer, the top of his feet
are beautiful white skin.

The spot of wine has now expanded 3 fold.
``Oh my gosh, oh my gosh'' he says again,
he looks like he is about to cry. ``I can't believe
this is happening, on the worst of days''
and the
rest of his speech is muffled. He takes of the seersucker,
which has now caused the spot to spread to the white
linen shirt he is wearing.
His head is small and his limbs long
He places a gucci snake wallet on the, entrusting
me with hesitant eyes and I point him towards a
drawer, where he bends over and exposing his behind.

I flop down on a sofa chair and light up a half-smoken
cigar.

``does ir ever stp raining``

``I am excited for the collapse of civlisation
and the

you sound like an evil movie villain he says laughing
placing his hand on my chest.

i want my mom to think shes pregnant so she stops drinking

\chapter*{dfj}
Two freakishly long
open - open wider, he says
akbar drills into the silver filling which causes immense pain for the man as
this causes
akbar told me he saw, derek chauvin behind bars
and was glad to see him rot there
the fuck is this
posters of chauvin, and thao
akbar hits his head, or akbar is already bad
alcohol is illegal from the start of
announces the pmq
look if you dont want to
do this all you have to do is
just say.

his face, rocked, wrecked, wraught
with all kinds of pleasure.
and get this alcohol - fucking alcohol - theyre talking of making it illegal
again what is this nazi germany

tom you was there, james, christ - one of you say something
but they simply shrug and finger their nails
you can leave anytime - all you have to do is say the word. he stops and
says softly in a genuine way
drinks
i cant i say apologetically
THERE IS NO ONE THERE, YOU DIBSHIT MORON.
your right patrick, there is no one there.
can he mindread
Tom Ford - Homosexual
Henry Ford - Entrepeneur

you new here, bronx accent
yes, i tentatively
rancid concoction of urine caked semen
I've had so much plastic surgery done I wonder, whether
if it would be possible to ever go back
or not
you no call here ever!

I imagine that she's so used to strangers spraying sticky white fluid all over her face, she thought it was normal behaviour to do it to someone else...
gritty macabre
nimbus stripe
which stems from
People these days look down on shoe-shining. Some would say it's low-skill grunt labor, or too blue collar. Truth be told, it's one of the ultimate gentlemanly pursuits. There's a finesse and an art to it that takes years to achieve.  People used to take pride in their appearance, and the people who helped you look your best (barbers, tailors, shoe-shiners) were considered your fashion coaches. They were an all-around pimp that knew how to make any random person look their best.
yesteryear
Cladding the sharp brown silhouette from head to toe, the shape is cut from a virgin wool blend and slimmed for the most flattering form. Top tip: throw some leather boots into the styling mix to elongate the look even more

A friend told me to wait wait
and wait. And I did. But she
never came.

jessages
burthenous

``MMM MMM''
I mumble, mouth half-full
to an old man
I'm really digging this
sushi
mink fur
species designed to be mass produced and consumed feels so belittling of the experience of life.
broiler chicken
julienne slices
timeless dated
and i insert into his
mouth, him a bit taken
aback but too riddled
with dementia to know
any better
airkissing the Omega
right and emm
death row how do i qualify for that
fat fucking kids, heading up to a bengali vape shop,
wearing puffy jackets to make up for the lack of gym and flabby arms
to look intimidtating,
so help me god, the fat fuck walking infront of me i wanna gut because he keeps
turning around to stare at me
kicked out of eton for biting
another pupils ear
look at his suit
look at what hes wearing
hahahahahahaha, clodded dirt
stains, way too oversized in the length
Why is it so funny - oh my and
he walks away

your an unreliable na-rrator

the old fart, ticking away, murmuring
something about Regan

look, look imagine that
guy, that nigger over there
could hear what you've been
saying about that black Race
HA, he squacks, probably
an actual African

i used to let the credits
run, because i was afraid i'd miss something
i aerate the mask
salute john chapman


This triggers the
release which
causes confusion,
centre of gravity
what way he will fall
if the wind
will pick up on.

when i cross the road
between im stopped by
a cop who asks me why
im so hot sweaty
and bloody and i pin the
blame on
hare hair
theres something
wrong with him,
eww why are you speaking
to him. you look like a teacher
she says, which stuns
me
sweat likea  crack baby.
excuse me do you know
a good dry cleaners,

i mean are we meant to not like trump just because he cameod in
you know what price you have less self awareness than a dog licking his
balls in public
\end{document}
